% ***************************************************
% Appendix
% ***************************************************
\chapter{Wordlist sources}

The following list contains the details of original wordlist sources, CHIRILA source information where applicable, and details of any phonemic normalisation procedures used to maintain comparability between phonemicisations in Ausphon. The list covers all languages used throughout the thesis.

\setlength{\parindent}{0pt}
\setlength{\parskip}{0.1in}

\textbf{Adnyamathanha}

CHIRILA source: CHIRILA/v2/McEnteeMcKenzie

\fullcite{mcentee_adna-mat-na_1992}

Phonemic normalisation: Coda tap normalized as vibrant. Otherwise,
voiced stops, taps and fricatives normalized to lenis obstruents.

\textbf{Alawa}

\fullcite{sharpe_alawa_2001}

\textbf{Amurdak}

\fullcite{handelsmann_towards_1991}

Phonemic normalisation: Prelateralized stops normalized as flapped
laterals.

\textbf{Angkamuthi}

\fullcite{crowley_uradhi_1983}

\newpage


\textbf{Anguthimri}

CHIRILA source: CHIRILA/v1/ASEDA0240

\fullcite{crowley_mbakwithi_1989}

\textbf{Atampaya}

\fullcite{crowley_uradhi_1983}

\textbf{Badimaya}

\fullcite{marmion_badimaya_1995}

Phonemic normalisation: Double a normalized to long vowel.

\textbf{Bakanh}

\fullcite{hamilton_pakanh_1997}

\textbf{Bardi}

CHIRILA source: CHIRILA/v1/akl99

\fullcite{aklif_ardiyooloon_1999}

\textbf{Bidyara}

\fullcite{breen_bidyara_1973}

\textbf{Bilinarra}

\fullcite{meakins_bilinarra_2013}

\textbf{Biri}

CHIRILA source: CHIRILA/v1/Terrell

\fullcite{terrill_biri_1999}

\newpage


\textbf{Bularnu}

\fullcite{breen_bularnu_1988}

\textbf{Bunuba}

\fullcite{kimberley_language_resource_centre_bunuba_2010}

\textbf{Burarra}

CHIRILA source: CHIRILA/v1/Glasgow

\fullcite{glasgow_burarra-gun-nartpa_1994}

\textbf{Butchulla}

\fullcite{bell_sketch_2003}

\textbf{Central Arrernte}

\fullcite{wilkins_mparntwe_nodate}

Phonemic normalisation: Labialized consonants normalized to C + w.
Prestopped nasals normalized to stop + nasal sequence. Prepalatalized
consonants normalized to j + C.

\textbf{Dalabon}

\fullcite{evans_first_2004}

\textbf{Dhangu}

\fullcite{zorc_yolngu_2004}

Phonemic normalisation: Lenis retroflex stop normalized to retroflex
flap.

\newpage


\textbf{Dharumbal}

CHIRILA source: CHIRILA/v2/ter02

\fullcite{terrill_dharumbal:_2002}

\textbf{Dhay'yi}

\fullcite{wunungmurra_dhalwangu_1993}

Phonemic normalisation: Lenis retroflex stop normalized to retroflex
flap; all other voicing is allophonic.

\textbf{Diyari}

\fullcite{austin_grammar_1981}

Phonemic normalisation: Phonetic trill-released stop normalized as stop
+ trill. Otherwise, voiced stops normalized as taps.

\textbf{Djabugay}

\fullcite{robertson_jaabugay_1997}

\textbf{Djapu}

CHIRILA source: CHIRILA/v1/mor83

\fullcite{morphy_djapu_1983}

Phonemic normalisation: Lenis retroflex stop normalized to retroflex
flap.

\textbf{Djinang}

CHIRILA source: CHIRILA/v1/ASEDA0009

\fullcite{waters_djinang_1988}

Phonemic normalisation: Glottal closure normalized to a segment phoneme.

\newpage


\textbf{Duungidjawu}

CHIRILA source: CHIRILA/v2/K\&W 04

\fullcite{kite_duungidjawu_2004}

\textbf{Dyirbal}

CHIRILA source: CHIRILA/v1/dix72

\fullcite{dixon_dyirbal_1972}

\textbf{Emmi}

\fullcite{ford_description_1998}

\textbf{Erre}

\fullcite{birch_first_2006}

Phonemic normalisation: Double stops normalized as fortis.

\textbf{Gamilaraay}

CHIRILA source: CHIRILA/v1/ash03

\fullcite{ash_gamilaraay_2003}

\textbf{Gangulu}

CHIRILA source: CHIRILA/v1/Terrell

\fullcite{terrill_biri_1999}

\textbf{Gidabal}

CHIRILA source: CHIRILA/v1/cro78

\fullcite{crowley_middle_1978}

\textbf{Gooniyandi}

\fullcite{kimberley_language_resource_centre_gooniyandi_1993}

\textbf{Gugu Badhun}

CHIRILA source: CHIRILA/v1/sut73

\fullcite{sutton_gugu-badhun_1973}

\textbf{Gumbaynggir}

\fullcite{murrbay_aboriginal_and_culture_cooperative_gumbaynggir_2001}

\textbf{Gunya}

CHIRILA source: CHIRILA/v1/dixbla81

\fullcite{breen_margany_1981}

\textbf{Gupapuyngu}

CHIRILA source: CHIRILA/v1/BL

\fullcite{lowe_temporary_1976}

\textbf{Gurindji}

\fullcite{meakins_gurindji_2013}

\textbf{Gurr-Goni}

\fullcite{green_gurr-goni_2015}

Phonemic normalisation: Geminate stops normalized to fortis.

\textbf{Guugu Yimidhirr}

\fullcite{haviland_guugu_1979}

\textbf{Guwamu}

CHIRILA source: CHIRILA/v1/Austin 1980

\fullcite{austin_guwamu_1980}

\textbf{Iwaidja}

\fullcite{pym_iwaidja-english_2011}

\textbf{Jaru}

\fullcite{tsunoda_jaru_1981}

Phonemic normalisation: iji and uwu normalized as long high vowels.

\textbf{Jawoyn}

\fullcite{merlan_jawoyn-english_2005}

\textbf{Jiwarli}

CHIRILA source: CHIRILA/v2/ASEDA0435

\fullcite{austin_dictionary_nodate-1}

\textbf{Kalkatungu}

CHIRILA source: CHIRILA/v2/ASEDA0205

\fullcite{blake_kalkatungu_1990}

Phonemic normalisation: Double short vowels normalized as long.

\textbf{Karajarri}

\fullcite{mckelson_studies_1989}

\textbf{Kariyarra}

\fullcite{smythe_kariyarra_nodate}

\textbf{Kartujarra}

\fullcite{ogrady_gardudjarra_1988}

\textbf{Kija}

CHIRILA source: CHIRILA/v1/bly01

\fullcite{blyth_wangka_2001}

\textbf{Kok Nar}

\fullcite{sommer_koko_nodate}

\textbf{Koko Bera}

\fullcite{black_kokoberrin_2007}

\textbf{Kugu Nganhcara}

CHIRILA source: CHIRILA/v1/ASEDA0021

\fullcite{smith_kugu_1989}

\textbf{Kukatj}

\fullcite{breen_kukatj_1991}

Phonemic normalisation: Featureless vowel normalized as schwa.

\textbf{Kukatja}

CHIRILA source: CHIRILA/v1/ASEDA0504

\fullcite{peile_basic_nodate}

\textbf{Kuku Yalanji}

\fullcite{hershberger_kuku-yalanji_1986}

\newpage


\textbf{Kurrama}

\fullcite{dench_kurrama_nodate}

\textbf{Kurtjar}

CHIRILA source: CHIRILA/v1/ASEDA0026

\fullcite{black_kurtjar_1988}

Phonemic normalisation: Retroflex glide\textasciitilde{}tap normalized
as glide.

\textbf{Kuugu Ya'u}

\fullcite{thompson_sand_1988}

\textbf{Lardil}

\fullcite{hale_lardil_1997}

\textbf{Larrakia}

\fullcite{harvey_larrakia_2004}

\textbf{Limilngan}

\fullcite{harvey_grammar_2001}

\textbf{Linngithigh}

\fullcite{hale_linngithigh_1999}

Phonemic normalisation: Trill-released stop normalized as stop + trill.
Prenasalized stops normalized to nasal + lenis stop.

\newpage


\textbf{Malkana}

\fullcite{gargett_salvage_2011}

\textbf{Malyangapa}

\fullcite{hercus_maljangapa-wadigali_1989}

\textbf{Mangala}

\fullcite{mckelson_mangala_1989}

\textbf{Margany}

CHIRILA source: CHIRILA/v1/bre81

\fullcite{breen_margany_1981}

\textbf{Marra}

\fullcite{heath_basic_1981}

\textbf{Martuthunira}

\fullcite{dench_martuthunira_1995}

\textbf{Matngele}

\fullcite{zandvoort_grammar_1999}

\textbf{Mawng}

\fullcite{singer_mawng_2015}

\newpage


\textbf{Mbabaram}

\fullcite{dixon_mbabaram_1991}

Phonemic normalisation: Labialized consonants normalized to C + w. Final
schwa treated as a phoneme.

\textbf{Mengerrdji}

\fullcite{birch_first_2006}

Phonemic normalisation: Double stops normalized as fortis.

\textbf{Miriwoong}

\fullcite{kofod_miriwung_1976}

\textbf{Mirniny}

\fullcite{ogrady_mirniny_1988}

\textbf{Mudburra}

\fullcite{nash_mudburra_1988}

\textbf{Murrinh-patha}

\fullcite{street_introduction_1987}

\textbf{Muruwari}

CHIRILA source: CHIRILA/v1/ASEDA0252

\fullcite{oates_muruwari_1992}

\newpage


\textbf{Nakara}

\fullcite{eather_first_2005}

Phonemic normalisation: Geminate stops normalized to fortis.

\textbf{Ngaanyatjarra}

\fullcite{glass_ngaanyatjarra_1988}

\textbf{Ngadjunmaya}

\fullcite{wangka_maya_pilbara_aboriginal_language_centre_ngajumaya_2008}

\textbf{Ngalakgan}

CHIRILA source: CHIRILA/v1/mor83

\fullcite{merlan_ngalakan_1983}

Phonemic normalisation: Geminate stops normalized to fortis.

\textbf{Ngandi}

\fullcite{heath_ngandi_1978}

\textbf{Ngardily}

\fullcite{green_ngardily_1988}

\textbf{Ngarinyin}

\fullcite{coate_ngarinjin-english_1974}

\textbf{Ngarinyman}

\fullcite{jones_ngarinman_2005}

\newpage


\textbf{Ngarla}

\fullcite{brown_ngarla-english_nodate}

\textbf{Ngarluma}

\fullcite{hale_ngarluma_1989}

\textbf{Ngawun}

CHIRILA source: CHIRILA/v2/BreenMayi

\fullcite{breen_mayi_1981}

\textbf{Ngiyambaa}

CHIRILA source: CHIRILA/v1/don-lex

\fullcite{donaldson_ngiyambaa_1997}

\textbf{Nhanda}

CHIRILA source: CHIRILA/v1/ble01

\fullcite{blevins_nhanda:_2001}

\textbf{Nhangu}

CHIRILA source: CHIRILA/v1/CB-fieldnotes

\fullcite{james_yan-nhangu_2003}

\textbf{Nhirrpi}

CHIRILA source: CHIRILA/v1/bow-nhi

\fullcite{bowern_nhirrpi_1999}

\newpage


\textbf{Nukunu}

CHIRILA source: CHIRILA/v2/her92

\fullcite{hercus_nukunu_1992}

Phonemic normalisation: Voiced retroflex stop normalized to retroflex
tap.

\textbf{Nungali}

\fullcite{bolt_elementary_1971}

\textbf{Nyamal}

\fullcite{burgman_nyamal_2007}

\textbf{Nyangumarta}

\fullcite{geytenbeek_nyangumarta-english_1991}

\textbf{Nyawaygi}

\fullcite{dixon_nyawaygi_1983}

\textbf{Nyikina}

CHIRILA source: CHIRILA/v1/Stokes

\fullcite{stokes_nyikina-english:_nodate}

\textbf{Nyiyaparli}

\fullcite{ogrady_nyiyabali_1988}

\textbf{Ogh Angkula}

\fullcite{sommer_ankula_nodate}

\textbf{Ogh Unyjan}

\fullcite{sommer_ogh_nodate-1}

\textbf{Olkol}

\fullcite{hamilton_uw_1997}

\textbf{Oykangand}

\fullcite{hamilton_uw_1997}

\textbf{Panyjima}

\fullcite{dench_panyjima_1991-1}

\textbf{Patjtjamalh}

\fullcite{ford_batjamalh:_1997}

\textbf{Payungu}

CHIRILA source: CHIRILA/v1/ASEDA0394

\fullcite{austin_payungu_nodate}

\textbf{Pintupi}

\fullcite{hansen_pintupi/luritja_1992}

\textbf{Pitta Pitta}

CHIRILA source: CHIRILA/v1/bla0275

\fullcite{blake_pitta_1990}

\textbf{Purduna}

\fullcite{burgman_burduna_2007}

\textbf{Putijarra}

\fullcite{wangka_maya_pilbara_aboriginal_language_centre_putijarra-english_2004}

\textbf{Rembarrnga}

\fullcite{mckay_rembarrnga_2011}

Phonemic normalisation: Geminate stops normalized to fortis.

\textbf{Ritharrngu}

CHIRILA source: CHIRILA/v1/Heath

\fullcite{heath_ritharngu_1976}

\textbf{Southern Paakintyi}

\fullcite{hercus_paakantyi_nodate}

\textbf{Thaayorre}

\fullcite{foote_kuuk_1993}

\textbf{Thalanyji}

CHIRILA source: CHIRILA/v2/ASEDA0437

\fullcite{austin_dictionary_nodate-2}

\textbf{Tharrkari}

\fullcite{austin_dictionary_1992-1}

\textbf{Thaynakwithi}

\fullcite{fletcher_thanakupis_2007}

\textbf{Thirarri}

\fullcite{austin_grammar_1981}

Phonemic normalisation: Phonetic trill-released stop normalized as stop
+ trill. Otherwise, voiced stops normalized as taps.

\textbf{Tiwi}

\fullcite{lee_tiwi-english_2013}

Phonemic normalisation: r + alveolar normalized as retroflex. Following
Breen 1979, (w)o is normalized as wa.

\textbf{Umpila}

\fullcite{ogrady_umpila_1988}

\textbf{Unggumi}

\fullcite{mcgregor_handbook_1985}

\textbf{Urningangg}

\fullcite{birch_first_2006}

\textbf{Waalubal}

CHIRILA source: CHIRILA/v1/cro78

\fullcite{crowley_middle_1978}

\textbf{Waanyi}

CHIRILA source: CHIRILA/v1/WaanyiDict

\fullcite{laughren_waanyi_2016}

\newpage


\textbf{Wagiman}

\fullcite{wilson_wagiman_2001}

\textbf{Walmajarri}

\fullcite{hudson_walmajarri_1993}

\textbf{Wambaya}

CHIRILA source: CHIRILA/v1/RN Wambaya 29,269,292; NE NA

\textbf{Wangkatja}

\fullcite{blyth_wangka_2001}

\textbf{Wangkumara}

CHIRILA source: CHIRILA/v1/robnd

\fullcite{robertson_wangkumara_1985}

Phonemic normalisation: Double a normalized to long vowel.

\textbf{Wanyjirra}

\fullcite{senge_grammar_2015}

\textbf{Wardaman}

CHIRILA source: CHIRILA/v1/Merlan NA

\textbf{Warlmanpa}

\fullcite{nash_preliminary_1984}

\textbf{Warlpiri}

CHIRILA source: CHIRILA/v2/WarlpiriDict

\fullcite{swartz_warlpiri_1996}

\textbf{Warluwarra}

\fullcite{breen_warluwara_1990}

Phonemic normalisation: Prenasalized stops normalized to nasal + lenis
stop. Tense glides normalized to fricatives. Tense lateral normalized to
double lateral.

\textbf{Warndarrang}

CHIRILA source: CHIRILA/v1/hea80

\fullcite{heath_basic_1980-1}

\textbf{Warnman}

CHIRILA source: CHIRILA/v2/ASEDA0334

\fullcite{eidwun_warnman_nodate}

\textbf{Warrgamay}

CHIRILA source: CHIRILA/v1/dixbla81

\fullcite{dixon_wargamay_1981}

\textbf{Warriyangga}

\fullcite{austin_dictionary_nodate-3}

\textbf{Watjarri}

\fullcite{mackman_wajarri_2012}

\textbf{Wemba Wemba}

\fullcite{hercus_wembawemba_1992}

\newpage


\textbf{Western Arrernte}

\fullcite{breen_introductory_2000}

Phonemic normalisation: Labialized consonants normalized to C + w.
Prestopped nasals normalized to stop + nasal sequence. Prepalatalized
consonants normalized to j + C.

\textbf{Western Wakaya}

\fullcite{breen_wakaya_2006}

\textbf{Wik Mungkan}

\fullcite{kilham_wik_2011}

\textbf{Wik-Ngathan}

CHIRILA source: CHIRILA/v2/PS

\fullcite{sutton_wik-ngathan_1995}

\textbf{Wirangu}

\fullcite{hercus_grammar_1999}

Phonemic normalisation: Double a normalized to long vowel.

\textbf{Wiri}

\fullcite{terrill_biri_1999}

\textbf{Worrorra}

\fullcite{mcgregor_handbook_1985}

\textbf{Wotjobaluk}

\fullcite{hercus_wergaia_nodate}

\textbf{Wubuy}

CHIRILA source: CHIRILA/v1/Nunggubuyu Flora Fauna

\fullcite{heath_nunggubuyu_1976}

Phonemic normalisation: Morphophonemic w1, w2 represented as their
phonemic realizations w,b,k.

\textbf{Yadhaykenu}

\fullcite{crowley_uradhi_1983}

\textbf{Yalarnnga}

CHIRILA source: CHIRILA/v1/ASEDA0204

\fullcite{breen_yalarnnga_nodate}

\textbf{Yandruwandha}

CHIRILA source: CHIRILA/v1/breyandr

\fullcite{breen_innamincka_2004}

Phonemic normalisation: Trill-released stop normalized as stop + trill.
Prestopped laterals normalized to stop + lateral sequence.

\textbf{Yanyuwa}

\fullcite{bradley_yanyuwa_nodate}

Phonemic normalisation: Prenasalized stops normalized to nasal + stop
sequence.

\textbf{Yawijibaya}

\fullcite{mcgregor_handbook_1985}

\textbf{Yaygir}

CHIRILA source: CHIRILA/v1/morelli2011

\fullcite{morelli_yaygirr_2012}

\textbf{Yidiny}

CHIRILA source: CHIRILA/v2/dix91

\fullcite{dixon_words_1991}

\textbf{Yindjibarndi}

\fullcite{anderson_yindjibarndi_nodate}

\textbf{Yinhawangka}

\fullcite{wangka_maya_pilbara_aboriginal_language_centre_yinhawangka_2008}

\textbf{Yintyingka}

\fullcite{verstraete_grammar_2015}

\textbf{Yir Yoront}

\fullcite{alpher_yir-yoront_1991}

\textbf{Yorta Yorta}

CHIRILA source: CHIRILA/v1/bowmor99

\fullcite{bowe_yorta_1999}

\newpage


\textbf{Yulparija}

\fullcite{mckelson_yulparija_1989}

\textbf{Yuwaalaraay}

CHIRILA source: CHIRILA/v1/ash03

\fullcite{ash_gamilaraay_2003}

\textbf{Yuwaliyaay}

CHIRILA source: CHIRILA/v1/ash03

\fullcite{ash_gamilaraay_2003}
