% ***************************************************
% Appendix
% ***************************************************
\chapter{Supplementary information for Chapter 3}

Supplementary information and materials for this study consist of five
parts. This document contains three sections of text-based supplementary
information:

\begin{itemize}
\tightlist
\item
  A.1: Guide to data and code
\item
  A.2: Original wordlist sources
\item
  A.3: Tables of results
\end{itemize}

In addition, two zip files are provided containing supplementary
materials:

\begin{itemize}
\tightlist
\item
  A.4: Data viewer
\item
  A.5: Data and code
\end{itemize}

As the name suggests, A.1 is a user guide to the various files and
directories in A.4 and A.5. A.2 gives bibliographic details for the
original wordlists used in the study. A.3 gives extended tables of
results, listing maximum likelihood estimates of parameters,
goodness-of-fit statistics and \(p\) values for each langauage and
distribution type.

A.4 is an interactive app for visualising phoneme frequencies in each
language, the fit of different distributions, and uncertainty in our
results. It was not used at any stage of analysis. The intention is to
give a convenient tool for viewing plots in any given language, rather
than simply presenting a list of plots for all 168 languages in a long,
unweildy document.

A.5 is a directory containing all the code and data files needed to
replicate the study and the original output we produced saved in an
Rdata format. For usage details, consult the guide in A.1 below.

\hypertarget{guide-to-data-and-code}{%
\section{Guide to data and code}\label{guide-to-data-and-code}}

A.5 is a zip file, \textbf{A5\_data\_and\_code.zip} containing data
files and code for replicating the study, plus the original, raw results
files generated as output. Unzipping the file produces a directory
containing three subdirectories, \emph{data}, \emph{R} and
\emph{results}.

\hypertarget{data-files}{%
\subsection{Data files}\label{data-files}}

The \emph{data} subdirectory contains two data spreadsheets in
tab-separated format, \textbf{Aus\_segment\_frequencies\_2020-05-21.tsv}
and \textbf{Aus\_metadata\_2020-05-21.tsv}. The first of these contains
frequency data extracted from the Ausphon-Lexicon database. Each row
corresponds to one unique phonological segment (identified in the
`match' column). The `lex\_ID' contains a Ausphon-Lexicon's numerical
identifier for each language variety. The corresponding common name of
the language variety is listed in the `variety\_name' column. The
`count' column contains the segment's raw count in the language's
wordlist, `freq' gives the segment's frequency expressed as a fraction
of the total number of segments in the wordlist. `n\_forms' is the
number of words in the language's lexicon.

The second file, \textbf{Aus\_metadata\_2020-05-21.tsv}, is a simple key
matching Ausphon-Lexicon ID numbers to language variety names.

\hypertarget{code}{%
\subsection{Code}\label{code}}

The \emph{R} subdirectory contains the R scripts used to conduct the
analyses in the study. Analysis was performed with the script
\textbf{Aus\_powerlaw.R}, which is called with a single parameter giving
the index of the language to be analyses (between 1 and 168). The script
was submitted as a job batch to the Awoonga high performance computer
cluster at The University of Queensland, Australia. The Awoonga system
has 40 nodes, each consisting of 24 cores (Intel(R) Xeon(R) CPU E5-2670
v3 @ 2.30GHz), with 256 GB of RAM and 300 GB of disk memory,
interconnected by a 10 Gigabit Ethernet network. The operating system is
CentOS version 7 and batch jobs are submitted via PBS Pro software. A
script \textbf{compile\_MLE\_results.R} compiles file many samll results
file generated by\textbf{Aus\_powerlaw.R} into the main results files
described in the next section. The script \textbf{Vuongs\_LRT.R}
performs Vuong's likelihood ratio tests.

The three R scripts are dependent on two R packages, \emph{tidyverse}
and \emph{poweRlaw}, for which we used versions 1.3.0 and 0.76.0
respectively. These packages are both available on CRAN
(cran.r-project.org) and if these are not already installed on the
user's machine, they can be installed via the standard
`install.packages' command in the R console. The scripts are also
dependent on the \emph{data} and \emph{results} subdirectories. As long
as these requirements are satisfied, any user should be able to open and
run the scripts in R software to reproduce the study's analysis and
results. As an alternative to \textbf{Aus\_powerlaw.R} which is called
with a parameter and analyses a single language, we provide
\textbf{Aus\_powerlaw\_all\_languages.R} which analyses all languages
and can be opened in R and run on its own, but be aware that the
bootstrapping procedures may take several days to run on a personal
machine.

\hypertarget{results-files}{%
\subsection{Results files}\label{results-files}}

Results are stored in the \emph{results} subdirectory, and a further
subdirectory within it, \emph{individual\_results}. The script
\textbf{Aus\_powerlaw.R} produces four results files for each individual
language, stored in Rdata format in the \emph{individual\_languages}
directory. The script \textbf{compile\_MLE\_results.R} compiles these
into four main results files in Rdata format, saved in the
\emph{results} directory. Each of those Rdata files contain four list
objects. The four lists are:

\textbf{aus\_dis*}: A list of length 168, where each element in the list
is a `dis*' object (defined in the \emph{poweRlaw} package)---one for
each language variety in our language sample. Each element in the list
is named with the applicable Ausphon-Lexicon lex\_ID. Each dis* object
contains the maximum likelihood estimates of the parameters for a given
distribution for a particular language. In other words, we use the
\emph{poweRlaw} package to fit a particular distribution to the segment
frequencies of each language and save the results for each language as
an element of a list. The `dis*' object classes contain a variety of
other information, such as a copy of all data points and information on
the package version used---see the documentation for the \emph{poweRlaw}
package for details.

\textbf{aus\_dis*\_xmin}: A list of length 168, exactly the same as
above, except an \(x_{min}\) parameter is estimated first using maximum
likelihood and then the distribution is fitted to the remaining
frequency values equal to or above \(x_{min}\).

\textbf{aus\_bootstrap\_*}: A list of length 168, as above. This time,
each element of the list is a `dis*' object which is the result of
running the bootstrap procedure (using the `bootstrap\_p' function in
the \emph{poweRlaw} package). Each `dis*' object includes the output of
each individual bootstrap iteration.

\textbf{aus\_bootstrap\_*\_xmin}: As above, but with the \(x_{min}\)
parameter included.

(replace * with one of `pl', `lnorm', `exp' or `pois')

THe script \textbf{Vuongs\_LRT.R} produces one results file in Rdata
format, saved in the \emph{results} subdirectory. This file,
\textbf{Aus\_Voungs\_LRT.Rdata} contains results of our seven pairwise
likelihood ratio test, in seven objects. One, named
\textbf{lrt\_results\_e\_l}, is the comparion of the exponential and
lognormal distributions without \(x_{min}\), and six named
\textbf{lrt\_results\_xmin\_\emph{a}\_\emph{b}} where \emph{a} and
\emph{b} are each possible combination of e, l and p, comparing the
exponential, lognormal and power law distributions using the \(x_{min}\)
parameter estimated for the \emph{a} distribution.

\hypertarget{guide-to-data-viewer}{%
\subsection{Guide to Data Viewer}\label{guide-to-data-viewer}}

A.4 is a zip file containing an interactive app for visualising phoneme
frequency data for each language. The app was produced in R, using the
package \emph{shiny} \autocite{chang_shiny_2018}. In addition the app
plots lines corresponding to the fit of each candidate distribution and
plots the results of each bootstrapping procedure (including approximate
95\% confidence intervals for each parameter). We plan to host the app
on the Internet, so it can be viewed simply through an Internet browser.
In the meantime, it can be run locally in R. Running the app locally
should be simple and need not require any coding or previous experience
with R software.

Unzipping the file reveals a directory containing an R file,
\textbf{app.R}, and two subdirectories, \emph{data} and \emph{results}.
These two subdirectories are simply copies of the same subdirectories in
A.5 (they are copied here to keep the app self-contained, so it can run
independently of the materials in A.5). To run the app, open the
\textbf{app.R} file in Rstudio and click `Run App'. Alternatively, if
using the regular R console, set the working directory to the location
of \textbf{app.R} and run the command `shiny::runApp()'.

\newpage

\hypertarget{original-wordlist-sources}{%
\section{Original wordlist sources}\label{original-wordlist-sources}}

\textbf{Adnyamathanha}

CHIRILA source: CHIRILA/v2/McEnteeMcKenzie

\fullcite{mcentee_adna-mat-na_1992}

Phonemic normalization: Coda tap normalized as vibrant. Otherwise,
voiced stops, taps and fricatives normalized to lenis obstruents.

\textbf{Alawa}

\fullcite{sharpe_alawa_2001}

\textbf{Amurdak}

\fullcite{handelsmann_towards_1991}

Phonemic normalization: Prelateralized stops normalized as flapped
laterals.

\textbf{Angkamuthi}

\fullcite{crowley_uradhi_1983}

\textbf{Anguthimri}

CHIRILA source: CHIRILA/v1/ASEDA0240

\fullcite{crowley_mbakwithi_1989}

\textbf{Atampaya}

\fullcite{crowley_uradhi_1983}

\textbf{Badimaya}

\fullcite{marmion_badimaya_1995}

Phonemic normalization: Double a normalized to long vowel.

\textbf{Bakanh}

\fullcite{hamilton_pakanh_1997}

\textbf{Bardi}

CHIRILA source: CHIRILA/v1/akl99

\fullcite{aklif_ardiyooloon_1999}

\textbf{Bidyara}

\fullcite{breen_bidyara_1973}

\textbf{Bilinarra}

\fullcite{meakins_bilinarra_2013}

\textbf{Biri}

CHIRILA source: CHIRILA/v1/Terrell

\fullcite{terrill_biri_1999}

\textbf{Bularnu}

\fullcite{breen_bularnu_1988}

\textbf{Bunuba}

\fullcite{kimberley_language_resource_centre_bunuba_2010}

\textbf{Burarra}

CHIRILA source: CHIRILA/v1/Glasgow

\fullcite{glasgow_burarra-gun-nartpa_1994}

\textbf{Butchulla}

\fullcite{bell_sketch_2003}

\textbf{Central Arrernte}

\fullcite{wilkins_mparntwe_nodate}

Phonemic normalization: Labialized consonants normalized to C + w.
Prestopped nasals normalized to stop + nasal sequence. Prepalatalized
consonants normalized to j + C.

\textbf{Dalabon}

\fullcite{evans_first_2004}

\textbf{Dhangu}

\fullcite{zorc_yolngu_2004}

Phonemic normalization: Lenis retroflex stop normalized to retroflex
flap.

\textbf{Dharumbal}

CHIRILA source: CHIRILA/v2/ter02

\fullcite{terrill_dharumbal:_2002}

\textbf{Dhay'yi}

\fullcite{wunungmurra_dhalwangu_1993}

Phonemic normalization: Lenis retroflex stop normalized to retroflex
flap; all other voicing is allophonic.

\textbf{Diyari}

\fullcite{austin_grammar_1981}

Phonemic normalization: Phonetic trill-released stop normalized as stop
+ trill. Otherwise, voiced stops normalized as taps.

\textbf{Djabugay}

\fullcite{robertson_jaabugay_1997}

\textbf{Djapu}

CHIRILA source: CHIRILA/v1/mor83

\fullcite{morphy_djapu_1983}

Phonemic normalization: Lenis retroflex stop normalized to retroflex
flap.

\textbf{Djinang}

CHIRILA source: CHIRILA/v1/ASEDA0009

\fullcite{waters_djinang_1988}

Phonemic normalization: Glottal closure normalized to a segment phoneme.

\textbf{Duungidjawu}

CHIRILA source: CHIRILA/v2/K\&W 04

\fullcite{kite_duungidjawu_2004}

\textbf{Dyirbal}

CHIRILA source: CHIRILA/v1/dix72

\fullcite{dixon_dyirbal_1972}

\textbf{Emmi}

\fullcite{ford_description_1998}

\textbf{Erre}

\fullcite{birch_first_2006}

Phonemic normalization: Double stops normalized as fortis.

\textbf{Gamilaraay}

CHIRILA source: CHIRILA/v1/ash03

\fullcite{ash_gamilaraay_2003}

\textbf{Gangulu}

CHIRILA source: CHIRILA/v1/Terrell

\fullcite{terrill_biri_1999}

\textbf{Gidabal}

CHIRILA source: CHIRILA/v1/cro78

\fullcite{crowley_middle_1978}

\textbf{Gooniyandi}

\fullcite{kimberley_language_resource_centre_gooniyandi_1993}

\textbf{Gugu Badhun}

CHIRILA source: CHIRILA/v1/sut73

\fullcite{sutton_gugu-badhun_1973}

\textbf{Gumbaynggir}

\fullcite{murrbay_aboriginal_and_culture_cooperative_gumbaynggir_2001}

\textbf{Gunya}

CHIRILA source: CHIRILA/v1/dixbla81

\fullcite{breen_margany_1981}

\textbf{Gupapuyngu}

CHIRILA source: CHIRILA/v1/BL

\fullcite{lowe_temporary_1976}

\textbf{Gurindji}

\fullcite{meakins_gurindji_2013}

\textbf{Gurr-Goni}

\fullcite{green_gurr-goni_2015}

Phonemic normalization: Geminate stops normalized to fortis.

\textbf{Guugu Yimidhirr}

\fullcite{haviland_guugu_1979}

\textbf{Guwamu}

CHIRILA source: CHIRILA/v1/Austin 1980

\fullcite{austin_guwamu_1980}

\textbf{Iwaidja}

\fullcite{pym_iwaidja-english_2011}

\textbf{Jaru}

\fullcite{tsunoda_jaru_1981}

Phonemic normalization: iji and uwu normalized as long high vowels.

\textbf{Jawoyn}

\fullcite{merlan_jawoyn-english_2005}

\textbf{Jiwarli}

CHIRILA source: CHIRILA/v2/ASEDA0435

\fullcite{austin_dictionary_nodate-1}

\textbf{Kalkatungu}

CHIRILA source: CHIRILA/v2/ASEDA0205

\fullcite{blake_kalkatungu_1990}

Phonemic normalization: Double short vowels normalized as long.

\textbf{Karajarri}

\fullcite{mckelson_studies_1989}

\textbf{Kariyarra}

\fullcite{smythe_kariyarra_nodate}

\textbf{Kartujarra}

\fullcite{ogrady_gardudjarra_1988}

\textbf{Kija}

CHIRILA source: CHIRILA/v1/bly01

\fullcite{blyth_wangka_2001}

\textbf{Kok Nar}

\fullcite{sommer_koko_nodate}

\textbf{Koko Bera}

\fullcite{black_kokoberrin_2007}

\textbf{Kugu Nganhcara}

CHIRILA source: CHIRILA/v1/ASEDA0021

\fullcite{smith_kugu_1989}

\textbf{Kukatj}

\fullcite{breen_kukatj_1991}

Phonemic normalization: Featureless vowel normalized as schwa.

\textbf{Kukatja}

CHIRILA source: CHIRILA/v1/ASEDA0504

\fullcite{peile_basic_nodate}

\textbf{Kuku Yalanji}

\fullcite{hershberger_kuku-yalanji_1986}

\textbf{Kungkari}

CHIRILA source: CHIRILA/v1/bre90

\fullcite{breen_salvage_1990}

\textbf{Kurrama}

\fullcite{dench_kurrama_nodate}

\textbf{Kurtjar}

CHIRILA source: CHIRILA/v1/ASEDA0026

\fullcite{black_kurtjar_1988}

Phonemic normalization: Retroflex glide\textasciitilde{}tap normalized
as glide.

\textbf{Kuugu Ya'u}

\fullcite{thompson_sand_1988}

\textbf{Lardil}

\fullcite{hale_lardil_1997}

\textbf{Larrakia}

\fullcite{harvey_larrakia_2004}

\textbf{Limilngan}

\fullcite{harvey_grammar_2001}

\textbf{Linngithigh}

\fullcite{hale_linngithigh_1999}

Phonemic normalization: Trill-released stop normalized as stop + trill.
Prenasalized stops normalized to nasal + lenis stop.

\textbf{Malkana}

\fullcite{gargett_salvage_2011}

\textbf{Malyangapa}

\fullcite{hercus_maljangapa-wadigali_1989}

\textbf{Mangala}

\fullcite{mckelson_mangala_1989}

\textbf{Margany}

CHIRILA source: CHIRILA/v1/bre81

\fullcite{breen_margany_1981}

\textbf{Marra}

\fullcite{heath_basic_1981}

\textbf{Martuthunira}

\fullcite{dench_martuthunira_1995}

\textbf{Matngele}

\fullcite{zandvoort_grammar_1999}

\textbf{Mawng}

\fullcite{singer_mawng_2015}

\textbf{Mbabaram}

\fullcite{dixon_mbabaram_1991}

Phonemic normalization: Labialized consonants normalized to C + w. Final
schwa treated as a phoneme.

\textbf{Mengerrdji}

\fullcite{birch_first_2006}

Phonemic normalization: Double stops normalized as fortis.

\textbf{Miriwoong}

\fullcite{kofod_miriwung_1976}

\textbf{Mirniny}

\fullcite{ogrady_mirniny_1988}

\textbf{Mudburra}

\fullcite{nash_mudburra_1988}

\textbf{Murrinh-patha}

\fullcite{street_introduction_1987}

\textbf{Muruwari}

CHIRILA source: CHIRILA/v1/ASEDA0252

\fullcite{oates_muruwari_1992}

\textbf{Nakara}

\fullcite{eather_first_2005}

Phonemic normalization: Geminate stops normalized to fortis.

\textbf{Ngaanyatjarra}

\fullcite{glass_ngaanyatjarra_1988}

\textbf{Ngadjunmaya}

\fullcite{wangka_maya_pilbara_aboriginal_language_centre_ngajumaya_2008}

\textbf{Ngalakgan}

CHIRILA source: CHIRILA/v1/mor83

\fullcite{merlan_ngalakan_1983}

Phonemic normalization: Geminate stops normalized to fortis.

\textbf{Ngamini}

CHIRILA source: CHIRILA/v1/brendn

\fullcite{breen_ngamini_1967}

Phonemic normalization: Phonetic trill-released stop normalized as stop
+ trill. Otherwise, voiced stops normalized as taps.

\textbf{Ngandi}

\fullcite{heath_ngandi_1978}

\textbf{Ngardily}

\fullcite{green_ngardily_1988}

\textbf{Ngarinyin}

\fullcite{coate_ngarinjin-english_1974}

\textbf{Ngarinyman}

\fullcite{jones_ngarinman_2005}

\textbf{Ngarla}

\fullcite{brown_ngarla-english_nodate}

\textbf{Ngarluma}

\fullcite{hale_ngarluma_1989}

\textbf{Ngawun}

CHIRILA source: CHIRILA/v2/BreenMayi

\fullcite{breen_mayi_1981}

\textbf{Ngiyambaa}

CHIRILA source: CHIRILA/v1/don-lex

\fullcite{donaldson_ngiyambaa_1997}

\textbf{Nhanda}

CHIRILA source: CHIRILA/v1/ble01

\fullcite{blevins_nhanda:_2001}

\textbf{Nhangu}

CHIRILA source: CHIRILA/v1/CB-fieldnotes

\fullcite{james_yan-nhangu_2003}

\textbf{Nhirrpi}

CHIRILA source: CHIRILA/v1/bow-nhi

\fullcite{bowern_nhirrpi_1999}

\textbf{Nukunu}

CHIRILA source: CHIRILA/v2/her92

\fullcite{hercus_nukunu_1992}

Phonemic normalization: Voiced retroflex stop normalized to retroflex
tap.

\textbf{Nungali}

\fullcite{bolt_elementary_1971}

\textbf{Nyamal}

\fullcite{burgman_nyamal_2007}

\textbf{Nyangumarta}

\fullcite{geytenbeek_nyangumarta-english_1991}

\textbf{Nyawaygi}

\fullcite{dixon_nyawaygi_1983}

\textbf{Nyikina}

CHIRILA source: CHIRILA/v1/Stokes

\fullcite{stokes_nyikina-english:_nodate}

\textbf{Nyiyaparli}

\fullcite{ogrady_nyiyabali_1988}

\textbf{Ogh Angkula}

\fullcite{sommer_ankula_nodate}

\textbf{Ogh Unyjan}

\fullcite{sommer_ogh_nodate-1}

\textbf{Olkol}

\fullcite{hamilton_uw_1997}

\textbf{Oykangand}

\fullcite{hamilton_uw_1997}

\textbf{Panyjima}

\fullcite{dench_panyjima_1991-1}

\textbf{Patjtjamalh}

\fullcite{ford_batjamalh:_1997}

\textbf{Payungu}

CHIRILA source: CHIRILA/v1/ASEDA0394

\fullcite{austin_payungu_nodate}

\textbf{Pintupi}

\fullcite{hansen_pintupi/luritja_1992}

\textbf{Pitta Pitta}

CHIRILA source: CHIRILA/v1/bla0275

\fullcite{blake_pitta_1990}

\textbf{Purduna}

\fullcite{burgman_burduna_2007}

\textbf{Putijarra}

\fullcite{wangka_maya_pilbara_aboriginal_language_centre_putijarra-english_2004}

\textbf{Rembarrnga}

\fullcite{mckay_rembarrnga_2011}

Phonemic normalization: Geminate stops normalized to fortis.

\textbf{Ritharrngu}

CHIRILA source: CHIRILA/v1/Heath

\fullcite{heath_ritharngu_1976}

\textbf{Southern Paakintyi}

\fullcite{hercus_paakantyi_nodate}

\textbf{Thaayorre}

\fullcite{foote_kuuk_1993}

\textbf{Thalanyji}

CHIRILA source: CHIRILA/v2/ASEDA0437

\fullcite{austin_dictionary_nodate-2}

\textbf{Tharrkari}

\fullcite{austin_dictionary_1992-1}

\textbf{Thaynakwithi}

\fullcite{fletcher_thanakupis_2007}

\textbf{Thirarri}

\fullcite{austin_grammar_1981}

Phonemic normalization: Phonetic trill-released stop normalized as stop
+ trill. Otherwise, voiced stops normalized as taps.

\textbf{Tiwi}

\fullcite{lee_tiwi-english_2013}

Phonemic normalization: r + alveolar normalized as retroflex. Following
Breen 1979, (w)o is normalized as wa.

\textbf{Umpila}

\fullcite{ogrady_umpila_1988}

\textbf{Unggumi}

\fullcite{mcgregor_handbook_1985}

\textbf{Urningangg}

\fullcite{birch_first_2006}

\textbf{Waalubal}

CHIRILA source: CHIRILA/v1/cro78

\fullcite{crowley_middle_1978}

\textbf{Waanyi}

CHIRILA source: CHIRILA/v1/WaanyiDict

\fullcite{laughren_waanyi_2016}

\textbf{Wagiman}

\fullcite{wilson_wagiman_2001}

\textbf{Walmajarri}

\fullcite{hudson_walmajarri_1993}

\textbf{Wambaya}

CHIRILA source: CHIRILA/v1/RN Wambaya 29,269,292; NE NA

\textbf{Wangkatja}

\fullcite{blyth_wangka_2001}

\textbf{Wangkumara}

CHIRILA source: CHIRILA/v1/robnd

\fullcite{robertson_wangkumara_1985}

Phonemic normalization: Double a normalized to long vowel.

\textbf{Wanyjirra}

\fullcite{senge_grammar_2015}

\textbf{Wardaman}

CHIRILA source: CHIRILA/v1/Merlan NA

\textbf{Warlmanpa}

\fullcite{nash_preliminary_1984}

\textbf{Warlpiri}

CHIRILA source: CHIRILA/v2/WarlpiriDict

\fullcite{schwartz_walpiri_1996}

\textbf{Warluwarra}

\fullcite{breen_warluwara_1990}

Phonemic normalization: Prenasalized stops normalized to nasal + lenis
stop. Tense glides normalized to fricatives. Tense lateral normalized to
double lateral.

\textbf{Warndarrang}

CHIRILA source: CHIRILA/v1/hea80

\fullcite{heath_basic_1980-1}

\textbf{Warnman}

CHIRILA source: CHIRILA/v2/ASEDA0334

\fullcite{eidwun_warnman_nodate}

\textbf{Warrgamay}

CHIRILA source: CHIRILA/v1/dixbla81

\fullcite{dixon_wargamay_1981}

\textbf{Warriyangga}

\fullcite{austin_dictionary_nodate-3}

\textbf{Watjarri}

\fullcite{mackman_wajarri_2012}

\textbf{Wemba Wemba}

\fullcite{hercus_wembawemba_1992}

\textbf{Western Arrernte}

\fullcite{breen_introductory_2000}

Phonemic normalization: Labialized consonants normalized to C + w.
Prestopped nasals normalized to stop + nasal sequence. Prepalatalized
consonants normalized to j + C.

\textbf{Western Wakaya}

\fullcite{breen_wakaya_2006}

\textbf{Wik Mungkan}

\fullcite{kilham_wik_2011}

\textbf{Wik-Ngathan}

CHIRILA source: CHIRILA/v2/PS

\fullcite{sutton_wik-ngathan_1995}

\textbf{Wirangu}

\fullcite{hercus_grammar_1999}

Phonemic normalization: Double a normalized to long vowel.

\textbf{Wiri}

\fullcite{terrill_biri_1999}

\textbf{Worrorra}

\fullcite{mcgregor_handbook_1985}

\textbf{Wotjobaluk}

\fullcite{hercus_wergaia_nodate}

\textbf{Wubuy}

CHIRILA source: CHIRILA/v1/Nunggubuyu Flora Fauna

\fullcite{heath_nunggubuyu_1976}

Phonemic normalization: Morphophonemic w1, w2 represented as their
phonemic realizations w,b,k.

\textbf{Yadhaykenu}

\fullcite{crowley_uradhi_1983}

\textbf{Yalarnnga}

CHIRILA source: CHIRILA/v1/ASEDA0204

\fullcite{breen_yalarnnga_nodate}

\textbf{Yandruwandha}

CHIRILA source: CHIRILA/v1/breyandr

\fullcite{breen_innamincka_2004}

Phonemic normalization: Trill-released stop normalized as stop + trill.
Prestopped laterals normalized to stop + lateral sequence.

\textbf{Yanyuwa}

\fullcite{bradley_yanyuwa_nodate}

Phonemic normalization: Prenasalized stops normalized to nasal + stop
sequence.

\textbf{Yarluyandi}

CHIRILA source: CHIRILA/v1/ASEDA0251

\fullcite{hercus_yarluyandi_nodate}

\textbf{Yawijibaya}

\fullcite{mcgregor_handbook_1985}

\textbf{Yaygir}

CHIRILA source: CHIRILA/v1/morelli2011

\fullcite{morelli_yaygirr_2012}

\textbf{Yidiny}

CHIRILA source: CHIRILA/v2/dix91

\fullcite{dixon_words_1991}

\textbf{Yindjibarndi}

\fullcite{anderson_yindjibarndi_nodate}

\textbf{Yinhawangka}

\fullcite{wangka_maya_pilbara_aboriginal_language_centre_yinhawangka_2008}

\textbf{Yintyingka}

\fullcite{verstraete_grammar_2015}

\textbf{Yir Yoront}

\fullcite{alpher_yir-yoront_1991}

\textbf{Yorta Yorta}

CHIRILA source: CHIRILA/v1/bowmor99

\fullcite{bowe_yorta_1999}

\textbf{Yulparija}

\fullcite{mckelson_yulparija_1989}

\textbf{Yuwaalaraay}

CHIRILA source: CHIRILA/v1/ash03

\fullcite{ash_gamilaraay_2003}

\textbf{Yuwaliyaay}

CHIRILA source: CHIRILA/v1/ash03

\fullcite{ash_gamilaraay_2003}

\newpage

\hypertarget{a.3.-tables-of-results}{%
\subsection{A.3. Tables of results}\label{a.3.-tables-of-results}}

The tables below give the results of maximum likelihood estimation for
each distribution type and each language variety. Each table contains
estimated parameter values, goodness-of-fit (Kolmogorov-Smirnof
statistic) and the \(p\) value from the bootstrapping procedure.

All tables contain a `\textbf{lex ID}' column giving the numerical
identifier for the language variety in the Ausphonlex database and a
`\textbf{language variety}' column giving the common name identifier in
the Ausphonlex database. Tables A.3.1--A.3.8 all contain a `\(p\)'
column giving the \(p\) value estimated via the bootstrapping procedure
and a `\textbf{goodness-of-fit}' column giving the Kolmogorov-Smirnov
statistic, which quantifies the distance between the fitted distribution
and the observed distribution of the data. The rows of each table are
ordered by the goodness-of-fit, from best-fitting to worst-fitting.

Table A.3.1 reports results for the power law distribution fitted to
each language's full segmental inventory (with no \(x_{min}\)
parameter). It gives the maximum likelihood estimate of the shape
parameter, \(\alpha\) and the number of contrastive phonological
segments in that language variety's segmental inventory (in the
`inventory size' column).

Table A.3.2 reports results for the power law distribution with the
addition of the \(x_{min}\) parameter. Thus, in addition to the shape
parameter, \(\alpha\), Table A.3.2 also gives the maximum likelihood
estimate of \(x_{min}\) for each language. The \(x_{min}\) parameter is
a count number whereby segments that appear fewer than \(x_{min}\) times
in the wordlist are disregarded. To make the figure comparable between
languages, here we report \(x_{min}\) as a fraction of the total number
of segments in a language's wordlist. The original \(x_{min}\) values in
count form can be accessed via the results files in A.5. The column
`\(n\) \textbf{segments}' reports the number of unique phonemes in that
language's segmental inventory that are at or above \(x_{min}\) in
frequency (in other words, the number of observations to which the
distribution has been fitted) and `\textbf{frac. of inventory}' gives
the fraction of that language's total segmental inventory to which the
distribution has been fitted.

Table A.3.3 reports results for the lognormal distribution fitted to
each language's full segmental inventory. Maximum likelihood estimates
for the \(log\) mean and \(log\) SD parameters are given. Table A.3.4
reports results for the lognormal distribution with an \(x_{min}\)
parameter included.

Tables A.3.5 and A.3.6 cover the exponential distribution, with and
without \(x_{min}\) respectively. They report maximum likelihood
estimates for the \(\lambda\) shape parameter. Likewise, Tables A.3.7
and A.3.8 cover the Poisson distribution, with and without \(x_{min}\).
The shape parameter for the Poisson distribution is also termed
\(\lambda\).

Lastly, Table A.3.9 reports results of Vuong's (1989) likelihood ratio
test. The test statistic, \(R\), is the ratio of the log likelihood of
the data given an exponential distribution model versus a lognormal
distribution model (with no \(x_{min}\) parameters). The sign of \(R\)
indicates which of the two models fits best (positive values indicate
the exponential distribution is preferred, negative values for the
lognormal distribution). Rows are ordered by \(R\). The `\(p\)' column
gives a one-sided \(p\) value indicating whether the exponential
distribution is favoured over the lognormal distribution to a
statistically significant degree. The `\textbf{signif.}' column
indicates whether the \(p\) value is considered statistically
significant after Bonferroni correction.

\newpage

\textbf{Table A.3.1. Power law distribution.}

\begin{longtable}[]{@{}rlrrrr@{}}
\toprule
\textbf{lex ID} & \textbf{language variety} & \(\alpha\) &
\textbf{inventory size} & \(p\) &
\textbf{goodness-of-fit}\tabularnewline
\midrule
\endhead
865 & Diyari & 1.69 & 25 & 0.25 & 0.15\tabularnewline
866 & Thirarri & 1.69 & 25 & 0.16 & 0.17\tabularnewline
170 & Wik-Ngathan & 1.67 & 28 & 0.07 & 0.19\tabularnewline
162 & Adnyamathanha & 1.72 & 29 & 0.04 & 0.20\tabularnewline
962 & Gunya & 1.41 & 31 & 0.03 & 0.21\tabularnewline
540 & Ngiyambaa & 1.57 & 21 & 0.06 & 0.22\tabularnewline
592 & Muruwari & 1.64 & 25 & 0.04 & 0.22\tabularnewline
821 & Gumbaynggir & 2.18 & 19 & 0.05 & 0.23\tabularnewline
939 & Unggumi & 1.38 & 30 & 0.01 & 0.25\tabularnewline
940 & Yawijibaya & 1.44 & 23 & 0.02 & 0.25\tabularnewline
656 & Kuugu Ya'u & 1.78 & 21 & 0.03 & 0.25\tabularnewline
930 & Purduna & 1.47 & 26 & 0.01 & 0.26\tabularnewline
787 & Jawoyn & 1.66 & 27 & 0.01 & 0.26\tabularnewline
1043 & Mbabaram & 1.44 & 27 & 0.00 & 0.26\tabularnewline
62 & Dhay'yi & 1.55 & 26 & 0.01 & 0.26\tabularnewline
958 & Margany & 1.35 & 30 & 0.00 & 0.27\tabularnewline
1042 & Thaayorre & 1.51 & 26 & 0.01 & 0.27\tabularnewline
949 & Kok Nar & 1.56 & 21 & 0.01 & 0.27\tabularnewline
89 & Bunuba & 1.37 & 24 & 0.02 & 0.27\tabularnewline
977 & Warndarrang & 1.88 & 19 & 0.01 & 0.27\tabularnewline
985 & Yaygir & 1.64 & 20 & 0.02 & 0.28\tabularnewline
13 & Dyirbal & 1.84 & 16 & 0.03 & 0.28\tabularnewline
1003 & Murrinh-patha & 1.46 & 25 & 0.00 & 0.28\tabularnewline
1008 & Yuwaalaraay & 1.48 & 21 & 0.02 & 0.28\tabularnewline
927 & Tiwi & 1.49 & 20 & 0.03 & 0.28\tabularnewline
979 & Mawng & 1.52 & 22 & 0.01 & 0.29\tabularnewline
983 & Nhangu & 1.50 & 31 & 0.00 & 0.29\tabularnewline
495 & Nyikina & 1.59 & 20 & 0.01 & 0.29\tabularnewline
1032 & Kuku Yalanji & 1.91 & 16 & 0.02 & 0.29\tabularnewline
740 & Kugu Nganhcara & 1.41 & 30 & 0.00 & 0.29\tabularnewline
853 & Lardil & 1.47 & 25 & 0.01 & 0.29\tabularnewline
30 & Duungidjawu & 1.52 & 23 & 0.00 & 0.30\tabularnewline
968 & Ogh Angkula & 1.58 & 24 & 0.00 & 0.30\tabularnewline
1002 & Yintyingka & 1.42 & 26 & 0.00 & 0.30\tabularnewline
63 & Dharumbal & 1.43 & 20 & 0.01 & 0.30\tabularnewline
771 & Kalkatungu & 1.50 & 26 & 0.00 & 0.30\tabularnewline
412 & Ritharrngu & 1.52 & 31 & 0.00 & 0.30\tabularnewline
475 & Southern Paakintyi & 1.49 & 27 & 0.00 & 0.30\tabularnewline
835 & Gugu Badhun & 1.65 & 17 & 0.01 & 0.30\tabularnewline
1007 & Yuwaliyaay & 1.43 & 21 & 0.01 & 0.31\tabularnewline
1018 & Djapu & 1.55 & 26 & 0.00 & 0.31\tabularnewline
77 & Dhangu & 1.45 & 26 & 0.00 & 0.31\tabularnewline
518 & Yarluyandi & 1.38 & 23 & 0.00 & 0.31\tabularnewline
807 & Gupapuyngu & 1.53 & 31 & 0.00 & 0.31\tabularnewline
101 & Butchulla & 1.29 & 24 & 0.01 & 0.32\tabularnewline
1012 & Warrgamay & 1.43 & 19 & 0.01 & 0.32\tabularnewline
929 & Wanyjirra & 1.60 & 21 & 0.00 & 0.32\tabularnewline
919 & Angkamuthi & 1.33 & 26 & 0.00 & 0.32\tabularnewline
1009 & Gamilaraay & 1.47 & 21 & 0.01 & 0.32\tabularnewline
427 & Yidiny & 1.58 & 19 & 0.01 & 0.32\tabularnewline
611 & Anguthimri & 1.26 & 34 & 0.00 & 0.32\tabularnewline
978 & Wotjobaluk & 1.56 & 19 & 0.00 & 0.32\tabularnewline
642 & Mangala & 1.35 & 22 & 0.01 & 0.32\tabularnewline
400 & Thalanyji & 1.35 & 26 & 0.00 & 0.33\tabularnewline
200 & Western Arrernte & 1.49 & 25 & 0.00 & 0.33\tabularnewline
91 & Bularnu & 1.27 & 30 & 0.00 & 0.33\tabularnewline
554 & Ngarluma & 1.54 & 23 & 0.00 & 0.33\tabularnewline
1029 & Martuthunira & 1.34 & 26 & 0.00 & 0.34\tabularnewline
546 & Yanyuwa & 1.37 & 23 & 0.01 & 0.34\tabularnewline
697 & Kurrama & 1.33 & 27 & 0.00 & 0.34\tabularnewline
926 & Limilngan & 1.28 & 24 & 0.00 & 0.34\tabularnewline
265 & Wardaman & 1.48 & 22 & 0.00 & 0.34\tabularnewline
252 & Warlmanpa & 1.29 & 28 & 0.00 & 0.34\tabularnewline
443 & Payungu & 1.32 & 26 & 0.00 & 0.34\tabularnewline
572 & Ngamini & 1.40 & 23 & 0.00 & 0.34\tabularnewline
790 & Jaru & 1.39 & 23 & 0.00 & 0.34\tabularnewline
105 & Bardi & 1.56 & 24 & 0.00 & 0.35\tabularnewline
946 & Kurtjar & 1.51 & 28 & 0.00 & 0.35\tabularnewline
1040 & Ngarinyin & 1.16 & 27 & 0.05 & 0.35\tabularnewline
1016 & Tharrkari & 1.31 & 32 & 0.00 & 0.35\tabularnewline
911 & Nyawaygi & 1.46 & 18 & 0.00 & 0.35\tabularnewline
269 & Wangkumara & 1.31 & 30 & 0.00 & 0.35\tabularnewline
925 & Larrakia & 1.22 & 29 & 0.00 & 0.35\tabularnewline
778 & Jiwarli & 1.37 & 26 & 0.00 & 0.35\tabularnewline
237 & Warluwarra & 1.20 & 33 & 0.00 & 0.35\tabularnewline
752 & Kija & 1.28 & 24 & 0.01 & 0.35\tabularnewline
363 & Yir Yoront & 1.42 & 26 & 0.00 & 0.35\tabularnewline
5 & Gangulu & 1.39 & 18 & 0.00 & 0.35\tabularnewline
1026 & Gidabal & 1.46 & 20 & 0.00 & 0.35\tabularnewline
928 & Bakanh & 1.30 & 26 & 0.00 & 0.35\tabularnewline
1031 & Ngadjunmaya & 1.26 & 25 & 0.00 & 0.36\tabularnewline
204 & Wemba Wemba & 1.44 & 22 & 0.00 & 0.36\tabularnewline
921 & Gurr-Goni & 1.39 & 27 & 0.00 & 0.36\tabularnewline
81 & Dalabon & 1.31 & 29 & 0.00 & 0.36\tabularnewline
631 & Yalarnnga & 1.37 & 24 & 0.00 & 0.36\tabularnewline
963 & Kungkari & 1.34 & 24 & 0.00 & 0.36\tabularnewline
800 & Guwamu & 1.30 & 21 & 0.00 & 0.36\tabularnewline
964 & Olkol & 1.19 & 31 & 0.00 & 0.36\tabularnewline
1001 & Ngandi & 1.20 & 34 & 0.00 & 0.36\tabularnewline
1025 & Waalubal & 1.43 & 20 & 0.00 & 0.36\tabularnewline
1006 & Central Arrernte & 1.52 & 25 & 0.00 & 0.36\tabularnewline
996 & Emmi & 1.31 & 31 & 0.00 & 0.36\tabularnewline
965 & Oykangand & 1.22 & 31 & 0.00 & 0.36\tabularnewline
982 & Nhirrpi & 1.25 & 30 & 0.00 & 0.36\tabularnewline
12 & Erre & 1.23 & 27 & 0.00 & 0.36\tabularnewline
847 & Ngalakgan & 1.31 & 27 & 0.00 & 0.36\tabularnewline
957 & Ngaanyatjarra & 1.52 & 23 & 0.00 & 0.37\tabularnewline
94 & Biri & 1.39 & 18 & 0.00 & 0.37\tabularnewline
934 & Urningangg & 1.23 & 28 & 0.00 & 0.37\tabularnewline
417 & Yindjibarndi & 1.49 & 25 & 0.00 & 0.37\tabularnewline
943 & Pintupi & 1.44 & 23 & 0.00 & 0.37\tabularnewline
905 & Malkana & 1.31 & 25 & 0.00 & 0.37\tabularnewline
288 & Wangkatja & 1.48 & 23 & 0.00 & 0.37\tabularnewline
519 & Nukunu & 1.31 & 28 & 0.00 & 0.37\tabularnewline
849 & Waanyi & 1.30 & 20 & 0.01 & 0.37\tabularnewline
945 & Wiri & 1.38 & 18 & 0.00 & 0.37\tabularnewline
1023 & Wubuy & 1.30 & 26 & 0.00 & 0.38\tabularnewline
118 & Badimaya & 1.30 & 24 & 0.00 & 0.38\tabularnewline
38 & Djabugay & 1.32 & 19 & 0.00 & 0.38\tabularnewline
31 & Djinang & 1.36 & 25 & 0.00 & 0.38\tabularnewline
838 & Gooniyandi & 1.34 & 23 & 0.00 & 0.38\tabularnewline
914 & Yinhawangka & 1.27 & 26 & 0.00 & 0.38\tabularnewline
744 & Koko Bera & 1.55 & 21 & 0.00 & 0.38\tabularnewline
618 & Mirniny & 1.23 & 25 & 0.00 & 0.38\tabularnewline
856 & Patjtjamalh & 1.20 & 27 & 0.00 & 0.38\tabularnewline
935 & Rembarrnga & 1.38 & 28 & 0.00 & 0.39\tabularnewline
922 & Nakara & 1.38 & 26 & 0.00 & 0.39\tabularnewline
852 & Gurindji & 1.27 & 23 & 0.01 & 0.39\tabularnewline
845 & Iwaidja & 1.38 & 23 & 0.00 & 0.39\tabularnewline
857 & Amurdak & 1.23 & 24 & 0.00 & 0.39\tabularnewline
621 & Mengerrdji & 1.22 & 26 & 0.00 & 0.39\tabularnewline
848 & Wagiman & 1.30 & 27 & 0.00 & 0.39\tabularnewline
1011 & Yorta Yorta & 1.23 & 24 & 0.00 & 0.40\tabularnewline
228 & Warriyangga & 1.23 & 26 & 0.00 & 0.40\tabularnewline
901 & Guugu Yimidhirr & 1.46 & 21 & 0.00 & 0.40\tabularnewline
952 & Ngawun & 1.23 & 22 & 0.00 & 0.40\tabularnewline
762 & Kariyarra & 1.27 & 24 & 0.00 & 0.40\tabularnewline
760 & Kartujarra & 1.28 & 23 & 0.00 & 0.41\tabularnewline
606 & Mudburra & 1.23 & 23 & 0.00 & 0.41\tabularnewline
85 & Burarra & 1.44 & 26 & 0.00 & 0.41\tabularnewline
534 & Nhanda & 1.22 & 33 & 0.00 & 0.41\tabularnewline
565 & Ngarinyman & 1.23 & 23 & 0.00 & 0.41\tabularnewline
1024 & Ngardily & 1.35 & 22 & 0.00 & 0.41\tabularnewline
242 & Warlpiri & 1.37 & 24 & 0.00 & 0.41\tabularnewline
1021 & Watjarri & 1.29 & 26 & 0.00 & 0.41\tabularnewline
433 & Pitta Pitta & 1.24 & 25 & 0.00 & 0.41\tabularnewline
923 & Matngele & 1.20 & 25 & 0.00 & 0.42\tabularnewline
917 & Nyamal & 1.19 & 24 & 0.00 & 0.42\tabularnewline
967 & Thaynakwithi & 1.22 & 32 & 0.00 & 0.42\tabularnewline
1030 & Putijarra & 1.18 & 25 & 0.00 & 0.42\tabularnewline
462 & Panyjima & 1.21 & 25 & 0.00 & 0.42\tabularnewline
99 & Bidyara & 1.31 & 19 & 0.00 & 0.42\tabularnewline
851 & Bilinarra & 1.24 & 23 & 0.00 & 0.42\tabularnewline
920 & Yadhaykenu & 1.26 & 25 & 0.00 & 0.42\tabularnewline
645 & Malyangapa & 1.25 & 25 & 0.00 & 0.43\tabularnewline
117 & Wirangu & 1.32 & 23 & 0.00 & 0.43\tabularnewline
734 & Kukatja & 1.33 & 23 & 0.00 & 0.43\tabularnewline
598 & Yandruwandha & 1.20 & 30 & 0.00 & 0.43\tabularnewline
493 & Nyiyaparli & 1.24 & 22 & 0.00 & 0.43\tabularnewline
1019 & Walmajarri & 1.21 & 23 & 0.00 & 0.43\tabularnewline
941 & Wambaya & 1.17 & 23 & 0.00 & 0.44\tabularnewline
650 & Linngithigh & 1.22 & 27 & 0.00 & 0.44\tabularnewline
737 & Kukatj & 1.23 & 25 & 0.00 & 0.44\tabularnewline
305 & Western Wakaya & 1.19 & 26 & 0.00 & 0.44\tabularnewline
563 & Ngarla & 1.21 & 23 & 0.00 & 0.45\tabularnewline
377 & Umpila & 1.25 & 22 & 0.00 & 0.45\tabularnewline
910 & Nungali & 1.38 & 16 & 0.00 & 0.45\tabularnewline
767 & Karajarri & 1.20 & 21 & 0.00 & 0.46\tabularnewline
918 & Atampaya & 1.21 & 25 & 0.00 & 0.46\tabularnewline
113 & Yulparija & 1.19 & 23 & 0.00 & 0.46\tabularnewline
966 & Wik Mungkan & 1.22 & 26 & 0.00 & 0.46\tabularnewline
232 & Warnman & 1.25 & 23 & 0.00 & 0.47\tabularnewline
841 & Worrorra & 1.23 & 25 & 0.00 & 0.47\tabularnewline
972 & Ogh Unyjan & 1.21 & 25 & 0.00 & 0.47\tabularnewline
915 & Alawa & 1.30 & 21 & 0.00 & 0.48\tabularnewline
620 & Miriwoong & 1.17 & 20 & 0.00 & 0.51\tabularnewline
863 & Marra & 1.18 & 20 & 0.00 & 0.52\tabularnewline
507 & Nyangumarta & 1.23 & 21 & 0.00 & 0.53\tabularnewline
\bottomrule
\end{longtable}

\newpage

\textbf{Table A.3.2. Power law distribution with \(x_{min}\).}

\begin{longtable}[]{@{}rlrrrrrr@{}}
\toprule
\textbf{lex ID} & \textbf{language variety} & \(\alpha\) & \(x_{min}\) &
\(n\) \textbf{segments} & \textbf{frac. of inventory} & \(p\) &
\textbf{goodness-of-fit}\tabularnewline
\midrule
\endhead
919 & Angkamuthi & 2.39 & 99 & 16 & 0.62 & 0.99 & 0.08\tabularnewline
1006 & Central Arrernte & 2.32 & 158 & 12 & 0.48 & 0.98 &
0.09\tabularnewline
762 & Kariyarra & 2.54 & 54 & 18 & 0.75 & 0.97 & 0.09\tabularnewline
288 & Wangkatja & 2.25 & 240 & 19 & 0.83 & 0.97 & 0.09\tabularnewline
400 & Thalanyji & 2.33 & 85 & 18 & 0.69 & 0.95 & 0.09\tabularnewline
228 & Warriyangga & 2.37 & 47 & 15 & 0.58 & 0.95 & 0.09\tabularnewline
972 & Ogh Unyjan & 3.03 & 74 & 15 & 0.60 & 0.97 & 0.09\tabularnewline
1024 & Ngardily & 2.32 & 56 & 17 & 0.77 & 0.95 & 0.09\tabularnewline
507 & Nyangumarta & 2.31 & 178 & 19 & 0.90 & 0.89 & 0.10\tabularnewline
845 & Iwaidja & 2.76 & 393 & 13 & 0.57 & 0.98 & 0.10\tabularnewline
778 & Jiwarli & 2.34 & 147 & 17 & 0.65 & 0.91 & 0.10\tabularnewline
1030 & Putijarra & 2.54 & 171 & 17 & 0.68 & 0.89 & 0.10\tabularnewline
563 & Ngarla & 2.42 & 193 & 17 & 0.74 & 0.90 & 0.10\tabularnewline
606 & Mudburra & 2.71 & 191 & 11 & 0.48 & 0.97 & 0.10\tabularnewline
170 & Wik-Ngathan & 3.79 & 249 & 12 & 0.43 & 0.97 & 0.11\tabularnewline
760 & Kartujarra & 2.35 & 147 & 12 & 0.52 & 0.94 & 0.11\tabularnewline
946 & Kurtjar & 3.36 & 189 & 16 & 0.57 & 0.90 & 0.11\tabularnewline
1023 & Wubuy & 2.46 & 200 & 14 & 0.54 & 0.93 & 0.11\tabularnewline
1003 & Murrinh-patha & 3.24 & 101 & 12 & 0.48 & 0.95 &
0.11\tabularnewline
921 & Gurr-Goni & 2.83 & 367 & 15 & 0.56 & 0.91 & 0.11\tabularnewline
914 & Yinhawangka & 2.26 & 120 & 20 & 0.77 & 0.75 & 0.11\tabularnewline
113 & Yulparija & 2.39 & 352 & 13 & 0.57 & 0.93 & 0.11\tabularnewline
963 & Kungkari & 2.38 & 29 & 15 & 0.62 & 0.83 & 0.11\tabularnewline
985 & Yaygir & 3.31 & 234 & 12 & 0.60 & 0.95 & 0.11\tabularnewline
925 & Larrakia & 2.99 & 203 & 9 & 0.31 & 0.98 & 0.11\tabularnewline
1019 & Walmajarri & 2.52 & 740 & 16 & 0.70 & 0.86 & 0.11\tabularnewline
162 & Adnyamathanha & 2.40 & 206 & 18 & 0.62 & 0.76 &
0.11\tabularnewline
917 & Nyamal & 2.58 & 175 & 13 & 0.54 & 0.91 & 0.12\tabularnewline
767 & Karajarri & 2.67 & 433 & 11 & 0.52 & 0.93 & 0.12\tabularnewline
12 & Erre & 3.45 & 102 & 11 & 0.41 & 0.95 & 0.12\tabularnewline
957 & Ngaanyatjarra & 2.34 & 249 & 19 & 0.83 & 0.74 &
0.12\tabularnewline
519 & Nukunu & 2.19 & 31 & 19 & 0.68 & 0.54 & 0.12\tabularnewline
967 & Thaynakwithi & 3.11 & 112 & 13 & 0.41 & 0.85 & 0.12\tabularnewline
117 & Wirangu & 2.48 & 78 & 13 & 0.57 & 0.88 & 0.12\tabularnewline
1040 & Ngarinyin & 3.34 & 1922 & 13 & 0.48 & 0.92 & 0.12\tabularnewline
592 & Muruwari & 2.35 & 184 & 15 & 0.60 & 0.82 & 0.12\tabularnewline
475 & Southern Paakintyi & 1.80 & 59 & 25 & 0.93 & 0.42 &
0.12\tabularnewline
849 & Waanyi & 2.70 & 341 & 12 & 0.60 & 0.91 & 0.12\tabularnewline
943 & Pintupi & 2.29 & 636 & 18 & 0.78 & 0.68 & 0.12\tabularnewline
852 & Gurindji & 2.76 & 1235 & 11 & 0.48 & 0.93 & 0.12\tabularnewline
656 & Kuugu Ya'u & 2.50 & 168 & 15 & 0.71 & 0.77 & 0.12\tabularnewline
91 & Bularnu & 1.98 & 43 & 22 & 0.73 & 0.48 & 0.12\tabularnewline
929 & Wanyjirra & 2.66 & 176 & 13 & 0.62 & 0.84 & 0.12\tabularnewline
1008 & Yuwaalaraay & 4.30 & 533 & 10 & 0.48 & 0.96 & 0.12\tabularnewline
631 & Yalarnnga & 2.45 & 98 & 14 & 0.58 & 0.80 & 0.13\tabularnewline
77 & Dhangu & 2.40 & 53 & 17 & 0.65 & 0.65 & 0.13\tabularnewline
740 & Kugu Nganhcara & 3.17 & 107 & 10 & 0.33 & 0.86 &
0.13\tabularnewline
265 & Wardaman & 2.72 & 337 & 15 & 0.68 & 0.74 & 0.13\tabularnewline
905 & Malkana & 2.54 & 49 & 13 & 0.52 & 0.70 & 0.13\tabularnewline
565 & Ngarinyman & 2.53 & 291 & 12 & 0.52 & 0.84 & 0.13\tabularnewline
821 & Gumbaynggir & 2.94 & 70 & 14 & 0.74 & 0.70 & 0.13\tabularnewline
982 & Nhirrpi & 2.63 & 43 & 15 & 0.50 & 0.66 & 0.13\tabularnewline
857 & Amurdak & 2.69 & 88 & 11 & 0.46 & 0.86 & 0.13\tabularnewline
572 & Ngamini & 2.45 & 176 & 11 & 0.48 & 0.90 & 0.13\tabularnewline
863 & Marra & 2.73 & 180 & 12 & 0.60 & 0.82 & 0.13\tabularnewline
204 & Wemba Wemba & 2.95 & 264 & 13 & 0.59 & 0.80 & 0.13\tabularnewline
865 & Diyari & 2.24 & 43 & 13 & 0.52 & 0.58 & 0.13\tabularnewline
81 & Dalabon & 3.22 & 681 & 15 & 0.52 & 0.65 & 0.13\tabularnewline
598 & Yandruwandha & 2.38 & 170 & 10 & 0.33 & 0.85 & 0.13\tabularnewline
866 & Thirarri & 2.24 & 43 & 13 & 0.52 & 0.59 & 0.13\tabularnewline
38 & Djabugay & 3.01 & 269 & 10 & 0.53 & 0.91 & 0.13\tabularnewline
952 & Ngawun & 2.50 & 59 & 12 & 0.55 & 0.79 & 0.13\tabularnewline
940 & Yawijibaya & 2.88 & 57 & 12 & 0.52 & 0.77 & 0.13\tabularnewline
650 & Linngithigh & 2.75 & 68 & 17 & 0.63 & 0.51 & 0.13\tabularnewline
493 & Nyiyaparli & 2.59 & 48 & 12 & 0.55 & 0.75 & 0.13\tabularnewline
621 & Mengerrdji & 2.97 & 85 & 13 & 0.50 & 0.75 & 0.13\tabularnewline
85 & Burarra & 2.45 & 380 & 18 & 0.69 & 0.42 & 0.13\tabularnewline
31 & Djinang & 2.29 & 319 & 18 & 0.72 & 0.48 & 0.14\tabularnewline
958 & Margany & 2.49 & 50 & 14 & 0.47 & 0.68 & 0.14\tabularnewline
744 & Koko Bera & 4.17 & 375 & 9 & 0.43 & 0.87 & 0.14\tabularnewline
1012 & Warrgamay & 2.49 & 169 & 13 & 0.68 & 0.77 & 0.14\tabularnewline
966 & Wik Mungkan & 2.54 & 671 & 16 & 0.62 & 0.57 & 0.14\tabularnewline
101 & Butchulla & 2.75 & 85 & 15 & 0.62 & 0.63 & 0.14\tabularnewline
996 & Emmi & 2.60 & 53 & 14 & 0.45 & 0.47 & 0.14\tabularnewline
62 & Dhay'yi & 2.25 & 149 & 17 & 0.65 & 0.53 & 0.14\tabularnewline
848 & Wagiman & 2.93 & 271 & 15 & 0.56 & 0.64 & 0.14\tabularnewline
901 & Guugu Yimidhirr & 2.71 & 47 & 15 & 0.71 & 0.60 &
0.14\tabularnewline
734 & Kukatja & 2.31 & 742 & 11 & 0.48 & 0.74 & 0.14\tabularnewline
1011 & Yorta Yorta & 2.91 & 84 & 9 & 0.38 & 0.86 & 0.14\tabularnewline
915 & Alawa & 2.70 & 521 & 14 & 0.67 & 0.65 & 0.14\tabularnewline
554 & Ngarluma & 2.39 & 132 & 18 & 0.78 & 0.49 & 0.14\tabularnewline
841 & Worrorra & 2.65 & 65 & 12 & 0.48 & 0.57 & 0.14\tabularnewline
232 & Warnman & 2.21 & 126 & 17 & 0.74 & 0.40 & 0.14\tabularnewline
807 & Gupapuyngu & 2.18 & 212 & 24 & 0.77 & 0.27 & 0.14\tabularnewline
443 & Payungu & 2.31 & 84 & 19 & 0.73 & 0.43 & 0.14\tabularnewline
968 & Ogh Angkula & 3.83 & 124 & 11 & 0.46 & 0.78 & 0.14\tabularnewline
242 & Warlpiri & 2.22 & 718 & 18 & 0.75 & 0.41 & 0.14\tabularnewline
1029 & Martuthunira & 2.55 & 170 & 15 & 0.58 & 0.59 &
0.14\tabularnewline
928 & Bakanh & 2.65 & 78 & 16 & 0.62 & 0.51 & 0.14\tabularnewline
1002 & Yintyingka & 2.38 & 60 & 16 & 0.62 & 0.54 & 0.14\tabularnewline
851 & Bilinarra & 2.29 & 240 & 17 & 0.74 & 0.51 & 0.14\tabularnewline
930 & Purduna & 2.55 & 112 & 15 & 0.58 & 0.60 & 0.14\tabularnewline
1032 & Kuku Yalanji & 2.45 & 334 & 15 & 0.94 & 0.62 &
0.14\tabularnewline
642 & Mangala & 2.67 & 296 & 11 & 0.50 & 0.73 & 0.14\tabularnewline
377 & Umpila & 2.52 & 129 & 15 & 0.68 & 0.61 & 0.14\tabularnewline
534 & Nhanda & 2.33 & 53 & 20 & 0.61 & 0.27 & 0.14\tabularnewline
433 & Pitta Pitta & 2.22 & 82 & 16 & 0.64 & 0.48 & 0.14\tabularnewline
89 & Bunuba & 2.81 & 141 & 13 & 0.54 & 0.70 & 0.14\tabularnewline
99 & Bidyara & 2.25 & 107 & 15 & 0.79 & 0.57 & 0.14\tabularnewline
1031 & Ngadjunmaya & 2.58 & 194 & 8 & 0.32 & 0.77 & 0.14\tabularnewline
5 & Gangulu & 2.91 & 162 & 7 & 0.39 & 0.91 & 0.14\tabularnewline
941 & Wambaya & 2.14 & 221 & 16 & 0.70 & 0.46 & 0.14\tabularnewline
518 & Yarluyandi & 2.47 & 61 & 12 & 0.52 & 0.63 & 0.14\tabularnewline
835 & Gugu Badhun & 2.61 & 102 & 12 & 0.71 & 0.70 & 0.15\tabularnewline
462 & Panyjima & 2.23 & 68 & 14 & 0.56 & 0.44 & 0.15\tabularnewline
697 & Kurrama & 2.22 & 101 & 17 & 0.63 & 0.38 & 0.15\tabularnewline
618 & Mirniny & 2.47 & 70 & 9 & 0.36 & 0.67 & 0.15\tabularnewline
918 & Atampaya & 2.48 & 80 & 13 & 0.52 & 0.48 & 0.15\tabularnewline
63 & Dharumbal & 3.01 & 158 & 8 & 0.40 & 0.87 & 0.15\tabularnewline
771 & Kalkatungu & 1.97 & 114 & 21 & 0.81 & 0.21 & 0.15\tabularnewline
269 & Wangkumara & 1.93 & 47 & 24 & 0.80 & 0.16 & 0.15\tabularnewline
200 & Western Arrernte & 2.81 & 81 & 9 & 0.36 & 0.70 &
0.15\tabularnewline
979 & Mawng & 2.80 & 723 & 11 & 0.50 & 0.69 & 0.15\tabularnewline
237 & Warluwarra & 2.33 & 161 & 14 & 0.42 & 0.47 & 0.15\tabularnewline
417 & Yindjibarndi & 2.30 & 94 & 18 & 0.72 & 0.29 & 0.15\tabularnewline
1021 & Watjarri & 2.33 & 129 & 19 & 0.73 & 0.23 & 0.15\tabularnewline
1016 & Tharrkari & 2.56 & 60 & 13 & 0.41 & 0.40 & 0.15\tabularnewline
1007 & Yuwaliyaay & 4.67 & 627 & 9 & 0.43 & 0.85 & 0.15\tabularnewline
977 & Warndarrang & 2.82 & 126 & 6 & 0.32 & 0.86 & 0.15\tabularnewline
1009 & Gamilaraay & 4.14 & 289 & 7 & 0.33 & 0.87 & 0.15\tabularnewline
920 & Yadhaykenu & 2.41 & 74 & 15 & 0.60 & 0.41 & 0.15\tabularnewline
1018 & Djapu & 2.33 & 126 & 16 & 0.62 & 0.30 & 0.16\tabularnewline
949 & Kok Nar & 3.03 & 85 & 13 & 0.62 & 0.54 & 0.16\tabularnewline
611 & Anguthimri & 2.37 & 41 & 20 & 0.59 & 0.20 & 0.16\tabularnewline
838 & Gooniyandi & 2.32 & 216 & 17 & 0.74 & 0.30 & 0.16\tabularnewline
540 & Ngiyambaa & 3.94 & 121 & 6 & 0.29 & 0.77 & 0.16\tabularnewline
252 & Warlmanpa & 2.37 & 235 & 8 & 0.29 & 0.58 & 0.16\tabularnewline
105 & Bardi & 2.06 & 59 & 22 & 0.92 & 0.13 & 0.16\tabularnewline
752 & Kija & 3.20 & 481 & 10 & 0.42 & 0.61 & 0.16\tabularnewline
847 & Ngalakgan & 3.85 & 229 & 11 & 0.41 & 0.50 & 0.16\tabularnewline
427 & Yidiny & 3.66 & 660 & 6 & 0.32 & 0.80 & 0.16\tabularnewline
983 & Nhangu & 2.51 & 275 & 14 & 0.45 & 0.28 & 0.16\tabularnewline
934 & Urningangg & 2.38 & 74 & 16 & 0.57 & 0.27 & 0.16\tabularnewline
1043 & Mbabaram & 3.06 & 41 & 12 & 0.44 & 0.39 & 0.16\tabularnewline
495 & Nyikina & 2.31 & 240 & 14 & 0.70 & 0.32 & 0.16\tabularnewline
978 & Wotjobaluk & 2.95 & 156 & 12 & 0.63 & 0.53 & 0.16\tabularnewline
1001 & Ngandi & 3.04 & 199 & 13 & 0.38 & 0.22 & 0.17\tabularnewline
412 & Ritharrngu & 2.73 & 406 & 6 & 0.19 & 0.59 & 0.17\tabularnewline
923 & Matngele & 3.97 & 221 & 10 & 0.40 & 0.57 & 0.17\tabularnewline
1025 & Waalubal & 3.29 & 360 & 12 & 0.60 & 0.48 & 0.17\tabularnewline
787 & Jawoyn & 3.73 & 374 & 14 & 0.52 & 0.32 & 0.17\tabularnewline
645 & Malyangapa & 2.02 & 21 & 18 & 0.72 & 0.10 & 0.17\tabularnewline
856 & Patjtjamalh & 3.29 & 222 & 13 & 0.48 & 0.43 & 0.17\tabularnewline
945 & Wiri & 2.19 & 57 & 13 & 0.72 & 0.39 & 0.17\tabularnewline
118 & Badimaya & 2.42 & 136 & 6 & 0.25 & 0.62 & 0.17\tabularnewline
1026 & Gidabal & 3.30 & 361 & 12 & 0.60 & 0.43 & 0.17\tabularnewline
911 & Nyawaygi & 3.31 & 219 & 6 & 0.33 & 0.82 & 0.17\tabularnewline
926 & Limilngan & 2.07 & 49 & 16 & 0.67 & 0.22 & 0.17\tabularnewline
935 & Rembarrnga & 3.58 & 263 & 9 & 0.32 & 0.47 & 0.18\tabularnewline
922 & Nakara & 2.24 & 127 & 20 & 0.77 & 0.05 & 0.18\tabularnewline
853 & Lardil & 3.55 & 663 & 12 & 0.48 & 0.44 & 0.18\tabularnewline
927 & Tiwi & 2.26 & 523 & 14 & 0.70 & 0.27 & 0.18\tabularnewline
910 & Nungali & 3.34 & 180 & 10 & 0.62 & 0.46 & 0.18\tabularnewline
737 & Kukatj & 4.64 & 294 & 8 & 0.32 & 0.58 & 0.19\tabularnewline
962 & Gunya & 2.25 & 89 & 13 & 0.42 & 0.07 & 0.19\tabularnewline
620 & Miriwoong & 4.07 & 953 & 8 & 0.40 & 0.54 & 0.19\tabularnewline
94 & Biri & 2.26 & 114 & 13 & 0.72 & 0.21 & 0.19\tabularnewline
1042 & Thaayorre & 5.74 & 1355 & 8 & 0.31 & 0.89 & 0.19\tabularnewline
939 & Unggumi & 2.65 & 66 & 13 & 0.43 & 0.13 & 0.19\tabularnewline
964 & Olkol & 2.10 & 164 & 21 & 0.68 & 0.04 & 0.19\tabularnewline
30 & Duungidjawu & 2.65 & 89 & 14 & 0.61 & 0.08 & 0.20\tabularnewline
965 & Oykangand & 2.34 & 171 & 19 & 0.61 & 0.03 & 0.20\tabularnewline
305 & Western Wakaya & 2.77 & 256 & 11 & 0.42 & 0.14 &
0.21\tabularnewline
546 & Yanyuwa & 1.96 & 216 & 18 & 0.78 & 0.03 & 0.21\tabularnewline
800 & Guwamu & 2.21 & 55 & 16 & 0.76 & 0.05 & 0.21\tabularnewline
13 & Dyirbal & 3.09 & 171 & 11 & 0.69 & 0.16 & 0.22\tabularnewline
363 & Yir Yoront & 3.51 & 318 & 14 & 0.54 & 0.04 & 0.23\tabularnewline
790 & Jaru & 3.13 & 552 & 12 & 0.52 & 0.07 & 0.23\tabularnewline
\bottomrule
\end{longtable}

\newpage

\textbf{Table A.3.3. Lognormal distribution.}

\begin{longtable}[]{@{}rlrrrrr@{}}
\toprule
\textbf{lex ID} & \textbf{language variety} & \(log\) \textbf{mean} &
\(log\) \textbf{SD} & \textbf{inventory size} & \(p\) &
\textbf{goodness-of-fit}\tabularnewline
\midrule
\endhead
866 & Thirarri & 3.20 & 1.35 & 25 & 1.00 & 0.06\tabularnewline
865 & Diyari & 3.17 & 1.36 & 25 & 0.99 & 0.06\tabularnewline
62 & Dhay'yi & 5.13 & 1.06 & 26 & 0.96 & 0.07\tabularnewline
771 & Kalkatungu & 5.32 & 1.09 & 26 & 0.94 & 0.08\tabularnewline
996 & Emmi & 3.64 & 1.13 & 31 & 0.84 & 0.08\tabularnewline
656 & Kuugu Ya'u & 5.29 & 0.85 & 21 & 0.96 & 0.08\tabularnewline
821 & Gumbaynggir & 4.38 & 0.64 & 19 & 0.96 & 0.08\tabularnewline
1018 & Djapu & 4.93 & 0.98 & 26 & 0.87 & 0.08\tabularnewline
427 & Yidiny & 6.01 & 0.77 & 19 & 0.97 & 0.09\tabularnewline
475 & Southern Paakintyi & 5.09 & 1.12 & 27 & 0.78 & 0.09\tabularnewline
645 & Malyangapa & 3.44 & 1.22 & 25 & 0.76 & 0.09\tabularnewline
962 & Gunya & 3.68 & 1.58 & 31 & 0.54 & 0.10\tabularnewline
598 & Yandruwandha & 4.41 & 1.42 & 30 & 0.64 & 0.10\tabularnewline
269 & Wangkumara & 4.47 & 1.21 & 30 & 0.59 & 0.10\tabularnewline
237 & Warluwarra & 4.38 & 1.62 & 33 & 0.51 & 0.10\tabularnewline
63 & Dharumbal & 4.42 & 1.18 & 20 & 0.83 & 0.10\tabularnewline
77 & Dhangu & 4.08 & 1.00 & 26 & 0.64 & 0.10\tabularnewline
546 & Yanyuwa & 5.96 & 1.13 & 23 & 0.77 & 0.10\tabularnewline
518 & Yarluyandi & 3.83 & 1.23 & 23 & 0.71 & 0.10\tabularnewline
5 & Gangulu & 4.68 & 1.01 & 18 & 0.88 & 0.10\tabularnewline
162 & Adnyamathanha & 5.16 & 1.14 & 29 & 0.51 & 0.10\tabularnewline
117 & Wirangu & 4.35 & 1.03 & 23 & 0.72 & 0.10\tabularnewline
740 & Kugu Nganhcara & 3.85 & 1.22 & 30 & 0.44 & 0.10\tabularnewline
540 & Ngiyambaa & 3.90 & 1.04 & 21 & 0.71 & 0.10\tabularnewline
200 & Western Arrernte & 4.01 & 0.94 & 25 & 0.58 & 0.11\tabularnewline
433 & Pitta Pitta & 4.52 & 1.25 & 25 & 0.61 & 0.11\tabularnewline
744 & Koko Bera & 5.71 & 0.63 & 21 & 0.75 & 0.11\tabularnewline
94 & Biri & 5.02 & 1.02 & 18 & 0.83 & 0.11\tabularnewline
204 & Wemba Wemba & 5.53 & 0.86 & 22 & 0.69 & 0.11\tabularnewline
945 & Wiri & 4.35 & 1.05 & 18 & 0.79 & 0.11\tabularnewline
982 & Nhirrpi & 3.39 & 1.29 & 30 & 0.38 & 0.11\tabularnewline
1032 & Kuku Yalanji & 6.30 & 0.71 & 16 & 0.84 & 0.11\tabularnewline
105 & Bardi & 4.78 & 0.94 & 24 & 0.52 & 0.11\tabularnewline
983 & Nhangu & 5.17 & 1.16 & 31 & 0.31 & 0.11\tabularnewline
968 & Ogh Angkula & 4.49 & 0.78 & 24 & 0.50 & 0.11\tabularnewline
979 & Mawng & 6.24 & 1.07 & 22 & 0.57 & 0.12\tabularnewline
495 & Nyikina & 5.61 & 1.05 & 20 & 0.62 & 0.12\tabularnewline
920 & Yadhaykenu & 4.25 & 1.21 & 25 & 0.47 & 0.12\tabularnewline
935 & Rembarrnga & 4.99 & 0.98 & 28 & 0.39 & 0.12\tabularnewline
1016 & Tharrkari & 3.66 & 1.19 & 32 & 0.25 & 0.12\tabularnewline
592 & Muruwari & 5.00 & 1.19 & 25 & 0.39 & 0.12\tabularnewline
918 & Atampaya & 4.22 & 1.24 & 25 & 0.45 & 0.12\tabularnewline
901 & Guugu Yimidhirr & 4.03 & 0.80 & 21 & 0.55 & 0.12\tabularnewline
412 & Ritharrngu & 5.09 & 1.16 & 31 & 0.22 & 0.12\tabularnewline
1024 & Ngardily & 4.40 & 0.99 & 22 & 0.49 & 0.12\tabularnewline
927 & Tiwi & 6.41 & 1.12 & 20 & 0.55 & 0.12\tabularnewline
265 & Wardaman & 5.94 & 0.86 & 22 & 0.50 & 0.12\tabularnewline
946 & Kurtjar & 5.13 & 0.79 & 28 & 0.29 & 0.12\tabularnewline
1002 & Yintyingka & 4.04 & 1.14 & 26 & 0.31 & 0.12\tabularnewline
1006 & Central Arrernte & 5.16 & 0.90 & 25 & 0.34 & 0.13\tabularnewline
835 & Gugu Badhun & 4.76 & 0.88 & 17 & 0.57 & 0.13\tabularnewline
1043 & Mbabaram & 3.16 & 1.11 & 27 & 0.19 & 0.13\tabularnewline
958 & Margany & 3.21 & 1.53 & 30 & 0.14 & 0.13\tabularnewline
807 & Gupapuyngu & 5.66 & 1.10 & 31 & 0.15 & 0.13\tabularnewline
534 & Nhanda & 3.95 & 1.25 & 33 & 0.13 & 0.13\tabularnewline
1029 & Martuthunira & 4.96 & 1.22 & 26 & 0.26 & 0.13\tabularnewline
925 & Larrakia & 4.07 & 1.70 & 29 & 0.19 & 0.13\tabularnewline
1042 & Thaayorre & 6.44 & 0.90 & 26 & 0.24 & 0.13\tabularnewline
1023 & Wubuy & 5.02 & 1.35 & 26 & 0.23 & 0.13\tabularnewline
919 & Angkamuthi & 4.52 & 1.25 & 26 & 0.23 & 0.13\tabularnewline
91 & Bularnu & 4.09 & 1.42 & 30 & 0.15 & 0.13\tabularnewline
845 & Iwaidja & 5.77 & 1.06 & 23 & 0.30 & 0.14\tabularnewline
963 & Kungkari & 3.29 & 1.32 & 24 & 0.21 & 0.14\tabularnewline
631 & Yalarnnga & 4.36 & 1.34 & 24 & 0.23 & 0.14\tabularnewline
30 & Duungidjawu & 4.37 & 1.04 & 23 & 0.23 & 0.14\tabularnewline
966 & Wik Mungkan & 6.50 & 1.18 & 26 & 0.22 & 0.14\tabularnewline
170 & Wik-Ngathan & 4.94 & 0.94 & 28 & 0.11 & 0.14\tabularnewline
915 & Alawa & 6.37 & 0.97 & 21 & 0.34 & 0.14\tabularnewline
922 & Nakara & 5.19 & 1.07 & 26 & 0.15 & 0.14\tabularnewline
118 & Badimaya & 4.30 & 1.19 & 24 & 0.19 & 0.15\tabularnewline
621 & Mengerrdji & 3.93 & 1.36 & 26 & 0.14 & 0.15\tabularnewline
99 & Bidyara & 5.06 & 1.07 & 19 & 0.33 & 0.15\tabularnewline
1009 & Gamilaraay & 5.07 & 0.98 & 21 & 0.26 & 0.15\tabularnewline
554 & Ngarluma & 5.16 & 1.00 & 23 & 0.18 & 0.15\tabularnewline
978 & Wotjobaluk & 4.99 & 0.89 & 19 & 0.29 & 0.15\tabularnewline
929 & Wanyjirra & 5.12 & 0.98 & 21 & 0.21 & 0.15\tabularnewline
377 & Umpila & 4.95 & 1.14 & 22 & 0.23 & 0.15\tabularnewline
697 & Kurrama & 4.51 & 1.45 & 27 & 0.11 & 0.15\tabularnewline
519 & Nukunu & 3.62 & 1.23 & 28 & 0.09 & 0.15\tabularnewline
852 & Gurindji & 6.66 & 1.38 & 23 & 0.19 & 0.15\tabularnewline
930 & Purduna & 4.38 & 1.29 & 26 & 0.09 & 0.15\tabularnewline
952 & Ngawun & 3.80 & 1.33 & 22 & 0.19 & 0.15\tabularnewline
841 & Worrorra & 3.91 & 1.21 & 25 & 0.13 & 0.15\tabularnewline
737 & Kukatj & 4.85 & 1.24 & 25 & 0.14 & 0.15\tabularnewline
572 & Ngamini & 4.79 & 1.27 & 23 & 0.15 & 0.15\tabularnewline
1003 & Murrinh-patha & 4.13 & 1.04 & 25 & 0.10 & 0.15\tabularnewline
13 & Dyirbal & 5.11 & 0.80 & 16 & 0.34 & 0.15\tabularnewline
921 & Gurr-Goni & 5.73 & 1.04 & 27 & 0.10 & 0.15\tabularnewline
926 & Limilngan & 3.91 & 1.50 & 24 & 0.12 & 0.15\tabularnewline
85 & Burarra & 6.15 & 0.96 & 26 & 0.10 & 0.15\tabularnewline
1012 & Warrgamay & 5.18 & 1.07 & 19 & 0.24 & 0.15\tabularnewline
928 & Bakanh & 4.23 & 1.15 & 26 & 0.10 & 0.15\tabularnewline
787 & Jawoyn & 5.56 & 0.90 & 27 & 0.07 & 0.16\tabularnewline
1025 & Waalubal & 5.76 & 0.88 & 20 & 0.21 & 0.16\tabularnewline
972 & Ogh Unyjan & 4.14 & 1.10 & 25 & 0.10 & 0.16\tabularnewline
790 & Jaru & 5.87 & 1.21 & 23 & 0.12 & 0.16\tabularnewline
1026 & Gidabal & 5.76 & 0.87 & 20 & 0.20 & 0.16\tabularnewline
400 & Thalanyji & 4.52 & 1.23 & 26 & 0.08 & 0.16\tabularnewline
363 & Yir Yoront & 5.49 & 0.88 & 26 & 0.09 & 0.16\tabularnewline
985 & Yaygir & 5.29 & 0.86 & 20 & 0.17 & 0.16\tabularnewline
911 & Nyawaygi & 4.78 & 1.06 & 18 & 0.20 & 0.16\tabularnewline
848 & Wagiman & 5.31 & 1.18 & 27 & 0.05 & 0.16\tabularnewline
957 & Ngaanyatjarra & 5.87 & 1.00 & 23 & 0.09 & 0.16\tabularnewline
905 & Malkana & 3.67 & 1.23 & 25 & 0.06 & 0.17\tabularnewline
642 & Mangala & 5.35 & 1.26 & 22 & 0.10 & 0.17\tabularnewline
1031 & Ngadjunmaya & 4.71 & 1.27 & 25 & 0.07 & 0.17\tabularnewline
838 & Gooniyandi & 5.57 & 1.17 & 23 & 0.08 & 0.17\tabularnewline
800 & Guwamu & 4.28 & 1.20 & 21 & 0.11 & 0.17\tabularnewline
943 & Pintupi & 6.73 & 1.13 & 23 & 0.07 & 0.17\tabularnewline
853 & Lardil & 5.94 & 1.13 & 25 & 0.05 & 0.17\tabularnewline
752 & Kija & 5.58 & 1.24 & 24 & 0.06 & 0.17\tabularnewline
228 & Warriyangga & 3.74 & 1.31 & 26 & 0.04 & 0.17\tabularnewline
89 & Bunuba & 4.48 & 1.31 & 24 & 0.05 & 0.17\tabularnewline
288 & Wangkatja & 5.85 & 1.10 & 23 & 0.06 & 0.17\tabularnewline
939 & Unggumi & 3.46 & 1.44 & 30 & 0.01 & 0.17\tabularnewline
618 & Mirniny & 3.84 & 1.28 & 25 & 0.04 & 0.18\tabularnewline
760 & Kartujarra & 4.88 & 1.27 & 23 & 0.06 & 0.18\tabularnewline
611 & Anguthimri & 3.36 & 1.49 & 34 & 0.01 & 0.18\tabularnewline
1008 & Yuwaalaraay & 5.66 & 1.11 & 21 & 0.06 & 0.18\tabularnewline
965 & Oykangand & 4.88 & 1.54 & 31 & 0.01 & 0.18\tabularnewline
949 & Kok Nar & 4.24 & 0.97 & 21 & 0.05 & 0.18\tabularnewline
443 & Payungu & 4.57 & 1.24 & 26 & 0.02 & 0.18\tabularnewline
417 & Yindjibarndi & 4.79 & 1.05 & 25 & 0.02 & 0.18\tabularnewline
977 & Warndarrang & 4.48 & 0.82 & 19 & 0.05 & 0.18\tabularnewline
31 & Djinang & 5.92 & 1.24 & 25 & 0.02 & 0.18\tabularnewline
1007 & Yuwaliyaay & 5.76 & 1.14 & 21 & 0.04 & 0.19\tabularnewline
940 & Yawijibaya & 3.33 & 1.43 & 23 & 0.01 & 0.19\tabularnewline
242 & Warlpiri & 6.82 & 1.27 & 24 & 0.02 & 0.19\tabularnewline
767 & Karajarri & 5.85 & 1.35 & 21 & 0.04 & 0.19\tabularnewline
847 & Ngalakgan & 4.90 & 1.15 & 27 & 0.01 & 0.20\tabularnewline
857 & Amurdak & 3.86 & 1.59 & 24 & 0.01 & 0.20\tabularnewline
1011 & Yorta Yorta & 3.78 & 1.41 & 24 & 0.01 & 0.20\tabularnewline
650 & Linngithigh & 4.04 & 1.35 & 27 & 0.01 & 0.20\tabularnewline
462 & Panyjima & 4.14 & 1.45 & 25 & 0.01 & 0.20\tabularnewline
734 & Kukatja & 6.51 & 1.21 & 23 & 0.01 & 0.20\tabularnewline
1040 & Ngarinyin & 6.52 & 1.94 & 27 & 0.01 & 0.20\tabularnewline
914 & Yinhawangka & 4.99 & 1.32 & 26 & 0.00 & 0.21\tabularnewline
12 & Erre & 3.75 & 1.53 & 27 & 0.00 & 0.21\tabularnewline
38 & Djabugay & 5.24 & 1.21 & 19 & 0.02 & 0.21\tabularnewline
934 & Urningangg & 3.72 & 1.90 & 28 & 0.00 & 0.21\tabularnewline
1001 & Ngandi & 4.41 & 1.68 & 34 & 0.00 & 0.21\tabularnewline
565 & Ngarinyman & 5.30 & 1.55 & 23 & 0.01 & 0.21\tabularnewline
81 & Dalabon & 6.04 & 1.31 & 29 & 0.00 & 0.21\tabularnewline
778 & Jiwarli & 5.00 & 1.26 & 26 & 0.00 & 0.22\tabularnewline
762 & Kariyarra & 4.08 & 1.25 & 24 & 0.00 & 0.22\tabularnewline
863 & Marra & 5.12 & 1.33 & 20 & 0.01 & 0.22\tabularnewline
305 & Western Wakaya & 4.83 & 1.64 & 26 & 0.00 & 0.22\tabularnewline
606 & Mudburra & 4.80 & 1.49 & 23 & 0.00 & 0.23\tabularnewline
910 & Nungali & 5.09 & 0.95 & 16 & 0.02 & 0.23\tabularnewline
493 & Nyiyaparli & 3.66 & 1.37 & 22 & 0.00 & 0.23\tabularnewline
252 & Warlmanpa & 3.89 & 2.28 & 28 & 0.00 & 0.24\tabularnewline
964 & Olkol & 4.77 & 2.13 & 31 & 0.00 & 0.24\tabularnewline
856 & Patjtjamalh & 4.43 & 1.95 & 27 & 0.00 & 0.24\tabularnewline
1021 & Watjarri & 4.95 & 1.37 & 26 & 0.00 & 0.24\tabularnewline
941 & Wambaya & 5.40 & 1.77 & 23 & 0.00 & 0.24\tabularnewline
967 & Thaynakwithi & 4.10 & 1.55 & 32 & 0.00 & 0.24\tabularnewline
851 & Bilinarra & 5.45 & 1.66 & 23 & 0.00 & 0.24\tabularnewline
563 & Ngarla & 5.27 & 1.56 & 23 & 0.00 & 0.24\tabularnewline
507 & Nyangumarta & 5.68 & 1.17 & 21 & 0.00 & 0.25\tabularnewline
849 & Waanyi & 5.32 & 1.70 & 20 & 0.00 & 0.25\tabularnewline
917 & Nyamal & 4.58 & 1.93 & 24 & 0.00 & 0.25\tabularnewline
620 & Miriwoong & 6.27 & 1.44 & 20 & 0.00 & 0.26\tabularnewline
1019 & Walmajarri & 6.39 & 1.77 & 23 & 0.00 & 0.26\tabularnewline
923 & Matngele & 4.45 & 1.82 & 25 & 0.00 & 0.27\tabularnewline
101 & Butchulla & 3.74 & 1.73 & 24 & 0.00 & 0.27\tabularnewline
232 & Warnman & 4.95 & 1.59 & 23 & 0.00 & 0.28\tabularnewline
1030 & Putijarra & 4.89 & 1.74 & 25 & 0.00 & 0.28\tabularnewline
113 & Yulparija & 5.57 & 1.76 & 23 & 0.00 & 0.30\tabularnewline
\bottomrule
\end{longtable}

\newpage

\textbf{Table A.3.4. Lognormal distribution with \(x_{min}\).}

\begin{longtable}[]{@{}rlrrrrrrr@{}}
\toprule
\textbf{lex ID} & \textbf{lang. variety} & \(log\) \textbf{mean} &
\(log\) \textbf{SD} & \(x_{min}\) & \(n\) \textbf{segments} &
\textbf{frac. inventory} & \(p\) & \textbf{gof}\tabularnewline
\midrule
\endhead
996 & Emmi & 3.76 & 0.97 & 7 & 29 & 0.94 & 1.00 & 0.05\tabularnewline
866 & Thirarri & 3.20 & 1.35 & 11 & 25 & 1.00 & 0.99 &
0.06\tabularnewline
865 & Diyari & 3.17 & 1.36 & 11 & 25 & 1.00 & 0.99 & 0.06\tabularnewline
966 & Wik Mungkan & 6.77 & 0.76 & 257 & 22 & 0.85 & 1.00 &
0.06\tabularnewline
565 & Ngarinyman & 5.67 & 0.89 & 115 & 19 & 0.83 & 1.00 &
0.06\tabularnewline
771 & Kalkatungu & 5.18 & 1.11 & 84 & 23 & 0.88 & 0.99 &
0.07\tabularnewline
841 & Worrorra & 3.85 & 1.00 & 20 & 23 & 0.92 & 0.98 &
0.07\tabularnewline
744 & Koko Bera & 5.77 & 0.52 & 150 & 19 & 0.90 & 0.99 &
0.07\tabularnewline
697 & Kurrama & 4.90 & 0.98 & 45 & 22 & 0.81 & 0.98 &
0.07\tabularnewline
475 & Southern Paakintyi & 4.74 & 1.32 & 69 & 22 & 0.81 & 0.95 &
0.07\tabularnewline
62 & Dhay'yi & 5.13 & 1.06 & 32 & 26 & 1.00 & 0.93 & 0.07\tabularnewline
915 & Alawa & 6.33 & 0.79 & 278 & 19 & 0.90 & 0.98 & 0.08\tabularnewline
1023 & Wubuy & 5.38 & 0.94 & 27 & 23 & 0.88 & 0.94 & 0.08\tabularnewline
656 & Kuugu Ya'u & 5.37 & 0.80 & 73 & 20 & 0.95 & 0.97 &
0.08\tabularnewline
85 & Burarra & 5.51 & 1.12 & 273 & 22 & 0.85 & 0.94 &
0.08\tabularnewline
269 & Wangkumara & 4.51 & 1.12 & 23 & 27 & 0.90 & 0.80 &
0.08\tabularnewline
928 & Bakanh & 4.63 & 0.68 & 34 & 21 & 0.81 & 0.92 & 0.08\tabularnewline
265 & Wardaman & 6.13 & 0.65 & 157 & 19 & 0.86 & 0.97 &
0.08\tabularnewline
952 & Ngawun & 3.88 & 1.00 & 35 & 16 & 0.73 & 0.98 & 0.08\tabularnewline
857 & Amurdak & 4.34 & 0.92 & 21 & 20 & 0.83 & 0.93 &
0.08\tabularnewline
5 & Gangulu & 4.87 & 0.83 & 42 & 15 & 0.83 & 0.98 & 0.08\tabularnewline
1018 & Djapu & 5.01 & 0.91 & 30 & 25 & 0.96 & 0.82 & 0.08\tabularnewline
767 & Karajarri & 5.71 & 0.98 & 233 & 17 & 0.81 & 0.97 &
0.08\tabularnewline
821 & Gumbaynggir & 4.38 & 0.64 & 41 & 19 & 1.00 & 0.93 &
0.08\tabularnewline
606 & Mudburra & 3.63 & 1.35 & 117 & 17 & 0.74 & 0.96 &
0.08\tabularnewline
495 & Nyikina & 5.88 & 0.84 & 75 & 18 & 0.90 & 0.96 &
0.08\tabularnewline
921 & Gurr-Goni & 5.88 & 0.80 & 173 & 22 & 0.81 & 0.87 &
0.08\tabularnewline
946 & Kurtjar & 5.32 & 0.57 & 60 & 25 & 0.89 & 0.78 &
0.08\tabularnewline
621 & Mengerrdji & 4.71 & 0.57 & 46 & 16 & 0.62 & 0.94 &
0.09\tabularnewline
427 & Yidiny & 6.01 & 0.77 & 75 & 19 & 1.00 & 0.94 & 0.09\tabularnewline
1024 & Ngardily & 1.87 & 1.63 & 56 & 17 & 0.77 & 0.94 &
0.09\tabularnewline
1006 & Central Arrernte & -6.19 & 3.11 & 158 & 12 & 0.48 & 0.97 &
0.09\tabularnewline
288 & Wangkatja & 2.01 & 1.98 & 240 & 19 & 0.83 & 0.95 &
0.09\tabularnewline
851 & Bilinarra & 5.76 & 0.94 & 162 & 19 & 0.83 & 0.93 &
0.09\tabularnewline
925 & Larrakia & 5.07 & 0.85 & 43 & 18 & 0.62 & 0.87 &
0.09\tabularnewline
926 & Limilngan & 4.46 & 0.97 & 25 & 18 & 0.75 & 0.87 &
0.09\tabularnewline
598 & Yandruwandha & 4.42 & 1.32 & 10 & 29 & 0.97 & 0.58 &
0.09\tabularnewline
963 & Kungkari & 3.45 & 1.02 & 11 & 21 & 0.88 & 0.79 &
0.09\tabularnewline
12 & Erre & 3.27 & 0.92 & 102 & 11 & 0.41 & 0.99 & 0.09\tabularnewline
540 & Ngiyambaa & 4.58 & 0.61 & 47 & 12 & 0.57 & 0.94 &
0.09\tabularnewline
31 & Djinang & 5.32 & 1.19 & 266 & 20 & 0.80 & 0.86 &
0.09\tabularnewline
917 & Nyamal & 4.96 & 1.02 & 82 & 19 & 0.79 & 0.88 & 0.09\tabularnewline
620 & Miriwoong & 6.61 & 0.65 & 189 & 18 & 0.90 & 0.92 &
0.09\tabularnewline
863 & Marra & 4.09 & 1.13 & 155 & 14 & 0.70 & 0.95 & 0.09\tabularnewline
1002 & Yintyingka & 4.45 & 0.80 & 32 & 19 & 0.73 & 0.73 &
0.09\tabularnewline
1012 & Warrgamay & 5.46 & 0.77 & 78 & 16 & 0.84 & 0.93 &
0.09\tabularnewline
934 & Urningangg & 4.90 & 0.59 & 51 & 17 & 0.61 & 0.86 &
0.09\tabularnewline
918 & Atampaya & 4.27 & 1.04 & 14 & 24 & 0.96 & 0.67 &
0.09\tabularnewline
237 & Warluwarra & 4.86 & 1.19 & 23 & 26 & 0.79 & 0.51 &
0.09\tabularnewline
170 & Wik-Ngathan & 5.65 & 0.46 & 144 & 16 & 0.57 & 0.86 &
0.09\tabularnewline
941 & Wambaya & 5.68 & 1.03 & 155 & 18 & 0.78 & 0.85 &
0.09\tabularnewline
412 & Ritharrngu & 5.51 & 0.84 & 48 & 26 & 0.84 & 0.54 &
0.09\tabularnewline
962 & Gunya & 4.58 & 1.04 & 27 & 20 & 0.65 & 0.61 & 0.09\tabularnewline
645 & Malyangapa & 3.44 & 1.22 & 1 & 25 & 1.00 & 0.57 &
0.09\tabularnewline
919 & Angkamuthi & -3.84 & 2.65 & 99 & 16 & 0.62 & 0.86 &
0.09\tabularnewline
204 & Wemba Wemba & 5.61 & 0.75 & 61 & 21 & 0.95 & 0.75 &
0.10\tabularnewline
518 & Yarluyandi & 3.95 & 1.12 & 10 & 21 & 0.91 & 0.66 &
0.10\tabularnewline
982 & Nhirrpi & 3.57 & 1.08 & 4 & 28 & 0.93 & 0.38 & 0.10\tabularnewline
91 & Bularnu & 3.09 & 1.59 & 44 & 21 & 0.70 & 0.58 & 0.10\tabularnewline
377 & Umpila & 5.05 & 0.87 & 37 & 21 & 0.95 & 0.71 & 0.10\tabularnewline
117 & Wirangu & 3.13 & 1.37 & 56 & 16 & 0.70 & 0.82 &
0.10\tabularnewline
228 & Warriyangga & 2.31 & 1.48 & 35 & 19 & 0.73 & 0.72 &
0.10\tabularnewline
752 & Kija & 5.93 & 0.74 & 269 & 16 & 0.67 & 0.88 & 0.10\tabularnewline
923 & Matngele & 5.22 & 0.60 & 69 & 20 & 0.80 & 0.72 &
0.10\tabularnewline
740 & Kugu Nganhcara & 2.63 & 1.18 & 94 & 12 & 0.40 & 0.83 &
0.10\tabularnewline
507 & Nyangumarta & 2.63 & 1.73 & 178 & 19 & 0.90 & 0.80 &
0.10\tabularnewline
760 & Kartujarra & 5.16 & 0.90 & 21 & 21 & 0.91 & 0.66 &
0.10\tabularnewline
63 & Dharumbal & 4.42 & 1.18 & 9 & 20 & 1.00 & 0.70 &
0.10\tabularnewline
847 & Ngalakgan & 5.25 & 0.66 & 53 & 23 & 0.85 & 0.55 &
0.10\tabularnewline
650 & Linngithigh & 4.41 & 0.72 & 21 & 24 & 0.89 & 0.51 &
0.10\tabularnewline
1025 & Waalubal & 6.11 & 0.49 & 209 & 15 & 0.75 & 0.85 &
0.10\tabularnewline
77 & Dhangu & 4.08 & 1.00 & 7 & 26 & 1.00 & 0.42 & 0.10\tabularnewline
546 & Yanyuwa & 5.96 & 1.13 & 27 & 23 & 1.00 & 0.60 &
0.10\tabularnewline
94 & Biri & 5.31 & 0.77 & 70 & 14 & 0.78 & 0.87 & 0.10\tabularnewline
631 & Yalarnnga & 4.67 & 1.04 & 7 & 22 & 0.92 & 0.59 &
0.10\tabularnewline
807 & Gupapuyngu & 5.00 & 1.21 & 212 & 24 & 0.77 & 0.53 &
0.10\tabularnewline
81 & Dalabon & 6.79 & 0.47 & 394 & 19 & 0.66 & 0.68 &
0.10\tabularnewline
778 & Jiwarli & 0.99 & 2.02 & 153 & 16 & 0.62 & 0.85 &
0.10\tabularnewline
99 & Bidyara & 4.17 & 1.20 & 107 & 15 & 0.79 & 0.84 &
0.10\tabularnewline
113 & Yulparija & 5.62 & 1.08 & 242 & 16 & 0.70 & 0.82 &
0.10\tabularnewline
162 & Adnyamathanha & 5.16 & 1.14 & 63 & 29 & 1.00 & 0.33 &
0.10\tabularnewline
945 & Wiri & 4.52 & 0.88 & 30 & 15 & 0.83 & 0.81 & 0.10\tabularnewline
30 & Duungidjawu & 4.70 & 0.74 & 19 & 20 & 0.87 & 0.58 &
0.10\tabularnewline
848 & Wagiman & 5.70 & 0.72 & 53 & 23 & 0.85 & 0.48 &
0.10\tabularnewline
979 & Mawng & 6.48 & 0.88 & 122 & 20 & 0.91 & 0.61 & 0.10\tabularnewline
935 & Rembarrnga & 5.14 & 0.80 & 28 & 26 & 0.93 & 0.33 &
0.11\tabularnewline
400 & Thalanyji & -1.73 & 2.38 & 85 & 18 & 0.69 & 0.68 &
0.11\tabularnewline
642 & Mangala & 5.47 & 0.93 & 170 & 16 & 0.73 & 0.74 &
0.11\tabularnewline
200 & Western Arrernte & 4.01 & 0.94 & 8 & 25 & 1.00 & 0.36 &
0.11\tabularnewline
957 & Ngaanyatjarra & 2.71 & 1.75 & 249 & 19 & 0.83 & 0.73 &
0.11\tabularnewline
433 & Pitta Pitta & 4.52 & 1.25 & 2 & 25 & 1.00 & 0.37 &
0.11\tabularnewline
1011 & Yorta Yorta & 4.26 & 0.80 & 15 & 20 & 0.83 & 0.50 &
0.11\tabularnewline
232 & Warnman & 5.68 & 0.87 & 202 & 9 & 0.39 & 0.84 &
0.11\tabularnewline
958 & Margany & 3.60 & 1.15 & 62 & 9 & 0.30 & 0.81 & 0.11\tabularnewline
1019 & Walmajarri & 6.97 & 0.81 & 226 & 20 & 0.87 & 0.58 &
0.11\tabularnewline
1001 & Ngandi & 4.97 & 0.85 & 76 & 25 & 0.74 & 0.31 &
0.11\tabularnewline
1030 & Putijarra & 2.44 & 1.63 & 157 & 18 & 0.72 & 0.66 &
0.11\tabularnewline
965 & Oykangand & 5.52 & 0.81 & 61 & 24 & 0.77 & 0.32 &
0.11\tabularnewline
519 & Nukunu & 1.96 & 1.61 & 25 & 22 & 0.79 & 0.38 & 0.11\tabularnewline
1031 & Ngadjunmaya & 5.17 & 0.79 & 35 & 20 & 0.80 & 0.46 &
0.11\tabularnewline
972 & Ogh Unyjan & -0.21 & 1.63 & 74 & 15 & 0.60 & 0.77 &
0.11\tabularnewline
1032 & Kuku Yalanji & 6.30 & 0.71 & 207 & 16 & 1.00 & 0.76 &
0.11\tabularnewline
105 & Bardi & 4.90 & 0.84 & 23 & 23 & 0.96 & 0.36 & 0.11\tabularnewline
305 & Western Wakaya & 5.30 & 0.94 & 26 & 23 & 0.88 & 0.38 &
0.11\tabularnewline
38 & Djabugay & 5.66 & 0.68 & 186 & 12 & 0.63 & 0.83 &
0.11\tabularnewline
737 & Kukatj & 5.72 & 0.38 & 170 & 12 & 0.48 & 0.73 &
0.11\tabularnewline
1026 & Gidabal & 6.04 & 0.55 & 184 & 16 & 0.80 & 0.62 &
0.11\tabularnewline
592 & Muruwari & 4.91 & 1.11 & 146 & 17 & 0.68 & 0.55 &
0.11\tabularnewline
838 & Gooniyandi & 4.20 & 1.37 & 216 & 17 & 0.74 & 0.60 &
0.11\tabularnewline
985 & Yaygir & 3.42 & 1.19 & 210 & 13 & 0.65 & 0.84 &
0.11\tabularnewline
983 & Nhangu & 5.17 & 1.16 & 28 & 31 & 1.00 & 0.15 & 0.11\tabularnewline
800 & Guwamu & 4.59 & 0.86 & 19 & 18 & 0.86 & 0.50 & 0.11\tabularnewline
101 & Butchulla & 0.82 & 1.63 & 85 & 15 & 0.62 & 0.79 &
0.11\tabularnewline
563 & Ngarla & 4.11 & 1.37 & 168 & 18 & 0.78 & 0.58 &
0.11\tabularnewline
968 & Ogh Angkula & 4.49 & 0.78 & 17 & 24 & 1.00 & 0.28 &
0.11\tabularnewline
852 & Gurindji & 7.05 & 0.87 & 217 & 20 & 0.87 & 0.44 &
0.11\tabularnewline
920 & Yadhaykenu & 4.25 & 1.21 & 2 & 25 & 1.00 & 0.24 &
0.12\tabularnewline
1016 & Tharrkari & 3.89 & 1.03 & 10 & 27 & 0.84 & 0.11 &
0.12\tabularnewline
978 & Wotjobaluk & 5.13 & 0.72 & 59 & 17 & 0.89 & 0.53 &
0.12\tabularnewline
927 & Tiwi & 6.66 & 0.94 & 193 & 17 & 0.85 & 0.51 & 0.12\tabularnewline
929 & Wanyjirra & 3.45 & 1.36 & 138 & 16 & 0.76 & 0.63 &
0.12\tabularnewline
845 & Iwaidja & 1.03 & 1.85 & 393 & 13 & 0.57 & 0.82 &
0.12\tabularnewline
964 & Olkol & 5.63 & 1.01 & 44 & 25 & 0.81 & 0.20 & 0.12\tabularnewline
901 & Guugu Yimidhirr & 4.03 & 0.80 & 7 & 21 & 1.00 & 0.30 &
0.12\tabularnewline
493 & Nyiyaparli & 3.87 & 0.87 & 20 & 19 & 0.86 & 0.35 &
0.12\tabularnewline
443 & Payungu & 1.55 & 1.85 & 85 & 18 & 0.69 & 0.53 &
0.12\tabularnewline
911 & Nyawaygi & 5.03 & 0.74 & 67 & 15 & 0.83 & 0.61 &
0.12\tabularnewline
611 & Anguthimri & 2.90 & 1.22 & 41 & 20 & 0.59 & 0.36 &
0.12\tabularnewline
967 & Thaynakwithi & 4.78 & 0.58 & 44 & 24 & 0.75 & 0.15 &
0.12\tabularnewline
417 & Yindjibarndi & 4.11 & 1.20 & 74 & 21 & 0.84 & 0.29 &
0.12\tabularnewline
572 & Ngamini & 4.87 & 1.13 & 131 & 12 & 0.52 & 0.65 &
0.12\tabularnewline
1003 & Murrinh-patha & 3.93 & 0.87 & 112 & 9 & 0.36 & 0.73 &
0.12\tabularnewline
849 & Waanyi & 0.77 & 1.90 & 341 & 12 & 0.60 & 0.74 &
0.12\tabularnewline
1043 & Mbabaram & 2.95 & 0.87 & 41 & 12 & 0.44 & 0.44 &
0.12\tabularnewline
1042 & Thaayorre & 6.52 & 0.83 & 127 & 25 & 0.96 & 0.14 &
0.12\tabularnewline
1029 & Martuthunira & 5.07 & 1.09 & 13 & 25 & 0.96 & 0.13 &
0.13\tabularnewline
462 & Panyjima & 5.12 & 0.81 & 106 & 8 & 0.32 & 0.64 &
0.13\tabularnewline
534 & Nhanda & 3.94 & 1.18 & 8 & 32 & 0.97 & 0.04 & 0.13\tabularnewline
943 & Pintupi & 5.91 & 1.26 & 550 & 19 & 0.83 & 0.35 &
0.13\tabularnewline
363 & Yir Yoront & 6.10 & 0.33 & 211 & 15 & 0.58 & 0.38 &
0.13\tabularnewline
242 & Warlpiri & 5.69 & 1.40 & 602 & 20 & 0.83 & 0.30 &
0.13\tabularnewline
835 & Gugu Badhun & 4.76 & 0.88 & 28 & 17 & 1.00 & 0.40 &
0.13\tabularnewline
252 & Warlmanpa & 5.04 & 1.05 & 72 & 20 & 0.71 & 0.29 &
0.13\tabularnewline
787 & Jawoyn & 6.01 & 0.54 & 160 & 20 & 0.74 & 0.18 &
0.13\tabularnewline
930 & Purduna & 4.72 & 1.05 & 18 & 23 & 0.88 & 0.11 &
0.13\tabularnewline
905 & Malkana & -3.27 & 2.40 & 41 & 16 & 0.64 & 0.36 &
0.13\tabularnewline
118 & Badimaya & 4.47 & 0.95 & 18 & 22 & 0.92 & 0.12 &
0.13\tabularnewline
940 & Yawijibaya & 1.19 & 1.53 & 50 & 13 & 0.57 & 0.55 &
0.13\tabularnewline
910 & Nungali & 4.96 & 0.76 & 118 & 13 & 0.81 & 0.54 &
0.14\tabularnewline
554 & Ngarluma & 5.52 & 0.95 & 224 & 8 & 0.35 & 0.63 &
0.14\tabularnewline
734 & Kukatja & 6.16 & 1.11 & 406 & 19 & 0.83 & 0.23 &
0.14\tabularnewline
1021 & Watjarri & 2.49 & 1.71 & 113 & 21 & 0.81 & 0.24 &
0.14\tabularnewline
790 & Jaru & 6.17 & 0.87 & 121 & 20 & 0.87 & 0.13 & 0.14\tabularnewline
922 & Nakara & 5.08 & 0.99 & 84 & 23 & 0.88 & 0.07 & 0.14\tabularnewline
914 & Yinhawangka & 2.13 & 1.79 & 120 & 20 & 0.77 & 0.21 &
0.14\tabularnewline
618 & Mirniny & 4.15 & 0.91 & 10 & 22 & 0.88 & 0.05 &
0.14\tabularnewline
13 & Dyirbal & 5.20 & 0.74 & 70 & 15 & 0.94 & 0.26 & 0.14\tabularnewline
1009 & Gamilaraay & 5.07 & 0.98 & 20 & 21 & 1.00 & 0.08 &
0.15\tabularnewline
853 & Lardil & 6.27 & 0.83 & 87 & 22 & 0.88 & 0.05 & 0.15\tabularnewline
949 & Kok Nar & 4.68 & 0.65 & 96 & 9 & 0.43 & 0.47 & 0.15\tabularnewline
1008 & Yuwaalaraay & 6.29 & 0.50 & 277 & 14 & 0.67 & 0.21 &
0.15\tabularnewline
89 & Bunuba & 5.02 & 0.88 & 40 & 18 & 0.75 & 0.06 & 0.15\tabularnewline
977 & Warndarrang & 1.60 & 1.53 & 126 & 6 & 0.32 & 0.66 &
0.15\tabularnewline
856 & Patjtjamalh & 5.33 & 0.75 & 66 & 20 & 0.74 & 0.04 &
0.15\tabularnewline
1040 & Ngarinyin & 7.59 & 0.72 & 689 & 18 & 0.67 & 0.03 &
0.17\tabularnewline
939 & Unggumi & 3.46 & 1.44 & 3 & 30 & 1.00 & 0.00 & 0.17\tabularnewline
1007 & Yuwaliyaay & 5.76 & 1.14 & 33 & 21 & 1.00 & 0.01 &
0.19\tabularnewline
\bottomrule
\end{longtable}

\newpage

\textbf{Table A.3.5. Exponential distribution.}

\begin{longtable}[]{@{}rlrrrr@{}}
\toprule
\textbf{lex ID} & \textbf{language variety} & \(\lambda\) &
\textbf{inventory size} & \(p\) &
\textbf{goodness-of-fit}\tabularnewline
\midrule
\endhead
1002 & Yintyingka & 0.01 & 26 & 0.97 & 0.08\tabularnewline
996 & Emmi & 0.02 & 31 & 0.91 & 0.08\tabularnewline
5 & Gangulu & 0.01 & 18 & 0.99 & 0.09\tabularnewline
1018 & Djapu & 0.01 & 26 & 0.94 & 0.09\tabularnewline
1023 & Wubuy & 0.00 & 26 & 0.95 & 0.09\tabularnewline
656 & Kuugu Ya'u & 0.00 & 21 & 0.97 & 0.09\tabularnewline
94 & Biri & 0.00 & 18 & 0.98 & 0.09\tabularnewline
952 & Ngawun & 0.01 & 22 & 0.93 & 0.09\tabularnewline
305 & Western Wakaya & 0.00 & 26 & 0.89 & 0.10\tabularnewline
12 & Erre & 0.01 & 27 & 0.83 & 0.10\tabularnewline
1031 & Ngadjunmaya & 0.01 & 25 & 0.87 & 0.10\tabularnewline
642 & Mangala & 0.00 & 22 & 0.93 & 0.10\tabularnewline
740 & Kugu Nganhcara & 0.01 & 30 & 0.75 & 0.10\tabularnewline
1011 & Yorta Yorta & 0.01 & 24 & 0.85 & 0.10\tabularnewline
945 & Wiri & 0.01 & 18 & 0.94 & 0.10\tabularnewline
845 & Iwaidja & 0.00 & 23 & 0.91 & 0.10\tabularnewline
852 & Gurindji & 0.00 & 23 & 0.96 & 0.10\tabularnewline
621 & Mengerrdji & 0.01 & 26 & 0.79 & 0.10\tabularnewline
540 & Ngiyambaa & 0.01 & 21 & 0.88 & 0.10\tabularnewline
968 & Ogh Angkula & 0.01 & 24 & 0.82 & 0.11\tabularnewline
1043 & Mbabaram & 0.03 & 27 & 0.70 & 0.11\tabularnewline
495 & Nyikina & 0.00 & 20 & 0.92 & 0.11\tabularnewline
979 & Mawng & 0.00 & 22 & 0.92 & 0.11\tabularnewline
807 & Gupapuyngu & 0.00 & 31 & 0.70 & 0.11\tabularnewline
565 & Ngarinyman & 0.00 & 23 & 0.84 & 0.11\tabularnewline
77 & Dhangu & 0.01 & 26 & 0.71 & 0.11\tabularnewline
1003 & Murrinh-patha & 0.01 & 25 & 0.72 & 0.11\tabularnewline
760 & Kartujarra & 0.00 & 23 & 0.80 & 0.11\tabularnewline
752 & Kija & 0.00 & 24 & 0.80 & 0.11\tabularnewline
30 & Duungidjawu & 0.01 & 23 & 0.77 & 0.11\tabularnewline
1001 & Ngandi & 0.01 & 34 & 0.53 & 0.11\tabularnewline
927 & Tiwi & 0.00 & 20 & 0.93 & 0.11\tabularnewline
821 & Gumbaynggir & 0.01 & 19 & 0.82 & 0.12\tabularnewline
928 & Bakanh & 0.01 & 26 & 0.67 & 0.12\tabularnewline
31 & Djinang & 0.00 & 25 & 0.81 & 0.12\tabularnewline
800 & Guwamu & 0.01 & 21 & 0.77 & 0.12\tabularnewline
935 & Rembarrnga & 0.00 & 28 & 0.61 & 0.12\tabularnewline
941 & Wambaya & 0.00 & 23 & 0.78 & 0.12\tabularnewline
170 & Wik-Ngathan & 0.01 & 28 & 0.58 & 0.12\tabularnewline
631 & Yalarnnga & 0.01 & 24 & 0.67 & 0.12\tabularnewline
1012 & Warrgamay & 0.00 & 19 & 0.82 & 0.12\tabularnewline
412 & Ritharrngu & 0.00 & 31 & 0.52 & 0.12\tabularnewline
841 & Worrorra & 0.01 & 25 & 0.62 & 0.12\tabularnewline
63 & Dharumbal & 0.01 & 20 & 0.77 & 0.12\tabularnewline
926 & Limilngan & 0.01 & 24 & 0.65 & 0.12\tabularnewline
790 & Jaru & 0.00 & 23 & 0.79 & 0.12\tabularnewline
851 & Bilinarra & 0.00 & 23 & 0.75 & 0.12\tabularnewline
105 & Bardi & 0.01 & 24 & 0.66 & 0.12\tabularnewline
62 & Dhay'yi & 0.00 & 26 & 0.59 & 0.12\tabularnewline
606 & Mudburra & 0.00 & 23 & 0.68 & 0.12\tabularnewline
838 & Gooniyandi & 0.00 & 23 & 0.71 & 0.12\tabularnewline
697 & Kurrama & 0.01 & 27 & 0.56 & 0.12\tabularnewline
848 & Wagiman & 0.00 & 27 & 0.55 & 0.13\tabularnewline
1024 & Ngardily & 0.01 & 22 & 0.66 & 0.13\tabularnewline
853 & Lardil & 0.00 & 25 & 0.68 & 0.13\tabularnewline
857 & Amurdak & 0.01 & 24 & 0.57 & 0.13\tabularnewline
737 & Kukatj & 0.01 & 25 & 0.56 & 0.13\tabularnewline
1009 & Gamilaraay & 0.00 & 21 & 0.65 & 0.13\tabularnewline
546 & Yanyuwa & 0.00 & 23 & 0.72 & 0.13\tabularnewline
911 & Nyawaygi & 0.01 & 18 & 0.73 & 0.13\tabularnewline
767 & Karajarri & 0.00 & 21 & 0.72 & 0.13\tabularnewline
99 & Bidyara & 0.00 & 19 & 0.69 & 0.13\tabularnewline
778 & Jiwarli & 0.00 & 26 & 0.49 & 0.13\tabularnewline
963 & Kungkari & 0.02 & 24 & 0.48 & 0.13\tabularnewline
918 & Atampaya & 0.01 & 25 & 0.47 & 0.14\tabularnewline
771 & Kalkatungu & 0.00 & 26 & 0.49 & 0.14\tabularnewline
288 & Wangkatja & 0.00 & 23 & 0.59 & 0.14\tabularnewline
965 & Oykangand & 0.00 & 31 & 0.32 & 0.14\tabularnewline
377 & Umpila & 0.00 & 22 & 0.53 & 0.14\tabularnewline
856 & Patjtjamalh & 0.00 & 27 & 0.39 & 0.14\tabularnewline
650 & Linngithigh & 0.01 & 27 & 0.37 & 0.14\tabularnewline
200 & Western Arrernte & 0.01 & 25 & 0.41 & 0.14\tabularnewline
427 & Yidiny & 0.00 & 19 & 0.68 & 0.14\tabularnewline
443 & Payungu & 0.01 & 26 & 0.40 & 0.14\tabularnewline
563 & Ngarla & 0.00 & 23 & 0.53 & 0.14\tabularnewline
921 & Gurr-Goni & 0.00 & 27 & 0.42 & 0.14\tabularnewline
964 & Olkol & 0.00 & 31 & 0.30 & 0.14\tabularnewline
917 & Nyamal & 0.00 & 24 & 0.44 & 0.14\tabularnewline
978 & Wotjobaluk & 0.01 & 19 & 0.60 & 0.14\tabularnewline
957 & Ngaanyatjarra & 0.00 & 23 & 0.53 & 0.14\tabularnewline
919 & Angkamuthi & 0.01 & 26 & 0.36 & 0.14\tabularnewline
89 & Bunuba & 0.01 & 24 & 0.43 & 0.14\tabularnewline
13 & Dyirbal & 0.01 & 16 & 0.69 & 0.14\tabularnewline
905 & Malkana & 0.01 & 25 & 0.36 & 0.15\tabularnewline
1019 & Walmajarri & 0.00 & 23 & 0.71 & 0.15\tabularnewline
762 & Kariyarra & 0.01 & 24 & 0.39 & 0.15\tabularnewline
1016 & Tharrkari & 0.01 & 32 & 0.20 & 0.15\tabularnewline
118 & Badimaya & 0.01 & 24 & 0.39 & 0.15\tabularnewline
787 & Jawoyn & 0.00 & 27 & 0.34 & 0.15\tabularnewline
417 & Yindjibarndi & 0.01 & 25 & 0.36 & 0.15\tabularnewline
982 & Nhirrpi & 0.02 & 30 & 0.23 & 0.15\tabularnewline
920 & Yadhaykenu & 0.01 & 25 & 0.34 & 0.15\tabularnewline
117 & Wirangu & 0.01 & 23 & 0.40 & 0.15\tabularnewline
929 & Wanyjirra & 0.00 & 21 & 0.47 & 0.15\tabularnewline
949 & Kok Nar & 0.01 & 21 & 0.45 & 0.15\tabularnewline
518 & Yarluyandi & 0.01 & 23 & 0.38 & 0.15\tabularnewline
228 & Warriyangga & 0.01 & 26 & 0.29 & 0.15\tabularnewline
985 & Yaygir & 0.00 & 20 & 0.50 & 0.15\tabularnewline
204 & Wemba Wemba & 0.00 & 22 & 0.43 & 0.15\tabularnewline
493 & Nyiyaparli & 0.01 & 22 & 0.38 & 0.15\tabularnewline
972 & Ogh Unyjan & 0.01 & 25 & 0.30 & 0.15\tabularnewline
835 & Gugu Badhun & 0.01 & 17 & 0.57 & 0.15\tabularnewline
1032 & Kuku Yalanji & 0.00 & 16 & 0.69 & 0.15\tabularnewline
1030 & Putijarra & 0.00 & 25 & 0.32 & 0.15\tabularnewline
242 & Warlpiri & 0.00 & 24 & 0.68 & 0.15\tabularnewline
592 & Muruwari & 0.00 & 25 & 0.31 & 0.16\tabularnewline
265 & Wardaman & 0.00 & 22 & 0.44 & 0.16\tabularnewline
977 & Warndarrang & 0.01 & 19 & 0.45 & 0.16\tabularnewline
1008 & Yuwaalaraay & 0.00 & 21 & 0.44 & 0.16\tabularnewline
462 & Panyjima & 0.01 & 25 & 0.28 & 0.16\tabularnewline
232 & Warnman & 0.00 & 23 & 0.34 & 0.16\tabularnewline
1029 & Martuthunira & 0.00 & 26 & 0.26 & 0.16\tabularnewline
930 & Purduna & 0.01 & 26 & 0.25 & 0.16\tabularnewline
967 & Thaynakwithi & 0.01 & 32 & 0.15 & 0.16\tabularnewline
113 & Yulparija & 0.00 & 23 & 0.42 & 0.16\tabularnewline
618 & Mirniny & 0.01 & 25 & 0.24 & 0.16\tabularnewline
38 & Djabugay & 0.00 & 19 & 0.45 & 0.16\tabularnewline
734 & Kukatja & 0.00 & 23 & 0.60 & 0.16\tabularnewline
269 & Wangkumara & 0.01 & 30 & 0.14 & 0.16\tabularnewline
85 & Burarra & 0.00 & 26 & 0.33 & 0.17\tabularnewline
400 & Thalanyji & 0.01 & 26 & 0.21 & 0.17\tabularnewline
572 & Ngamini & 0.00 & 23 & 0.27 & 0.17\tabularnewline
611 & Anguthimri & 0.02 & 34 & 0.08 & 0.17\tabularnewline
162 & Adnyamathanha & 0.00 & 29 & 0.16 & 0.17\tabularnewline
554 & Ngarluma & 0.00 & 23 & 0.26 & 0.17\tabularnewline
847 & Ngalakgan & 0.00 & 27 & 0.16 & 0.17\tabularnewline
934 & Urningangg & 0.01 & 28 & 0.15 & 0.17\tabularnewline
363 & Yir Yoront & 0.00 & 26 & 0.19 & 0.17\tabularnewline
237 & Warluwarra & 0.00 & 33 & 0.09 & 0.17\tabularnewline
598 & Yandruwandha & 0.01 & 30 & 0.11 & 0.17\tabularnewline
901 & Guugu Yimidhirr & 0.01 & 21 & 0.26 & 0.17\tabularnewline
1026 & Gidabal & 0.00 & 20 & 0.33 & 0.17\tabularnewline
1007 & Yuwaliyaay & 0.00 & 21 & 0.33 & 0.17\tabularnewline
475 & Southern Paakintyi & 0.00 & 27 & 0.16 & 0.17\tabularnewline
939 & Unggumi & 0.01 & 30 & 0.09 & 0.17\tabularnewline
849 & Waanyi & 0.00 & 20 & 0.34 & 0.18\tabularnewline
865 & Diyari & 0.02 & 25 & 0.15 & 0.18\tabularnewline
866 & Thirarri & 0.02 & 25 & 0.14 & 0.18\tabularnewline
645 & Malyangapa & 0.02 & 25 & 0.14 & 0.18\tabularnewline
433 & Pitta Pitta & 0.01 & 25 & 0.15 & 0.18\tabularnewline
966 & Wik Mungkan & 0.00 & 26 & 0.34 & 0.18\tabularnewline
923 & Matngele & 0.01 & 25 & 0.14 & 0.18\tabularnewline
925 & Larrakia & 0.01 & 29 & 0.09 & 0.18\tabularnewline
1006 & Central Arrernte & 0.00 & 25 & 0.14 & 0.18\tabularnewline
1021 & Watjarri & 0.00 & 26 & 0.13 & 0.18\tabularnewline
1042 & Thaayorre & 0.00 & 26 & 0.25 & 0.18\tabularnewline
1025 & Waalubal & 0.00 & 20 & 0.27 & 0.18\tabularnewline
946 & Kurtjar & 0.01 & 28 & 0.10 & 0.18\tabularnewline
914 & Yinhawangka & 0.00 & 26 & 0.12 & 0.18\tabularnewline
922 & Nakara & 0.00 & 26 & 0.11 & 0.18\tabularnewline
863 & Marra & 0.00 & 20 & 0.22 & 0.19\tabularnewline
91 & Bularnu & 0.01 & 30 & 0.06 & 0.19\tabularnewline
519 & Nukunu & 0.01 & 28 & 0.06 & 0.19\tabularnewline
958 & Margany & 0.02 & 30 & 0.03 & 0.20\tabularnewline
1040 & Ngarinyin & 0.00 & 27 & 0.33 & 0.20\tabularnewline
962 & Gunya & 0.01 & 31 & 0.02 & 0.20\tabularnewline
534 & Nhanda & 0.01 & 33 & 0.02 & 0.21\tabularnewline
983 & Nhangu & 0.00 & 31 & 0.03 & 0.21\tabularnewline
943 & Pintupi & 0.00 & 23 & 0.25 & 0.21\tabularnewline
940 & Yawijibaya & 0.02 & 23 & 0.04 & 0.22\tabularnewline
744 & Koko Bera & 0.00 & 21 & 0.06 & 0.22\tabularnewline
81 & Dalabon & 0.00 & 29 & 0.03 & 0.22\tabularnewline
507 & Nyangumarta & 0.00 & 21 & 0.05 & 0.24\tabularnewline
915 & Alawa & 0.00 & 21 & 0.07 & 0.24\tabularnewline
910 & Nungali & 0.00 & 16 & 0.05 & 0.26\tabularnewline
101 & Butchulla & 0.01 & 24 & 0.01 & 0.26\tabularnewline
252 & Warlmanpa & 0.00 & 28 & 0.00 & 0.26\tabularnewline
620 & Miriwoong & 0.00 & 20 & 0.04 & 0.27\tabularnewline
\bottomrule
\end{longtable}

\newpage

\textbf{Table A.3.6. Exponential distribution with \(x_{min}\).}

\begin{longtable}[]{@{}rlrrrrrr@{}}
\toprule
\textbf{lex ID} & \textbf{language variety} & \(\lambda\) & \(x_{min}\)
& \(n\) \textbf{segments} & \textbf{frac. of inventory} & \(p\) &
\textbf{goodness-of-fit}\tabularnewline
\midrule
\endhead
1002 & Yintyingka & 0.01 & 11 & 24 & 0.92 & 0.98 & 0.07\tabularnewline
925 & Larrakia & 0.01 & 21 & 21 & 0.72 & 0.99 & 0.07\tabularnewline
966 & Wik Mungkan & 0.00 & 456 & 19 & 0.73 & 1.00 & 0.07\tabularnewline
1023 & Wubuy & 0.00 & 12 & 25 & 0.96 & 0.96 & 0.08\tabularnewline
740 & Kugu Nganhcara & 0.01 & 11 & 26 & 0.87 & 0.92 &
0.08\tabularnewline
915 & Alawa & 0.00 & 250 & 20 & 0.95 & 0.99 & 0.08\tabularnewline
996 & Emmi & 0.02 & 2 & 31 & 1.00 & 0.83 & 0.08\tabularnewline
265 & Wardaman & 0.00 & 224 & 18 & 0.82 & 0.99 & 0.09\tabularnewline
5 & Gangulu & 0.01 & 9 & 18 & 1.00 & 0.98 & 0.09\tabularnewline
427 & Yidiny & 0.00 & 164 & 18 & 0.95 & 0.99 & 0.09\tabularnewline
1018 & Djapu & 0.01 & 25 & 26 & 1.00 & 0.90 & 0.09\tabularnewline
656 & Kuugu Ya'u & 0.00 & 65 & 21 & 1.00 & 0.94 & 0.09\tabularnewline
565 & Ngarinyman & 0.00 & 115 & 19 & 0.83 & 0.95 & 0.09\tabularnewline
952 & Ngawun & 0.01 & 10 & 19 & 0.86 & 0.92 & 0.09\tabularnewline
377 & Umpila & 0.01 & 37 & 21 & 0.95 & 0.92 & 0.09\tabularnewline
697 & Kurrama & 0.00 & 7 & 25 & 0.93 & 0.83 & 0.09\tabularnewline
744 & Koko Bera & 0.01 & 244 & 15 & 0.71 & 0.97 & 0.09\tabularnewline
935 & Rembarrnga & 0.01 & 64 & 25 & 0.89 & 0.83 & 0.09\tabularnewline
94 & Biri & 0.00 & 12 & 18 & 1.00 & 0.96 & 0.09\tabularnewline
621 & Mengerrdji & 0.01 & 65 & 15 & 0.58 & 0.94 & 0.10\tabularnewline
928 & Bakanh & 0.01 & 52 & 19 & 0.73 & 0.84 & 0.10\tabularnewline
495 & Nyikina & 0.00 & 67 & 19 & 0.95 & 0.92 & 0.10\tabularnewline
305 & Western Wakaya & 0.00 & 1 & 26 & 1.00 & 0.78 & 0.10\tabularnewline
105 & Bardi & 0.01 & 79 & 16 & 0.67 & 0.93 & 0.10\tabularnewline
12 & Erre & 0.01 & 1 & 27 & 1.00 & 0.70 & 0.10\tabularnewline
921 & Gurr-Goni & 0.00 & 173 & 22 & 0.81 & 0.85 & 0.10\tabularnewline
934 & Urningangg & 0.01 & 36 & 21 & 0.75 & 0.81 & 0.10\tabularnewline
1031 & Ngadjunmaya & 0.01 & 3 & 25 & 1.00 & 0.77 & 0.10\tabularnewline
642 & Mangala & 0.00 & 13 & 22 & 1.00 & 0.86 & 0.10\tabularnewline
540 & Ngiyambaa & 0.01 & 27 & 16 & 0.76 & 0.87 & 0.10\tabularnewline
1012 & Warrgamay & 0.00 & 105 & 15 & 0.79 & 0.95 & 0.10\tabularnewline
926 & Limilngan & 0.01 & 4 & 22 & 0.92 & 0.80 & 0.10\tabularnewline
852 & Gurindji & 0.00 & 43 & 22 & 0.96 & 0.91 & 0.10\tabularnewline
412 & Ritharrngu & 0.00 & 37 & 29 & 0.94 & 0.61 & 0.10\tabularnewline
1011 & Yorta Yorta & 0.01 & 14 & 21 & 0.88 & 0.76 & 0.10\tabularnewline
63 & Dharumbal & 0.01 & 36 & 15 & 0.75 & 0.92 & 0.10\tabularnewline
170 & Wik-Ngathan & 0.01 & 230 & 13 & 0.46 & 0.93 & 0.10\tabularnewline
946 & Kurtjar & 0.01 & 153 & 19 & 0.68 & 0.81 & 0.10\tabularnewline
965 & Oykangand & 0.00 & 58 & 25 & 0.81 & 0.66 & 0.10\tabularnewline
1043 & Mbabaram & 0.03 & 4 & 26 & 0.96 & 0.57 & 0.10\tabularnewline
945 & Wiri & 0.01 & 6 & 18 & 1.00 & 0.90 & 0.10\tabularnewline
863 & Marra & 0.00 & 67 & 19 & 0.95 & 0.88 & 0.10\tabularnewline
845 & Iwaidja & 0.00 & 24 & 23 & 1.00 & 0.80 & 0.10\tabularnewline
857 & Amurdak & 0.01 & 2 & 23 & 0.96 & 0.73 & 0.10\tabularnewline
1001 & Ngandi & 0.01 & 3 & 33 & 0.97 & 0.45 & 0.10\tabularnewline
807 & Gupapuyngu & 0.00 & 50 & 30 & 0.97 & 0.50 & 0.11\tabularnewline
968 & Ogh Angkula & 0.01 & 17 & 24 & 1.00 & 0.68 & 0.11\tabularnewline
767 & Karajarri & 0.00 & 111 & 19 & 0.90 & 0.83 & 0.11\tabularnewline
204 & Wemba Wemba & 0.00 & 97 & 20 & 0.91 & 0.78 & 0.11\tabularnewline
81 & Dalabon & 0.00 & 581 & 18 & 0.62 & 0.87 & 0.11\tabularnewline
30 & Duungidjawu & 0.01 & 43 & 19 & 0.83 & 0.80 & 0.11\tabularnewline
821 & Gumbaynggir & 0.02 & 62 & 15 & 0.79 & 0.85 & 0.11\tabularnewline
979 & Mawng & 0.00 & 86 & 22 & 1.00 & 0.81 & 0.11\tabularnewline
752 & Kija & 0.00 & 269 & 16 & 0.67 & 0.88 & 0.11\tabularnewline
964 & Olkol & 0.00 & 3 & 28 & 0.90 & 0.49 & 0.11\tabularnewline
611 & Anguthimri & 0.01 & 7 & 28 & 0.82 & 0.38 & 0.11\tabularnewline
851 & Bilinarra & 0.00 & 162 & 19 & 0.83 & 0.80 & 0.11\tabularnewline
77 & Dhangu & 0.01 & 7 & 26 & 1.00 & 0.53 & 0.11\tabularnewline
939 & Unggumi & 0.01 & 9 & 24 & 0.80 & 0.52 & 0.11\tabularnewline
1003 & Murrinh-patha & 0.01 & 8 & 25 & 1.00 & 0.54 & 0.11\tabularnewline
760 & Kartujarra & 0.00 & 4 & 23 & 1.00 & 0.64 & 0.11\tabularnewline
927 & Tiwi & 0.00 & 88 & 20 & 1.00 & 0.82 & 0.11\tabularnewline
848 & Wagiman & 0.00 & 130 & 22 & 0.81 & 0.64 & 0.11\tabularnewline
232 & Warnman & 0.00 & 202 & 9 & 0.39 & 0.95 & 0.12\tabularnewline
941 & Wambaya & 0.00 & 5 & 22 & 0.96 & 0.62 & 0.12\tabularnewline
620 & Miriwoong & 0.00 & 536 & 14 & 0.70 & 0.90 & 0.12\tabularnewline
31 & Djinang & 0.00 & 24 & 25 & 1.00 & 0.57 & 0.12\tabularnewline
38 & Djabugay & 0.00 & 186 & 12 & 0.63 & 0.90 & 0.12\tabularnewline
800 & Guwamu & 0.01 & 3 & 21 & 1.00 & 0.61 & 0.12\tabularnewline
917 & Nyamal & 0.00 & 3 & 22 & 0.92 & 0.57 & 0.12\tabularnewline
972 & Ogh Unyjan & 0.01 & 36 & 21 & 0.84 & 0.46 & 0.12\tabularnewline
790 & Jaru & 0.00 & 43 & 22 & 0.96 & 0.59 & 0.12\tabularnewline
650 & Linngithigh & 0.01 & 33 & 23 & 0.85 & 0.45 & 0.12\tabularnewline
911 & Nyawaygi & 0.01 & 67 & 15 & 0.83 & 0.82 & 0.12\tabularnewline
847 & Ngalakgan & 0.01 & 119 & 20 & 0.74 & 0.58 & 0.12\tabularnewline
631 & Yalarnnga & 0.01 & 6 & 24 & 1.00 & 0.48 & 0.12\tabularnewline
841 & Worrorra & 0.01 & 1 & 25 & 1.00 & 0.42 & 0.12\tabularnewline
923 & Matngele & 0.01 & 109 & 18 & 0.72 & 0.65 & 0.12\tabularnewline
978 & Wotjobaluk & 0.01 & 83 & 16 & 0.84 & 0.71 & 0.12\tabularnewline
62 & Dhay'yi & 0.00 & 228 & 10 & 0.38 & 0.66 & 0.12\tabularnewline
771 & Kalkatungu & 0.00 & 45 & 24 & 0.92 & 0.40 & 0.12\tabularnewline
967 & Thaynakwithi & 0.01 & 67 & 23 & 0.72 & 0.38 & 0.12\tabularnewline
737 & Kukatj & 0.01 & 35 & 23 & 0.92 & 0.39 & 0.12\tabularnewline
606 & Mudburra & 0.00 & 2 & 23 & 1.00 & 0.48 & 0.12\tabularnewline
943 & Pintupi & 0.00 & 415 & 20 & 0.87 & 0.71 & 0.12\tabularnewline
838 & Gooniyandi & 0.00 & 15 & 23 & 1.00 & 0.49 & 0.12\tabularnewline
901 & Guugu Yimidhirr & 0.02 & 26 & 19 & 0.90 & 0.52 &
0.13\tabularnewline
1025 & Waalubal & 0.00 & 372 & 11 & 0.55 & 0.83 & 0.13\tabularnewline
962 & Gunya & 0.01 & 11 & 25 & 0.81 & 0.31 & 0.13\tabularnewline
1024 & Ngardily & 0.01 & 5 & 22 & 1.00 & 0.45 & 0.13\tabularnewline
853 & Lardil & 0.00 & 50 & 25 & 1.00 & 0.40 & 0.13\tabularnewline
963 & Kungkari & 0.01 & 50 & 7 & 0.29 & 0.78 & 0.13\tabularnewline
1009 & Gamilaraay & 0.00 & 20 & 21 & 1.00 & 0.46 & 0.13\tabularnewline
546 & Yanyuwa & 0.00 & 27 & 23 & 1.00 & 0.44 & 0.13\tabularnewline
856 & Patjtjamalh & 0.00 & 2 & 25 & 0.93 & 0.27 & 0.13\tabularnewline
99 & Bidyara & 0.00 & 7 & 19 & 1.00 & 0.51 & 0.13\tabularnewline
778 & Jiwarli & 0.00 & 11 & 26 & 1.00 & 0.25 & 0.13\tabularnewline
918 & Atampaya & 0.01 & 1 & 25 & 1.00 & 0.26 & 0.14\tabularnewline
940 & Yawijibaya & 0.01 & 10 & 18 & 0.78 & 0.41 & 0.14\tabularnewline
1032 & Kuku Yalanji & 0.00 & 378 & 12 & 0.75 & 0.76 &
0.14\tabularnewline
288 & Wangkatja & 0.00 & 48 & 23 & 1.00 & 0.32 & 0.14\tabularnewline
237 & Warluwarra & 0.00 & 23 & 26 & 0.79 & 0.15 & 0.14\tabularnewline
1026 & Gidabal & 0.00 & 284 & 14 & 0.70 & 0.61 & 0.14\tabularnewline
200 & Western Arrernte & 0.01 & 8 & 25 & 1.00 & 0.19 &
0.14\tabularnewline
958 & Margany & 0.01 & 7 & 24 & 0.80 & 0.18 & 0.14\tabularnewline
443 & Payungu & 0.01 & 5 & 26 & 1.00 & 0.18 & 0.14\tabularnewline
563 & Ngarla & 0.00 & 2 & 23 & 1.00 & 0.27 & 0.14\tabularnewline
519 & Nukunu & 0.01 & 53 & 9 & 0.32 & 0.67 & 0.14\tabularnewline
1019 & Walmajarri & 0.00 & 226 & 20 & 0.87 & 0.40 & 0.14\tabularnewline
957 & Ngaanyatjarra & 0.00 & 57 & 23 & 1.00 & 0.25 & 0.14\tabularnewline
919 & Angkamuthi & 0.01 & 5 & 26 & 1.00 & 0.15 & 0.14\tabularnewline
89 & Bunuba & 0.01 & 7 & 24 & 1.00 & 0.20 & 0.14\tabularnewline
13 & Dyirbal & 0.01 & 59 & 16 & 1.00 & 0.51 & 0.14\tabularnewline
905 & Malkana & 0.01 & 2 & 25 & 1.00 & 0.15 & 0.15\tabularnewline
985 & Yaygir & 0.00 & 107 & 17 & 0.85 & 0.36 & 0.15\tabularnewline
762 & Kariyarra & 0.01 & 2 & 24 & 1.00 & 0.17 & 0.15\tabularnewline
1016 & Tharrkari & 0.01 & 2 & 32 & 1.00 & 0.05 & 0.15\tabularnewline
910 & Nungali & 0.01 & 115 & 14 & 0.88 & 0.61 & 0.15\tabularnewline
118 & Badimaya & 0.01 & 3 & 24 & 1.00 & 0.17 & 0.15\tabularnewline
787 & Jawoyn & 0.00 & 64 & 27 & 1.00 & 0.11 & 0.15\tabularnewline
417 & Yindjibarndi & 0.01 & 17 & 25 & 1.00 & 0.15 & 0.15\tabularnewline
982 & Nhirrpi & 0.02 & 1 & 30 & 1.00 & 0.06 & 0.15\tabularnewline
920 & Yadhaykenu & 0.01 & 2 & 25 & 1.00 & 0.14 & 0.15\tabularnewline
117 & Wirangu & 0.01 & 4 & 23 & 1.00 & 0.18 & 0.15\tabularnewline
592 & Muruwari & 0.00 & 66 & 20 & 0.80 & 0.25 & 0.15\tabularnewline
598 & Yandruwandha & 0.00 & 92 & 14 & 0.47 & 0.35 & 0.15\tabularnewline
929 & Wanyjirra & 0.00 & 36 & 21 & 1.00 & 0.25 & 0.15\tabularnewline
949 & Kok Nar & 0.01 & 13 & 21 & 1.00 & 0.23 & 0.15\tabularnewline
518 & Yarluyandi & 0.01 & 4 & 23 & 1.00 & 0.16 & 0.15\tabularnewline
228 & Warriyangga & 0.01 & 1 & 26 & 1.00 & 0.11 & 0.15\tabularnewline
252 & Warlmanpa & 0.00 & 6 & 22 & 0.79 & 0.18 & 0.15\tabularnewline
475 & Southern Paakintyi & 0.00 & 106 & 18 & 0.67 & 0.21 &
0.15\tabularnewline
400 & Thalanyji & 0.00 & 161 & 7 & 0.27 & 0.59 & 0.15\tabularnewline
85 & Burarra & 0.00 & 284 & 21 & 0.81 & 0.18 & 0.15\tabularnewline
493 & Nyiyaparli & 0.01 & 1 & 22 & 1.00 & 0.17 & 0.15\tabularnewline
462 & Panyjima & 0.01 & 106 & 8 & 0.32 & 0.60 & 0.15\tabularnewline
113 & Yulparija & 0.00 & 151 & 20 & 0.87 & 0.22 & 0.15\tabularnewline
645 & Malyangapa & 0.01 & 57 & 7 & 0.28 & 0.60 & 0.15\tabularnewline
835 & Gugu Badhun & 0.01 & 28 & 17 & 1.00 & 0.36 & 0.15\tabularnewline
1030 & Putijarra & 0.00 & 1 & 25 & 1.00 & 0.10 & 0.15\tabularnewline
242 & Warlpiri & 0.00 & 63 & 24 & 1.00 & 0.33 & 0.15\tabularnewline
849 & Waanyi & 0.00 & 211 & 15 & 0.75 & 0.39 & 0.15\tabularnewline
433 & Pitta Pitta & 0.00 & 150 & 7 & 0.28 & 0.60 & 0.16\tabularnewline
977 & Warndarrang & 0.01 & 35 & 19 & 1.00 & 0.23 & 0.16\tabularnewline
1008 & Yuwaalaraay & 0.00 & 39 & 21 & 1.00 & 0.19 & 0.16\tabularnewline
1029 & Martuthunira & 0.00 & 8 & 26 & 1.00 & 0.08 & 0.16\tabularnewline
930 & Purduna & 0.01 & 12 & 26 & 1.00 & 0.08 & 0.16\tabularnewline
1042 & Thaayorre & 0.00 & 208 & 24 & 0.92 & 0.09 & 0.16\tabularnewline
914 & Yinhawangka & 0.00 & 220 & 8 & 0.31 & 0.57 & 0.16\tabularnewline
618 & Mirniny & 0.01 & 1 & 25 & 1.00 & 0.07 & 0.16\tabularnewline
572 & Ngamini & 0.00 & 17 & 22 & 0.96 & 0.10 & 0.16\tabularnewline
734 & Kukatja & 0.00 & 35 & 23 & 1.00 & 0.22 & 0.16\tabularnewline
269 & Wangkumara & 0.01 & 4 & 30 & 1.00 & 0.02 & 0.16\tabularnewline
363 & Yir Yoront & 0.00 & 44 & 25 & 0.96 & 0.04 & 0.17\tabularnewline
162 & Adnyamathanha & 0.00 & 63 & 29 & 1.00 & 0.02 & 0.17\tabularnewline
554 & Ngarluma & 0.00 & 30 & 23 & 1.00 & 0.08 & 0.17\tabularnewline
507 & Nyangumarta & 0.00 & 307 & 9 & 0.43 & 0.54 & 0.17\tabularnewline
1007 & Yuwaliyaay & 0.00 & 33 & 21 & 1.00 & 0.09 & 0.17\tabularnewline
865 & Diyari & 0.01 & 13 & 23 & 0.92 & 0.04 & 0.17\tabularnewline
866 & Thirarri & 0.01 & 13 & 23 & 0.92 & 0.03 & 0.17\tabularnewline
534 & Nhanda & 0.00 & 106 & 6 & 0.18 & 0.52 & 0.18\tabularnewline
1006 & Central Arrernte & 0.00 & 27 & 25 & 1.00 & 0.02 &
0.18\tabularnewline
1021 & Watjarri & 0.00 & 5 & 26 & 1.00 & 0.02 & 0.18\tabularnewline
922 & Nakara & 0.00 & 14 & 26 & 1.00 & 0.02 & 0.18\tabularnewline
101 & Butchulla & 0.01 & 85 & 15 & 0.62 & 0.14 & 0.19\tabularnewline
91 & Bularnu & 0.01 & 2 & 30 & 1.00 & 0.00 & 0.19\tabularnewline
983 & Nhangu & 0.00 & 130 & 19 & 0.61 & 0.02 & 0.19\tabularnewline
1040 & Ngarinyin & 0.00 & 2 & 27 & 1.00 & 0.05 & 0.20\tabularnewline
\bottomrule
\end{longtable}

\newpage

\textbf{Table A.3.7. Poisson distribution.}

\begin{longtable}[]{@{}rlrrrr@{}}
\toprule
\textbf{lex ID} & \textbf{language variety} & \(\lambda\) &
\textbf{inventory size} & \(p\) &
\textbf{goodness-of-fit}\tabularnewline
\midrule
\endhead
972 & Ogh Unyjan & 94.24 & 25 & 0 & 0.45\tabularnewline
946 & Kurtjar & 218.96 & 28 & 0 & 0.46\tabularnewline
363 & Yir Yoront & 325.35 & 26 & 0 & 0.46\tabularnewline
940 & Yawijibaya & 67.52 & 23 & 0 & 0.46\tabularnewline
967 & Thaynakwithi & 114.44 & 32 & 0 & 0.46\tabularnewline
787 & Jawoyn & 387.26 & 27 & 0 & 0.47\tabularnewline
81 & Dalabon & 726.28 & 29 & 0 & 0.47\tabularnewline
928 & Bakanh & 110.96 & 26 & 0 & 0.47\tabularnewline
821 & Gumbaynggir & 108.68 & 19 & 0 & 0.47\tabularnewline
934 & Urningangg & 107.14 & 28 & 0 & 0.47\tabularnewline
1008 & Yuwaalaraay & 471.62 & 21 & 0 & 0.48\tabularnewline
1007 & Yuwaliyaay & 520.43 & 21 & 0 & 0.48\tabularnewline
1009 & Gamilaraay & 236.52 & 21 & 0 & 0.48\tabularnewline
949 & Kok Nar & 107.81 & 21 & 0 & 0.49\tabularnewline
101 & Butchulla & 113.88 & 24 & 0 & 0.49\tabularnewline
1025 & Waalubal & 424.70 & 20 & 0 & 0.50\tabularnewline
621 & Mengerrdji & 91.58 & 26 & 0 & 0.50\tabularnewline
1026 & Gidabal & 424.95 & 20 & 0 & 0.50\tabularnewline
744 & Koko Bera & 357.86 & 21 & 0 & 0.50\tabularnewline
968 & Ogh Angkula & 120.38 & 24 & 0 & 0.50\tabularnewline
170 & Wik-Ngathan & 219.75 & 28 & 0 & 0.50\tabularnewline
939 & Unggumi & 75.20 & 30 & 0 & 0.50\tabularnewline
1043 & Mbabaram & 40.44 & 27 & 0 & 0.51\tabularnewline
540 & Ngiyambaa & 82.86 & 21 & 0 & 0.51\tabularnewline
848 & Wagiman & 334.41 & 27 & 0 & 0.51\tabularnewline
847 & Ngalakgan & 208.44 & 27 & 0 & 0.51\tabularnewline
923 & Matngele & 182.64 & 25 & 0 & 0.51\tabularnewline
856 & Patjtjamalh & 215.96 & 27 & 0 & 0.52\tabularnewline
1040 & Ngarinyin & 1850.44 & 27 & 0 & 0.52\tabularnewline
901 & Guugu Yimidhirr & 75.29 & 21 & 0 & 0.52\tabularnewline
1003 & Murrinh-patha & 100.64 & 25 & 0 & 0.52\tabularnewline
853 & Lardil & 645.00 & 25 & 0 & 0.52\tabularnewline
38 & Djabugay & 313.21 & 19 & 0 & 0.52\tabularnewline
790 & Jaru & 638.04 & 23 & 0 & 0.52\tabularnewline
800 & Guwamu & 125.10 & 21 & 0 & 0.52\tabularnewline
89 & Bunuba & 178.71 & 24 & 0 & 0.53\tabularnewline
996 & Emmi & 64.35 & 31 & 0 & 0.53\tabularnewline
1002 & Yintyingka & 98.00 & 26 & 0 & 0.53\tabularnewline
958 & Margany & 64.53 & 30 & 0 & 0.53\tabularnewline
30 & Duungidjawu & 124.96 & 23 & 0 & 0.53\tabularnewline
910 & Nungali & 227.00 & 16 & 0 & 0.54\tabularnewline
985 & Yaygir & 287.10 & 20 & 0 & 0.54\tabularnewline
1042 & Thaayorre & 890.58 & 26 & 0 & 0.54\tabularnewline
978 & Wotjobaluk & 207.63 & 19 & 0 & 0.54\tabularnewline
857 & Amurdak & 104.25 & 24 & 0 & 0.54\tabularnewline
493 & Nyiyaparli & 69.91 & 22 & 0 & 0.54\tabularnewline
965 & Oykangand & 272.42 & 31 & 0 & 0.54\tabularnewline
650 & Linngithigh & 97.48 & 27 & 0 & 0.54\tabularnewline
979 & Mawng & 876.68 & 22 & 0 & 0.55\tabularnewline
611 & Anguthimri & 64.97 & 34 & 0 & 0.55\tabularnewline
737 & Kukatj & 203.48 & 25 & 0 & 0.55\tabularnewline
265 & Wardaman & 521.77 & 22 & 0 & 0.55\tabularnewline
1001 & Ngandi & 188.32 & 34 & 0 & 0.55\tabularnewline
5 & Gangulu & 167.00 & 18 & 0 & 0.56\tabularnewline
1011 & Yorta Yorta & 84.08 & 24 & 0 & 0.56\tabularnewline
740 & Kugu Nganhcara & 88.50 & 30 & 0 & 0.56\tabularnewline
427 & Yidiny & 540.42 & 19 & 0 & 0.56\tabularnewline
94 & Biri & 234.56 & 18 & 0 & 0.56\tabularnewline
911 & Nyawaygi & 187.61 & 18 & 0 & 0.56\tabularnewline
620 & Miriwoong & 833.75 & 20 & 0 & 0.56\tabularnewline
12 & Erre & 86.89 & 27 & 0 & 0.56\tabularnewline
63 & Dharumbal & 150.30 & 20 & 0 & 0.56\tabularnewline
841 & Worrorra & 85.52 & 25 & 0 & 0.56\tabularnewline
852 & Gurindji & 1478.43 & 23 & 0 & 0.57\tabularnewline
952 & Ngawun & 84.55 & 22 & 0 & 0.57\tabularnewline
1012 & Warrgamay & 284.79 & 19 & 0 & 0.58\tabularnewline
252 & Warlmanpa & 236.82 & 28 & 0 & 0.58\tabularnewline
982 & Nhirrpi & 59.30 & 30 & 0 & 0.58\tabularnewline
305 & Western Wakaya & 267.12 & 26 & 0 & 0.58\tabularnewline
983 & Nhangu & 347.97 & 31 & 0 & 0.58\tabularnewline
752 & Kija & 455.75 & 24 & 0 & 0.58\tabularnewline
1032 & Kuku Yalanji & 754.31 & 16 & 0 & 0.58\tabularnewline
915 & Alawa & 819.76 & 21 & 0 & 0.58\tabularnewline
926 & Limilngan & 110.79 & 24 & 0 & 0.58\tabularnewline
105 & Bardi & 184.71 & 24 & 0 & 0.58\tabularnewline
977 & Warndarrang & 136.95 & 19 & 0 & 0.59\tabularnewline
642 & Mangala & 385.36 & 22 & 0 & 0.59\tabularnewline
1016 & Tharrkari & 75.97 & 32 & 0 & 0.59\tabularnewline
443 & Payungu & 183.73 & 26 & 0 & 0.59\tabularnewline
228 & Warriyangga & 80.85 & 26 & 0 & 0.59\tabularnewline
377 & Umpila & 222.73 & 22 & 0 & 0.59\tabularnewline
945 & Wiri & 122.78 & 18 & 0 & 0.60\tabularnewline
204 & Wemba Wemba & 347.82 & 22 & 0 & 0.60\tabularnewline
495 & Nyikina & 468.55 & 20 & 0 & 0.60\tabularnewline
927 & Tiwi & 1100.60 & 20 & 0 & 0.60\tabularnewline
925 & Larrakia & 153.24 & 29 & 0 & 0.60\tabularnewline
922 & Nakara & 320.04 & 26 & 0 & 0.60\tabularnewline
1031 & Ngadjunmaya & 202.72 & 25 & 0 & 0.60\tabularnewline
606 & Mudburra & 242.65 & 23 & 0 & 0.60\tabularnewline
935 & Rembarrnga & 221.36 & 28 & 0 & 0.61\tabularnewline
905 & Malkana & 73.96 & 25 & 0 & 0.61\tabularnewline
518 & Yarluyandi & 91.30 & 23 & 0 & 0.61\tabularnewline
845 & Iwaidja & 525.39 & 23 & 0 & 0.61\tabularnewline
851 & Bilinarra & 503.00 & 23 & 0 & 0.61\tabularnewline
546 & Yanyuwa & 675.48 & 23 & 0 & 0.61\tabularnewline
941 & Wambaya & 508.91 & 23 & 0 & 0.61\tabularnewline
77 & Dhangu & 95.31 & 26 & 0 & 0.61\tabularnewline
237 & Warluwarra & 215.64 & 33 & 0 & 0.61\tabularnewline
534 & Nhanda & 103.94 & 33 & 0 & 0.61\tabularnewline
412 & Ritharrngu & 309.90 & 31 & 0 & 0.61\tabularnewline
200 & Western Arrernte & 91.60 & 25 & 0 & 0.61\tabularnewline
598 & Yandruwandha & 185.47 & 30 & 0 & 0.62\tabularnewline
118 & Badimaya & 132.67 & 24 & 0 & 0.62\tabularnewline
921 & Gurr-Goni & 482.26 & 27 & 0 & 0.62\tabularnewline
920 & Yadhaykenu & 129.72 & 25 & 0 & 0.62\tabularnewline
966 & Wik Mungkan & 1043.19 & 26 & 0 & 0.62\tabularnewline
417 & Yindjibarndi & 203.44 & 25 & 0 & 0.62\tabularnewline
929 & Wanyjirra & 271.71 & 21 & 0 & 0.63\tabularnewline
963 & Kungkari & 52.79 & 24 & 0 & 0.63\tabularnewline
697 & Kurrama & 198.04 & 27 & 0 & 0.63\tabularnewline
930 & Purduna & 173.77 & 26 & 0 & 0.63\tabularnewline
838 & Gooniyandi & 453.43 & 23 & 0 & 0.63\tabularnewline
1029 & Martuthunira & 263.35 & 26 & 0 & 0.63\tabularnewline
863 & Marra & 264.95 & 20 & 0 & 0.63\tabularnewline
1024 & Ngardily & 125.36 & 22 & 0 & 0.64\tabularnewline
964 & Olkol & 349.77 & 31 & 0 & 0.64\tabularnewline
645 & Malyangapa & 58.48 & 25 & 0 & 0.64\tabularnewline
592 & Muruwari & 320.88 & 25 & 0 & 0.64\tabularnewline
849 & Waanyi & 487.40 & 20 & 0 & 0.64\tabularnewline
962 & Gunya & 119.39 & 31 & 0 & 0.64\tabularnewline
771 & Kalkatungu & 373.27 & 26 & 0 & 0.64\tabularnewline
1018 & Djapu & 224.62 & 26 & 0 & 0.64\tabularnewline
618 & Mirniny & 86.96 & 25 & 0 & 0.64\tabularnewline
807 & Gupapuyngu & 520.52 & 31 & 0 & 0.65\tabularnewline
565 & Ngarinyman & 409.91 & 23 & 0 & 0.65\tabularnewline
656 & Kuugu Ya'u & 305.86 & 21 & 0 & 0.65\tabularnewline
117 & Wirangu & 126.04 & 23 & 0 & 0.65\tabularnewline
1023 & Wubuy & 294.08 & 26 & 0 & 0.65\tabularnewline
760 & Kartujarra & 238.70 & 23 & 0 & 0.65\tabularnewline
919 & Angkamuthi & 180.88 & 26 & 0 & 0.65\tabularnewline
99 & Bidyara & 246.11 & 19 & 0 & 0.65\tabularnewline
1019 & Walmajarri & 1323.57 & 23 & 0 & 0.65\tabularnewline
232 & Warnman & 295.09 & 23 & 0 & 0.65\tabularnewline
943 & Pintupi & 1476.22 & 23 & 0 & 0.65\tabularnewline
85 & Burarra & 739.81 & 26 & 0 & 0.65\tabularnewline
631 & Yalarnnga & 159.67 & 24 & 0 & 0.65\tabularnewline
62 & Dhay'yi & 296.73 & 26 & 0 & 0.65\tabularnewline
778 & Jiwarli & 289.15 & 26 & 0 & 0.65\tabularnewline
762 & Kariyarra & 105.88 & 24 & 0 & 0.66\tabularnewline
917 & Nyamal & 254.75 & 24 & 0 & 0.66\tabularnewline
767 & Karajarri & 599.05 & 21 & 0 & 0.66\tabularnewline
572 & Ngamini & 252.83 & 23 & 0 & 0.66\tabularnewline
865 & Diyari & 75.92 & 25 & 0 & 0.67\tabularnewline
866 & Thirarri & 75.96 & 25 & 0 & 0.67\tabularnewline
475 & Southern Paakintyi & 314.19 & 27 & 0 & 0.67\tabularnewline
91 & Bularnu & 138.10 & 30 & 0 & 0.67\tabularnewline
507 & Nyangumarta & 459.86 & 21 & 0 & 0.67\tabularnewline
957 & Ngaanyatjarra & 579.57 & 23 & 0 & 0.67\tabularnewline
918 & Atampaya & 124.20 & 25 & 0 & 0.67\tabularnewline
1030 & Putijarra & 297.56 & 25 & 0 & 0.67\tabularnewline
13 & Dyirbal & 242.94 & 16 & 0 & 0.68\tabularnewline
31 & Djinang & 673.56 & 25 & 0 & 0.68\tabularnewline
400 & Thalanyji & 175.85 & 26 & 0 & 0.69\tabularnewline
835 & Gugu Badhun & 175.12 & 17 & 0 & 0.69\tabularnewline
113 & Yulparija & 581.22 & 23 & 0 & 0.70\tabularnewline
554 & Ngarluma & 293.39 & 23 & 0 & 0.70\tabularnewline
288 & Wangkatja & 610.09 & 23 & 0 & 0.70\tabularnewline
734 & Kukatja & 1174.91 & 23 & 0 & 0.70\tabularnewline
269 & Wangkumara & 172.03 & 30 & 0 & 0.70\tabularnewline
462 & Panyjima & 129.20 & 25 & 0 & 0.70\tabularnewline
519 & Nukunu & 72.00 & 28 & 0 & 0.70\tabularnewline
563 & Ngarla & 392.61 & 23 & 0 & 0.71\tabularnewline
242 & Warlpiri & 1704.25 & 24 & 0 & 0.71\tabularnewline
1006 & Central Arrernte & 287.80 & 25 & 0 & 0.72\tabularnewline
162 & Adnyamathanha & 412.69 & 29 & 0 & 0.72\tabularnewline
433 & Pitta Pitta & 173.60 & 25 & 0 & 0.72\tabularnewline
914 & Yinhawangka & 283.50 & 26 & 0 & 0.73\tabularnewline
1021 & Watjarri & 279.65 & 26 & 0 & 0.75\tabularnewline
\bottomrule
\end{longtable}

\newpage

\textbf{Table A.3.8. Poisson distribution with \(x_{min}\).}

\begin{longtable}[]{@{}rlrrrrrr@{}}
\toprule
\textbf{lex ID} & \textbf{language variety} & \(\lambda\) & \(x_{min}\)
& \(n\) \textbf{segments} & \textbf{frac. of inventory} & \(p\) &
\textbf{goodness-of-fit}\tabularnewline
\midrule
\endhead
1002 & Yintyingka & 0.01 & 11 & 24 & 0.92 & 0.98 & 0.07\tabularnewline
925 & Larrakia & 0.01 & 21 & 21 & 0.72 & 0.99 & 0.07\tabularnewline
966 & Wik Mungkan & 0.00 & 456 & 19 & 0.73 & 1.00 & 0.07\tabularnewline
1023 & Wubuy & 0.00 & 12 & 25 & 0.96 & 0.96 & 0.08\tabularnewline
740 & Kugu Nganhcara & 0.01 & 11 & 26 & 0.87 & 0.92 &
0.08\tabularnewline
915 & Alawa & 0.00 & 250 & 20 & 0.95 & 0.99 & 0.08\tabularnewline
996 & Emmi & 0.02 & 2 & 31 & 1.00 & 0.83 & 0.08\tabularnewline
265 & Wardaman & 0.00 & 224 & 18 & 0.82 & 0.99 & 0.09\tabularnewline
5 & Gangulu & 0.01 & 9 & 18 & 1.00 & 0.98 & 0.09\tabularnewline
427 & Yidiny & 0.00 & 164 & 18 & 0.95 & 0.99 & 0.09\tabularnewline
1018 & Djapu & 0.01 & 25 & 26 & 1.00 & 0.90 & 0.09\tabularnewline
656 & Kuugu Ya'u & 0.00 & 65 & 21 & 1.00 & 0.94 & 0.09\tabularnewline
565 & Ngarinyman & 0.00 & 115 & 19 & 0.83 & 0.95 & 0.09\tabularnewline
952 & Ngawun & 0.01 & 10 & 19 & 0.86 & 0.92 & 0.09\tabularnewline
377 & Umpila & 0.01 & 37 & 21 & 0.95 & 0.92 & 0.09\tabularnewline
697 & Kurrama & 0.00 & 7 & 25 & 0.93 & 0.83 & 0.09\tabularnewline
744 & Koko Bera & 0.01 & 244 & 15 & 0.71 & 0.97 & 0.09\tabularnewline
935 & Rembarrnga & 0.01 & 64 & 25 & 0.89 & 0.83 & 0.09\tabularnewline
94 & Biri & 0.00 & 12 & 18 & 1.00 & 0.96 & 0.09\tabularnewline
621 & Mengerrdji & 0.01 & 65 & 15 & 0.58 & 0.94 & 0.10\tabularnewline
928 & Bakanh & 0.01 & 52 & 19 & 0.73 & 0.84 & 0.10\tabularnewline
495 & Nyikina & 0.00 & 67 & 19 & 0.95 & 0.92 & 0.10\tabularnewline
305 & Western Wakaya & 0.00 & 1 & 26 & 1.00 & 0.78 & 0.10\tabularnewline
105 & Bardi & 0.01 & 79 & 16 & 0.67 & 0.93 & 0.10\tabularnewline
12 & Erre & 0.01 & 1 & 27 & 1.00 & 0.70 & 0.10\tabularnewline
921 & Gurr-Goni & 0.00 & 173 & 22 & 0.81 & 0.85 & 0.10\tabularnewline
934 & Urningangg & 0.01 & 36 & 21 & 0.75 & 0.81 & 0.10\tabularnewline
1031 & Ngadjunmaya & 0.01 & 3 & 25 & 1.00 & 0.77 & 0.10\tabularnewline
642 & Mangala & 0.00 & 13 & 22 & 1.00 & 0.86 & 0.10\tabularnewline
540 & Ngiyambaa & 0.01 & 27 & 16 & 0.76 & 0.87 & 0.10\tabularnewline
1012 & Warrgamay & 0.00 & 105 & 15 & 0.79 & 0.95 & 0.10\tabularnewline
926 & Limilngan & 0.01 & 4 & 22 & 0.92 & 0.80 & 0.10\tabularnewline
852 & Gurindji & 0.00 & 43 & 22 & 0.96 & 0.91 & 0.10\tabularnewline
412 & Ritharrngu & 0.00 & 37 & 29 & 0.94 & 0.61 & 0.10\tabularnewline
1011 & Yorta Yorta & 0.01 & 14 & 21 & 0.88 & 0.76 & 0.10\tabularnewline
63 & Dharumbal & 0.01 & 36 & 15 & 0.75 & 0.92 & 0.10\tabularnewline
170 & Wik-Ngathan & 0.01 & 230 & 13 & 0.46 & 0.93 & 0.10\tabularnewline
946 & Kurtjar & 0.01 & 153 & 19 & 0.68 & 0.81 & 0.10\tabularnewline
965 & Oykangand & 0.00 & 58 & 25 & 0.81 & 0.66 & 0.10\tabularnewline
1043 & Mbabaram & 0.03 & 4 & 26 & 0.96 & 0.57 & 0.10\tabularnewline
945 & Wiri & 0.01 & 6 & 18 & 1.00 & 0.90 & 0.10\tabularnewline
863 & Marra & 0.00 & 67 & 19 & 0.95 & 0.88 & 0.10\tabularnewline
845 & Iwaidja & 0.00 & 24 & 23 & 1.00 & 0.80 & 0.10\tabularnewline
857 & Amurdak & 0.01 & 2 & 23 & 0.96 & 0.73 & 0.10\tabularnewline
1001 & Ngandi & 0.01 & 3 & 33 & 0.97 & 0.45 & 0.10\tabularnewline
807 & Gupapuyngu & 0.00 & 50 & 30 & 0.97 & 0.50 & 0.11\tabularnewline
968 & Ogh Angkula & 0.01 & 17 & 24 & 1.00 & 0.68 & 0.11\tabularnewline
767 & Karajarri & 0.00 & 111 & 19 & 0.90 & 0.83 & 0.11\tabularnewline
204 & Wemba Wemba & 0.00 & 97 & 20 & 0.91 & 0.78 & 0.11\tabularnewline
81 & Dalabon & 0.00 & 581 & 18 & 0.62 & 0.87 & 0.11\tabularnewline
30 & Duungidjawu & 0.01 & 43 & 19 & 0.83 & 0.80 & 0.11\tabularnewline
821 & Gumbaynggir & 0.02 & 62 & 15 & 0.79 & 0.85 & 0.11\tabularnewline
979 & Mawng & 0.00 & 86 & 22 & 1.00 & 0.81 & 0.11\tabularnewline
752 & Kija & 0.00 & 269 & 16 & 0.67 & 0.88 & 0.11\tabularnewline
964 & Olkol & 0.00 & 3 & 28 & 0.90 & 0.49 & 0.11\tabularnewline
611 & Anguthimri & 0.01 & 7 & 28 & 0.82 & 0.38 & 0.11\tabularnewline
851 & Bilinarra & 0.00 & 162 & 19 & 0.83 & 0.80 & 0.11\tabularnewline
77 & Dhangu & 0.01 & 7 & 26 & 1.00 & 0.53 & 0.11\tabularnewline
939 & Unggumi & 0.01 & 9 & 24 & 0.80 & 0.52 & 0.11\tabularnewline
1003 & Murrinh-patha & 0.01 & 8 & 25 & 1.00 & 0.54 & 0.11\tabularnewline
760 & Kartujarra & 0.00 & 4 & 23 & 1.00 & 0.64 & 0.11\tabularnewline
927 & Tiwi & 0.00 & 88 & 20 & 1.00 & 0.82 & 0.11\tabularnewline
848 & Wagiman & 0.00 & 130 & 22 & 0.81 & 0.64 & 0.11\tabularnewline
232 & Warnman & 0.00 & 202 & 9 & 0.39 & 0.95 & 0.12\tabularnewline
941 & Wambaya & 0.00 & 5 & 22 & 0.96 & 0.62 & 0.12\tabularnewline
620 & Miriwoong & 0.00 & 536 & 14 & 0.70 & 0.90 & 0.12\tabularnewline
31 & Djinang & 0.00 & 24 & 25 & 1.00 & 0.57 & 0.12\tabularnewline
38 & Djabugay & 0.00 & 186 & 12 & 0.63 & 0.90 & 0.12\tabularnewline
800 & Guwamu & 0.01 & 3 & 21 & 1.00 & 0.61 & 0.12\tabularnewline
917 & Nyamal & 0.00 & 3 & 22 & 0.92 & 0.57 & 0.12\tabularnewline
972 & Ogh Unyjan & 0.01 & 36 & 21 & 0.84 & 0.46 & 0.12\tabularnewline
790 & Jaru & 0.00 & 43 & 22 & 0.96 & 0.59 & 0.12\tabularnewline
650 & Linngithigh & 0.01 & 33 & 23 & 0.85 & 0.45 & 0.12\tabularnewline
911 & Nyawaygi & 0.01 & 67 & 15 & 0.83 & 0.82 & 0.12\tabularnewline
847 & Ngalakgan & 0.01 & 119 & 20 & 0.74 & 0.58 & 0.12\tabularnewline
631 & Yalarnnga & 0.01 & 6 & 24 & 1.00 & 0.48 & 0.12\tabularnewline
841 & Worrorra & 0.01 & 1 & 25 & 1.00 & 0.42 & 0.12\tabularnewline
923 & Matngele & 0.01 & 109 & 18 & 0.72 & 0.65 & 0.12\tabularnewline
978 & Wotjobaluk & 0.01 & 83 & 16 & 0.84 & 0.71 & 0.12\tabularnewline
62 & Dhay'yi & 0.00 & 228 & 10 & 0.38 & 0.66 & 0.12\tabularnewline
771 & Kalkatungu & 0.00 & 45 & 24 & 0.92 & 0.40 & 0.12\tabularnewline
967 & Thaynakwithi & 0.01 & 67 & 23 & 0.72 & 0.38 & 0.12\tabularnewline
737 & Kukatj & 0.01 & 35 & 23 & 0.92 & 0.39 & 0.12\tabularnewline
606 & Mudburra & 0.00 & 2 & 23 & 1.00 & 0.48 & 0.12\tabularnewline
943 & Pintupi & 0.00 & 415 & 20 & 0.87 & 0.71 & 0.12\tabularnewline
838 & Gooniyandi & 0.00 & 15 & 23 & 1.00 & 0.49 & 0.12\tabularnewline
901 & Guugu Yimidhirr & 0.02 & 26 & 19 & 0.90 & 0.52 &
0.13\tabularnewline
1025 & Waalubal & 0.00 & 372 & 11 & 0.55 & 0.83 & 0.13\tabularnewline
962 & Gunya & 0.01 & 11 & 25 & 0.81 & 0.31 & 0.13\tabularnewline
1024 & Ngardily & 0.01 & 5 & 22 & 1.00 & 0.45 & 0.13\tabularnewline
853 & Lardil & 0.00 & 50 & 25 & 1.00 & 0.40 & 0.13\tabularnewline
963 & Kungkari & 0.01 & 50 & 7 & 0.29 & 0.78 & 0.13\tabularnewline
1009 & Gamilaraay & 0.00 & 20 & 21 & 1.00 & 0.46 & 0.13\tabularnewline
546 & Yanyuwa & 0.00 & 27 & 23 & 1.00 & 0.44 & 0.13\tabularnewline
856 & Patjtjamalh & 0.00 & 2 & 25 & 0.93 & 0.27 & 0.13\tabularnewline
99 & Bidyara & 0.00 & 7 & 19 & 1.00 & 0.51 & 0.13\tabularnewline
778 & Jiwarli & 0.00 & 11 & 26 & 1.00 & 0.25 & 0.13\tabularnewline
918 & Atampaya & 0.01 & 1 & 25 & 1.00 & 0.26 & 0.14\tabularnewline
940 & Yawijibaya & 0.01 & 10 & 18 & 0.78 & 0.41 & 0.14\tabularnewline
1032 & Kuku Yalanji & 0.00 & 378 & 12 & 0.75 & 0.76 &
0.14\tabularnewline
288 & Wangkatja & 0.00 & 48 & 23 & 1.00 & 0.32 & 0.14\tabularnewline
237 & Warluwarra & 0.00 & 23 & 26 & 0.79 & 0.15 & 0.14\tabularnewline
1026 & Gidabal & 0.00 & 284 & 14 & 0.70 & 0.61 & 0.14\tabularnewline
200 & Western Arrernte & 0.01 & 8 & 25 & 1.00 & 0.19 &
0.14\tabularnewline
958 & Margany & 0.01 & 7 & 24 & 0.80 & 0.18 & 0.14\tabularnewline
443 & Payungu & 0.01 & 5 & 26 & 1.00 & 0.18 & 0.14\tabularnewline
563 & Ngarla & 0.00 & 2 & 23 & 1.00 & 0.27 & 0.14\tabularnewline
519 & Nukunu & 0.01 & 53 & 9 & 0.32 & 0.67 & 0.14\tabularnewline
1019 & Walmajarri & 0.00 & 226 & 20 & 0.87 & 0.40 & 0.14\tabularnewline
957 & Ngaanyatjarra & 0.00 & 57 & 23 & 1.00 & 0.25 & 0.14\tabularnewline
919 & Angkamuthi & 0.01 & 5 & 26 & 1.00 & 0.15 & 0.14\tabularnewline
89 & Bunuba & 0.01 & 7 & 24 & 1.00 & 0.20 & 0.14\tabularnewline
13 & Dyirbal & 0.01 & 59 & 16 & 1.00 & 0.51 & 0.14\tabularnewline
905 & Malkana & 0.01 & 2 & 25 & 1.00 & 0.15 & 0.15\tabularnewline
985 & Yaygir & 0.00 & 107 & 17 & 0.85 & 0.36 & 0.15\tabularnewline
762 & Kariyarra & 0.01 & 2 & 24 & 1.00 & 0.17 & 0.15\tabularnewline
1016 & Tharrkari & 0.01 & 2 & 32 & 1.00 & 0.05 & 0.15\tabularnewline
910 & Nungali & 0.01 & 115 & 14 & 0.88 & 0.61 & 0.15\tabularnewline
118 & Badimaya & 0.01 & 3 & 24 & 1.00 & 0.17 & 0.15\tabularnewline
787 & Jawoyn & 0.00 & 64 & 27 & 1.00 & 0.11 & 0.15\tabularnewline
417 & Yindjibarndi & 0.01 & 17 & 25 & 1.00 & 0.15 & 0.15\tabularnewline
982 & Nhirrpi & 0.02 & 1 & 30 & 1.00 & 0.06 & 0.15\tabularnewline
920 & Yadhaykenu & 0.01 & 2 & 25 & 1.00 & 0.14 & 0.15\tabularnewline
117 & Wirangu & 0.01 & 4 & 23 & 1.00 & 0.18 & 0.15\tabularnewline
592 & Muruwari & 0.00 & 66 & 20 & 0.80 & 0.25 & 0.15\tabularnewline
598 & Yandruwandha & 0.00 & 92 & 14 & 0.47 & 0.35 & 0.15\tabularnewline
929 & Wanyjirra & 0.00 & 36 & 21 & 1.00 & 0.25 & 0.15\tabularnewline
949 & Kok Nar & 0.01 & 13 & 21 & 1.00 & 0.23 & 0.15\tabularnewline
518 & Yarluyandi & 0.01 & 4 & 23 & 1.00 & 0.16 & 0.15\tabularnewline
228 & Warriyangga & 0.01 & 1 & 26 & 1.00 & 0.11 & 0.15\tabularnewline
252 & Warlmanpa & 0.00 & 6 & 22 & 0.79 & 0.18 & 0.15\tabularnewline
475 & Southern Paakintyi & 0.00 & 106 & 18 & 0.67 & 0.21 &
0.15\tabularnewline
400 & Thalanyji & 0.00 & 161 & 7 & 0.27 & 0.59 & 0.15\tabularnewline
85 & Burarra & 0.00 & 284 & 21 & 0.81 & 0.18 & 0.15\tabularnewline
493 & Nyiyaparli & 0.01 & 1 & 22 & 1.00 & 0.17 & 0.15\tabularnewline
462 & Panyjima & 0.01 & 106 & 8 & 0.32 & 0.60 & 0.15\tabularnewline
113 & Yulparija & 0.00 & 151 & 20 & 0.87 & 0.22 & 0.15\tabularnewline
645 & Malyangapa & 0.01 & 57 & 7 & 0.28 & 0.60 & 0.15\tabularnewline
835 & Gugu Badhun & 0.01 & 28 & 17 & 1.00 & 0.36 & 0.15\tabularnewline
1030 & Putijarra & 0.00 & 1 & 25 & 1.00 & 0.10 & 0.15\tabularnewline
242 & Warlpiri & 0.00 & 63 & 24 & 1.00 & 0.33 & 0.15\tabularnewline
849 & Waanyi & 0.00 & 211 & 15 & 0.75 & 0.39 & 0.15\tabularnewline
433 & Pitta Pitta & 0.00 & 150 & 7 & 0.28 & 0.60 & 0.16\tabularnewline
977 & Warndarrang & 0.01 & 35 & 19 & 1.00 & 0.23 & 0.16\tabularnewline
1008 & Yuwaalaraay & 0.00 & 39 & 21 & 1.00 & 0.19 & 0.16\tabularnewline
1029 & Martuthunira & 0.00 & 8 & 26 & 1.00 & 0.08 & 0.16\tabularnewline
930 & Purduna & 0.01 & 12 & 26 & 1.00 & 0.08 & 0.16\tabularnewline
1042 & Thaayorre & 0.00 & 208 & 24 & 0.92 & 0.09 & 0.16\tabularnewline
914 & Yinhawangka & 0.00 & 220 & 8 & 0.31 & 0.57 & 0.16\tabularnewline
618 & Mirniny & 0.01 & 1 & 25 & 1.00 & 0.07 & 0.16\tabularnewline
572 & Ngamini & 0.00 & 17 & 22 & 0.96 & 0.10 & 0.16\tabularnewline
734 & Kukatja & 0.00 & 35 & 23 & 1.00 & 0.22 & 0.16\tabularnewline
269 & Wangkumara & 0.01 & 4 & 30 & 1.00 & 0.02 & 0.16\tabularnewline
363 & Yir Yoront & 0.00 & 44 & 25 & 0.96 & 0.04 & 0.17\tabularnewline
162 & Adnyamathanha & 0.00 & 63 & 29 & 1.00 & 0.02 & 0.17\tabularnewline
554 & Ngarluma & 0.00 & 30 & 23 & 1.00 & 0.08 & 0.17\tabularnewline
507 & Nyangumarta & 0.00 & 307 & 9 & 0.43 & 0.54 & 0.17\tabularnewline
1007 & Yuwaliyaay & 0.00 & 33 & 21 & 1.00 & 0.09 & 0.17\tabularnewline
865 & Diyari & 0.01 & 13 & 23 & 0.92 & 0.04 & 0.17\tabularnewline
866 & Thirarri & 0.01 & 13 & 23 & 0.92 & 0.03 & 0.17\tabularnewline
534 & Nhanda & 0.00 & 106 & 6 & 0.18 & 0.52 & 0.18\tabularnewline
1006 & Central Arrernte & 0.00 & 27 & 25 & 1.00 & 0.02 &
0.18\tabularnewline
1021 & Watjarri & 0.00 & 5 & 26 & 1.00 & 0.02 & 0.18\tabularnewline
922 & Nakara & 0.00 & 14 & 26 & 1.00 & 0.02 & 0.18\tabularnewline
101 & Butchulla & 0.01 & 85 & 15 & 0.62 & 0.14 & 0.19\tabularnewline
91 & Bularnu & 0.01 & 2 & 30 & 1.00 & 0.00 & 0.19\tabularnewline
983 & Nhangu & 0.00 & 130 & 19 & 0.61 & 0.02 & 0.19\tabularnewline
1040 & Ngarinyin & 0.00 & 2 & 27 & 1.00 & 0.05 & 0.20\tabularnewline
\bottomrule
\end{longtable}

\newpage

\textbf{Table A.3.9. Comparing exponential and lognormal distributions
using Vuong's likelihood ratio test.}

* \(p\) \textless{} 0.05 after Bonferroni correction. ** \(p\)
\textless{} 0.01 after Bonferroni correction.

\begin{longtable}[]{@{}rlrrl@{}}
\toprule
\textbf{lex ID} & \textbf{language variety} & \(R\) & \(p\) &
\textbf{signif.}\tabularnewline
\midrule
\endhead
967 & Thaynakwithi & 3.88 & 0.000 & **\tabularnewline
81 & Dalabon & 3.83 & 0.000 & *\tabularnewline
650 & Linngithigh & 3.63 & 0.000 & *\tabularnewline
923 & Matngele & 2.58 & 0.005 &\tabularnewline
1007 & Yuwaliyaay & 2.56 & 0.005 &\tabularnewline
30 & Duungidjawu & 2.53 & 0.006 &\tabularnewline
621 & Mengerrdji & 2.44 & 0.007 &\tabularnewline
493 & Nyiyaparli & 2.40 & 0.008 &\tabularnewline
38 & Djabugay & 2.39 & 0.008 &\tabularnewline
1008 & Yuwaalaraay & 2.37 & 0.009 &\tabularnewline
911 & Nyawaygi & 2.31 & 0.010 &\tabularnewline
305 & Western Wakaya & 2.14 & 0.016 &\tabularnewline
113 & Yulparija & 2.06 & 0.020 &\tabularnewline
620 & Miriwoong & 2.03 & 0.021 &\tabularnewline
737 & Kukatj & 1.99 & 0.023 &\tabularnewline
847 & Ngalakgan & 1.98 & 0.024 &\tabularnewline
853 & Lardil & 1.96 & 0.025 &\tabularnewline
232 & Warnman & 1.90 & 0.028 &\tabularnewline
563 & Ngarla & 1.89 & 0.029 &\tabularnewline
12 & Erre & 1.89 & 0.029 &\tabularnewline
851 & Bilinarra & 1.88 & 0.030 &\tabularnewline
565 & Ngarinyman & 1.86 & 0.031 &\tabularnewline
170 & Wik-Ngathan & 1.86 & 0.032 &\tabularnewline
852 & Gurindji & 1.85 & 0.032 &\tabularnewline
928 & Bakanh & 1.80 & 0.036 &\tabularnewline
1019 & Walmajarri & 1.79 & 0.037 &\tabularnewline
848 & Wagiman & 1.70 & 0.044 &\tabularnewline
752 & Kija & 1.69 & 0.045 &\tabularnewline
1030 & Putijarra & 1.68 & 0.046 &\tabularnewline
1012 & Warrgamay & 1.67 & 0.048 &\tabularnewline
863 & Marra & 1.63 & 0.051 &\tabularnewline
965 & Oykangand & 1.62 & 0.052 &\tabularnewline
734 & Kukatja & 1.60 & 0.055 &\tabularnewline
1009 & Gamilaraay & 1.56 & 0.060 &\tabularnewline
1011 & Yorta Yorta & 1.51 & 0.066 &\tabularnewline
941 & Wambaya & 1.49 & 0.068 &\tabularnewline
606 & Mudburra & 1.49 & 0.069 &\tabularnewline
949 & Kok Nar & 1.47 & 0.071 &\tabularnewline
767 & Karajarri & 1.43 & 0.076 &\tabularnewline
31 & Djinang & 1.37 & 0.085 &\tabularnewline
787 & Jawoyn & 1.32 & 0.094 &\tabularnewline
642 & Mangala & 1.24 & 0.108 &\tabularnewline
760 & Kartujarra & 1.21 & 0.113 &\tabularnewline
1001 & Ngandi & 1.17 & 0.121 &\tabularnewline
838 & Gooniyandi & 1.15 & 0.125 &\tabularnewline
790 & Jaru & 1.13 & 0.129 &\tabularnewline
1023 & Wubuy & 1.11 & 0.134 &\tabularnewline
921 & Gurr-Goni & 1.08 & 0.141 &\tabularnewline
762 & Kariyarra & 1.07 & 0.143 &\tabularnewline
1021 & Watjarri & 1.05 & 0.147 &\tabularnewline
800 & Guwamu & 1.05 & 0.147 &\tabularnewline
856 & Patjtjamalh & 1.01 & 0.155 &\tabularnewline
952 & Ngawun & 0.95 & 0.170 &\tabularnewline
978 & Wotjobaluk & 0.95 & 0.172 &\tabularnewline
1002 & Yintyingka & 0.94 & 0.174 &\tabularnewline
849 & Waanyi & 0.92 & 0.178 &\tabularnewline
857 & Amurdak & 0.91 & 0.182 &\tabularnewline
507 & Nyangumarta & 0.90 & 0.185 &\tabularnewline
1042 & Thaayorre & 0.88 & 0.189 &\tabularnewline
377 & Umpila & 0.88 & 0.189 &\tabularnewline
972 & Ogh Unyjan & 0.88 & 0.190 &\tabularnewline
934 & Urningangg & 0.87 & 0.193 &\tabularnewline
841 & Worrorra & 0.81 & 0.208 &\tabularnewline
966 & Wik Mungkan & 0.81 & 0.208 &\tabularnewline
1031 & Ngadjunmaya & 0.81 & 0.210 &\tabularnewline
540 & Ngiyambaa & 0.78 & 0.217 &\tabularnewline
917 & Nyamal & 0.77 & 0.220 &\tabularnewline
1003 & Murrinh-patha & 0.77 & 0.220 &\tabularnewline
462 & Panyjima & 0.77 & 0.221 &\tabularnewline
1043 & Mbabaram & 0.75 & 0.226 &\tabularnewline
495 & Nyikina & 0.75 & 0.226 &\tabularnewline
363 & Yir Yoront & 0.70 & 0.243 &\tabularnewline
910 & Nungali & 0.69 & 0.244 &\tabularnewline
996 & Emmi & 0.66 & 0.255 &\tabularnewline
914 & Yinhawangka & 0.66 & 0.256 &\tabularnewline
242 & Warlpiri & 0.66 & 0.256 &\tabularnewline
1026 & Gidabal & 0.65 & 0.256 &\tabularnewline
99 & Bidyara & 0.65 & 0.259 &\tabularnewline
964 & Olkol & 0.64 & 0.262 &\tabularnewline
618 & Mirniny & 0.62 & 0.267 &\tabularnewline
94 & Biri & 0.62 & 0.268 &\tabularnewline
1025 & Waalubal & 0.60 & 0.273 &\tabularnewline
963 & Kungkari & 0.58 & 0.281 &\tabularnewline
979 & Mawng & 0.57 & 0.285 &\tabularnewline
228 & Warriyangga & 0.54 & 0.293 &\tabularnewline
926 & Limilngan & 0.54 & 0.296 &\tabularnewline
945 & Wiri & 0.54 & 0.296 &\tabularnewline
929 & Wanyjirra & 0.53 & 0.299 &\tabularnewline
740 & Kugu Nganhcara & 0.53 & 0.299 &\tabularnewline
63 & Dharumbal & 0.50 & 0.308 &\tabularnewline
935 & Rembarrnga & 0.48 & 0.317 &\tabularnewline
631 & Yalarnnga & 0.47 & 0.319 &\tabularnewline
697 & Kurrama & 0.47 & 0.321 &\tabularnewline
985 & Yaygir & 0.45 & 0.326 &\tabularnewline
5 & Gangulu & 0.44 & 0.332 &\tabularnewline
918 & Atampaya & 0.39 & 0.350 &\tabularnewline
1040 & Ngarinyin & 0.37 & 0.356 &\tabularnewline
105 & Bardi & 0.36 & 0.358 &\tabularnewline
845 & Iwaidja & 0.36 & 0.361 &\tabularnewline
13 & Dyirbal & 0.35 & 0.362 &\tabularnewline
915 & Alawa & 0.34 & 0.366 &\tabularnewline
118 & Badimaya & 0.32 & 0.373 &\tabularnewline
265 & Wardaman & 0.32 & 0.375 &\tabularnewline
946 & Kurtjar & 0.30 & 0.381 &\tabularnewline
1029 & Martuthunira & 0.28 & 0.392 &\tabularnewline
835 & Gugu Badhun & 0.25 & 0.401 &\tabularnewline
546 & Yanyuwa & 0.25 & 0.403 &\tabularnewline
204 & Wemba Wemba & 0.23 & 0.409 &\tabularnewline
778 & Jiwarli & 0.21 & 0.416 &\tabularnewline
417 & Yindjibarndi & 0.21 & 0.417 &\tabularnewline
433 & Pitta Pitta & 0.21 & 0.418 &\tabularnewline
905 & Malkana & 0.20 & 0.422 &\tabularnewline
89 & Bunuba & 0.16 & 0.435 &\tabularnewline
611 & Anguthimri & 0.13 & 0.447 &\tabularnewline
443 & Payungu & 0.13 & 0.447 &\tabularnewline
412 & Ritharrngu & 0.10 & 0.459 &\tabularnewline
400 & Thalanyji & 0.10 & 0.462 &\tabularnewline
101 & Butchulla & 0.07 & 0.471 &\tabularnewline
1024 & Ngardily & 0.01 & 0.495 &\tabularnewline
288 & Wangkatja & 0.00 & 0.501 &\tabularnewline
656 & Kuugu Ya'u & -0.01 & 0.504 &\tabularnewline
957 & Ngaanyatjarra & -0.01 & 0.505 &\tabularnewline
920 & Yadhaykenu & -0.02 & 0.509 &\tabularnewline
925 & Larrakia & -0.03 & 0.511 &\tabularnewline
427 & Yidiny & -0.03 & 0.513 &\tabularnewline
1018 & Djapu & -0.04 & 0.517 &\tabularnewline
117 & Wirangu & -0.07 & 0.530 &\tabularnewline
807 & Gupapuyngu & -0.08 & 0.530 &\tabularnewline
821 & Gumbaynggir & -0.09 & 0.535 &\tabularnewline
62 & Dhay'yi & -0.10 & 0.541 &\tabularnewline
645 & Malyangapa & -0.11 & 0.543 &\tabularnewline
982 & Nhirrpi & -0.12 & 0.549 &\tabularnewline
77 & Dhangu & -0.14 & 0.555 &\tabularnewline
940 & Yawijibaya & -0.18 & 0.570 &\tabularnewline
901 & Guugu Yimidhirr & -0.18 & 0.571 &\tabularnewline
519 & Nukunu & -0.20 & 0.581 &\tabularnewline
968 & Ogh Angkula & -0.21 & 0.581 &\tabularnewline
919 & Angkamuthi & -0.26 & 0.602 &\tabularnewline
1032 & Kuku Yalanji & -0.26 & 0.603 &\tabularnewline
85 & Burarra & -0.27 & 0.607 &\tabularnewline
930 & Purduna & -0.33 & 0.628 &\tabularnewline
943 & Pintupi & -0.33 & 0.628 &\tabularnewline
598 & Yandruwandha & -0.34 & 0.631 &\tabularnewline
939 & Unggumi & -0.34 & 0.634 &\tabularnewline
927 & Tiwi & -0.35 & 0.636 &\tabularnewline
977 & Warndarrang & -0.35 & 0.636 &\tabularnewline
518 & Yarluyandi & -0.38 & 0.649 &\tabularnewline
592 & Muruwari & -0.40 & 0.654 &\tabularnewline
922 & Nakara & -0.45 & 0.673 &\tabularnewline
534 & Nhanda & -0.45 & 0.674 &\tabularnewline
554 & Ngarluma & -0.47 & 0.679 &\tabularnewline
572 & Ngamini & -0.49 & 0.689 &\tabularnewline
744 & Koko Bera & -0.50 & 0.691 &\tabularnewline
252 & Warlmanpa & -0.55 & 0.709 &\tabularnewline
771 & Kalkatungu & -0.59 & 0.722 &\tabularnewline
91 & Bularnu & -0.59 & 0.724 &\tabularnewline
269 & Wangkumara & -0.64 & 0.740 &\tabularnewline
958 & Margany & -0.66 & 0.744 &\tabularnewline
237 & Warluwarra & -0.67 & 0.749 &\tabularnewline
983 & Nhangu & -0.72 & 0.765 &\tabularnewline
1016 & Tharrkari & -0.85 & 0.803 &\tabularnewline
475 & Southern Paakintyi & -0.99 & 0.839 &\tabularnewline
962 & Gunya & -1.02 & 0.846 &\tabularnewline
865 & Diyari & -1.06 & 0.855 &\tabularnewline
866 & Thirarri & -1.06 & 0.855 &\tabularnewline
200 & Western Arrernte & -1.06 & 0.855 &\tabularnewline
162 & Adnyamathanha & -1.34 & 0.909 &\tabularnewline
1006 & Central Arrernte & -1.60 & 0.946 &\tabularnewline
\bottomrule
\end{longtable}

\newpage

\textbf{Table A.3.10. Comparing exponential and lognormal distributions
with \(x_{min}\) using Vuong's likelihood ratio test.}

Part A. Using \(x_{min}\) from the exponential fit. \(R > 0\) favours
exponential.

* \(p\) \textless{} 0.05 after Bonferroni correction. ** \(p\)
\textless{} 0.01 after Bonferroni correction.

\begin{longtable}[]{@{}rlrrl@{}}
\toprule
\textbf{lex ID} & \textbf{language variety} & \(R\) & \(p\) &
\textbf{signif.}\tabularnewline
\midrule
\endhead
856 & Patjtjamalh & 2.68 & 0.004 &\tabularnewline
1007 & Yuwaliyaay & 2.56 & 0.005 &\tabularnewline
493 & Nyiyaparli & 2.40 & 0.008 &\tabularnewline
1008 & Yuwaalaraay & 2.37 & 0.009 &\tabularnewline
964 & Olkol & 2.21 & 0.013 &\tabularnewline
305 & Western Wakaya & 2.14 & 0.016 &\tabularnewline
853 & Lardil & 1.96 & 0.025 &\tabularnewline
563 & Ngarla & 1.89 & 0.029 &\tabularnewline
12 & Erre & 1.89 & 0.029 &\tabularnewline
1030 & Putijarra & 1.68 & 0.046 &\tabularnewline
252 & Warlmanpa & 1.60 & 0.055 &\tabularnewline
734 & Kukatja & 1.60 & 0.055 &\tabularnewline
1009 & Gamilaraay & 1.56 & 0.060 &\tabularnewline
606 & Mudburra & 1.49 & 0.069 &\tabularnewline
934 & Urningangg & 1.47 & 0.071 &\tabularnewline
917 & Nyamal & 1.47 & 0.071 &\tabularnewline
949 & Kok Nar & 1.47 & 0.071 &\tabularnewline
1001 & Ngandi & 1.40 & 0.080 &\tabularnewline
540 & Ngiyambaa & 1.39 & 0.082 &\tabularnewline
31 & Djinang & 1.37 & 0.085 &\tabularnewline
965 & Oykangand & 1.37 & 0.086 &\tabularnewline
941 & Wambaya & 1.36 & 0.086 &\tabularnewline
787 & Jawoyn & 1.32 & 0.094 &\tabularnewline
642 & Mangala & 1.24 & 0.108 &\tabularnewline
857 & Amurdak & 1.22 & 0.111 &\tabularnewline
760 & Kartujarra & 1.21 & 0.113 &\tabularnewline
978 & Wotjobaluk & 1.20 & 0.115 &\tabularnewline
838 & Gooniyandi & 1.15 & 0.125 &\tabularnewline
762 & Kariyarra & 1.07 & 0.143 &\tabularnewline
1023 & Wubuy & 1.05 & 0.146 &\tabularnewline
1021 & Watjarri & 1.05 & 0.147 &\tabularnewline
800 & Guwamu & 1.05 & 0.147 &\tabularnewline
790 & Jaru & 0.95 & 0.171 &\tabularnewline
852 & Gurindji & 0.93 & 0.176 &\tabularnewline
1042 & Thaayorre & 0.86 & 0.194 &\tabularnewline
940 & Yawijibaya & 0.82 & 0.207 &\tabularnewline
841 & Worrorra & 0.81 & 0.208 &\tabularnewline
1002 & Yintyingka & 0.81 & 0.209 &\tabularnewline
1031 & Ngadjunmaya & 0.81 & 0.210 &\tabularnewline
926 & Limilngan & 0.78 & 0.218 &\tabularnewline
1043 & Mbabaram & 0.78 & 0.219 &\tabularnewline
1003 & Murrinh-patha & 0.77 & 0.220 &\tabularnewline
737 & Kukatj & 0.74 & 0.230 &\tabularnewline
495 & Nyikina & 0.72 & 0.236 &\tabularnewline
952 & Ngawun & 0.71 & 0.239 &\tabularnewline
427 & Yidiny & 0.70 & 0.242 &\tabularnewline
62 & Dhay'yi & 0.68 & 0.250 &\tabularnewline
996 & Emmi & 0.66 & 0.255 &\tabularnewline
242 & Warlpiri & 0.66 & 0.256 &\tabularnewline
99 & Bidyara & 0.65 & 0.259 &\tabularnewline
618 & Mirniny & 0.62 & 0.267 &\tabularnewline
697 & Kurrama & 0.62 & 0.268 &\tabularnewline
94 & Biri & 0.62 & 0.268 &\tabularnewline
81 & Dalabon & 0.58 & 0.280 &\tabularnewline
979 & Mawng & 0.57 & 0.285 &\tabularnewline
228 & Warriyangga & 0.54 & 0.293 &\tabularnewline
925 & Larrakia & 0.54 & 0.295 &\tabularnewline
611 & Anguthimri & 0.54 & 0.295 &\tabularnewline
945 & Wiri & 0.54 & 0.296 &\tabularnewline
645 & Malyangapa & 0.54 & 0.296 &\tabularnewline
105 & Bardi & 0.53 & 0.297 &\tabularnewline
929 & Wanyjirra & 0.53 & 0.299 &\tabularnewline
400 & Thalanyji & 0.50 & 0.309 &\tabularnewline
30 & Duungidjawu & 0.48 & 0.317 &\tabularnewline
631 & Yalarnnga & 0.47 & 0.319 &\tabularnewline
963 & Kungkari & 0.46 & 0.324 &\tabularnewline
5 & Gangulu & 0.44 & 0.332 &\tabularnewline
918 & Atampaya & 0.39 & 0.350 &\tabularnewline
63 & Dharumbal & 0.37 & 0.355 &\tabularnewline
1040 & Ngarinyin & 0.37 & 0.356 &\tabularnewline
845 & Iwaidja & 0.36 & 0.361 &\tabularnewline
13 & Dyirbal & 0.35 & 0.362 &\tabularnewline
118 & Badimaya & 0.32 & 0.373 &\tabularnewline
740 & Kugu Nganhcara & 0.31 & 0.377 &\tabularnewline
923 & Matngele & 0.29 & 0.386 &\tabularnewline
946 & Kurtjar & 0.28 & 0.389 &\tabularnewline
1029 & Martuthunira & 0.28 & 0.392 &\tabularnewline
621 & Mengerrdji & 0.26 & 0.398 &\tabularnewline
835 & Gugu Badhun & 0.25 & 0.401 &\tabularnewline
546 & Yanyuwa & 0.25 & 0.403 &\tabularnewline
911 & Nyawaygi & 0.24 & 0.404 &\tabularnewline
433 & Pitta Pitta & 0.24 & 0.405 &\tabularnewline
363 & Yir Yoront & 0.24 & 0.406 &\tabularnewline
778 & Jiwarli & 0.21 & 0.416 &\tabularnewline
417 & Yindjibarndi & 0.21 & 0.417 &\tabularnewline
1012 & Warrgamay & 0.21 & 0.419 &\tabularnewline
905 & Malkana & 0.20 & 0.422 &\tabularnewline
901 & Guugu Yimidhirr & 0.20 & 0.422 &\tabularnewline
821 & Gumbaynggir & 0.19 & 0.424 &\tabularnewline
89 & Bunuba & 0.16 & 0.435 &\tabularnewline
752 & Kija & 0.16 & 0.437 &\tabularnewline
412 & Ritharrngu & 0.14 & 0.444 &\tabularnewline
620 & Miriwoong & 0.14 & 0.444 &\tabularnewline
443 & Payungu & 0.13 & 0.447 &\tabularnewline
972 & Ogh Unyjan & 0.12 & 0.452 &\tabularnewline
38 & Djabugay & 0.12 & 0.452 &\tabularnewline
232 & Warnman & 0.12 & 0.453 &\tabularnewline
915 & Alawa & 0.11 & 0.456 &\tabularnewline
1032 & Kuku Yalanji & 0.05 & 0.479 &\tabularnewline
1025 & Waalubal & 0.05 & 0.482 &\tabularnewline
534 & Nhanda & 0.05 & 0.482 &\tabularnewline
507 & Nyangumarta & 0.04 & 0.485 &\tabularnewline
939 & Unggumi & 0.03 & 0.486 &\tabularnewline
1024 & Ngardily & 0.01 & 0.495 &\tabularnewline
288 & Wangkatja & 0.00 & 0.501 &\tabularnewline
744 & Koko Bera & 0.00 & 0.502 &\tabularnewline
656 & Kuugu Ya'u & -0.01 & 0.504 &\tabularnewline
957 & Ngaanyatjarra & -0.01 & 0.505 &\tabularnewline
920 & Yadhaykenu & -0.02 & 0.509 &\tabularnewline
1018 & Djapu & -0.04 & 0.517 &\tabularnewline
204 & Wemba Wemba & -0.05 & 0.519 &\tabularnewline
170 & Wik-Ngathan & -0.05 & 0.522 &\tabularnewline
117 & Wirangu & -0.07 & 0.530 &\tabularnewline
1026 & Gidabal & -0.08 & 0.532 &\tabularnewline
914 & Yinhawangka & -0.09 & 0.538 &\tabularnewline
982 & Nhirrpi & -0.12 & 0.549 &\tabularnewline
377 & Umpila & -0.13 & 0.551 &\tabularnewline
1011 & Yorta Yorta & -0.13 & 0.552 &\tabularnewline
77 & Dhangu & -0.14 & 0.555 &\tabularnewline
966 & Wik Mungkan & -0.15 & 0.561 &\tabularnewline
985 & Yaygir & -0.18 & 0.570 &\tabularnewline
592 & Muruwari & -0.18 & 0.570 &\tabularnewline
807 & Gupapuyngu & -0.18 & 0.571 &\tabularnewline
650 & Linngithigh & -0.20 & 0.578 &\tabularnewline
968 & Ogh Angkula & -0.21 & 0.581 &\tabularnewline
935 & Rembarrnga & -0.21 & 0.582 &\tabularnewline
462 & Panyjima & -0.21 & 0.584 &\tabularnewline
848 & Wagiman & -0.21 & 0.585 &\tabularnewline
863 & Marra & -0.23 & 0.590 &\tabularnewline
919 & Angkamuthi & -0.26 & 0.602 &\tabularnewline
519 & Nukunu & -0.29 & 0.615 &\tabularnewline
767 & Karajarri & -0.30 & 0.618 &\tabularnewline
928 & Bakanh & -0.31 & 0.621 &\tabularnewline
930 & Purduna & -0.33 & 0.628 &\tabularnewline
910 & Nungali & -0.34 & 0.632 &\tabularnewline
927 & Tiwi & -0.35 & 0.636 &\tabularnewline
977 & Warndarrang & -0.35 & 0.636 &\tabularnewline
518 & Yarluyandi & -0.38 & 0.649 &\tabularnewline
265 & Wardaman & -0.42 & 0.665 &\tabularnewline
922 & Nakara & -0.45 & 0.673 &\tabularnewline
983 & Nhangu & -0.46 & 0.679 &\tabularnewline
554 & Ngarluma & -0.47 & 0.679 &\tabularnewline
851 & Bilinarra & -0.47 & 0.681 &\tabularnewline
962 & Gunya & -0.49 & 0.687 &\tabularnewline
958 & Margany & -0.49 & 0.687 &\tabularnewline
565 & Ngarinyman & -0.53 & 0.701 &\tabularnewline
967 & Thaynakwithi & -0.54 & 0.706 &\tabularnewline
598 & Yandruwandha & -0.55 & 0.709 &\tabularnewline
921 & Gurr-Goni & -0.57 & 0.715 &\tabularnewline
849 & Waanyi & -0.58 & 0.720 &\tabularnewline
572 & Ngamini & -0.59 & 0.721 &\tabularnewline
847 & Ngalakgan & -0.59 & 0.723 &\tabularnewline
91 & Bularnu & -0.59 & 0.724 &\tabularnewline
269 & Wangkumara & -0.64 & 0.740 &\tabularnewline
475 & Southern Paakintyi & -0.66 & 0.745 &\tabularnewline
237 & Warluwarra & -0.78 & 0.783 &\tabularnewline
101 & Butchulla & -0.79 & 0.786 &\tabularnewline
85 & Burarra & -0.81 & 0.791 &\tabularnewline
113 & Yulparija & -0.81 & 0.792 &\tabularnewline
943 & Pintupi & -0.84 & 0.799 &\tabularnewline
1016 & Tharrkari & -0.85 & 0.803 &\tabularnewline
865 & Diyari & -0.98 & 0.837 &\tabularnewline
866 & Thirarri & -0.99 & 0.839 &\tabularnewline
1019 & Walmajarri & -1.00 & 0.841 &\tabularnewline
771 & Kalkatungu & -1.05 & 0.852 &\tabularnewline
200 & Western Arrernte & -1.06 & 0.855 &\tabularnewline
162 & Adnyamathanha & -1.34 & 0.909 &\tabularnewline
1006 & Central Arrernte & -1.60 & 0.946 &\tabularnewline
\bottomrule
\end{longtable}

\newpage

\textbf{Table A.3.11. Comparing exponential and lognormal distributions
with \(x_{min}\) using Vuong's likelihood ratio test.}

Part B. Using \(x_{min}\) from the lognormal fit. \(R > 0\) favours
lognormal.

* \(p\) \textless{} 0.05 after Bonferroni correction. ** \(p\)
\textless{} 0.01 after Bonferroni correction.

\begin{longtable}[]{@{}rlrrl@{}}
\toprule
\textbf{lex ID} & \textbf{language variety} & \(R\) & \(p\) &
\textbf{signif.}\tabularnewline
\midrule
\endhead
1021 & Watjarri & 1.45 & 0.074 &\tabularnewline
762 & Kariyarra & 1.37 & 0.085 &\tabularnewline
919 & Angkamuthi & 1.36 & 0.087 &\tabularnewline
162 & Adnyamathanha & 1.34 & 0.091 &\tabularnewline
1016 & Tharrkari & 1.32 & 0.093 &\tabularnewline
905 & Malkana & 1.32 & 0.094 &\tabularnewline
91 & Bularnu & 1.29 & 0.099 &\tabularnewline
1006 & Central Arrernte & 1.27 & 0.102 &\tabularnewline
914 & Yinhawangka & 1.23 & 0.109 &\tabularnewline
400 & Thalanyji & 1.23 & 0.109 &\tabularnewline
957 & Ngaanyatjarra & 1.21 & 0.113 &\tabularnewline
1030 & Putijarra & 1.21 & 0.113 &\tabularnewline
519 & Nukunu & 1.20 & 0.116 &\tabularnewline
228 & Warriyangga & 1.17 & 0.122 &\tabularnewline
507 & Nyangumarta & 1.16 & 0.124 &\tabularnewline
288 & Wangkatja & 1.15 & 0.125 &\tabularnewline
922 & Nakara & 1.11 & 0.132 &\tabularnewline
443 & Payungu & 1.11 & 0.133 &\tabularnewline
269 & Wangkumara & 1.08 & 0.139 &\tabularnewline
200 & Western Arrernte & 1.06 & 0.145 &\tabularnewline
866 & Thirarri & 1.06 & 0.145 &\tabularnewline
865 & Diyari & 1.06 & 0.145 &\tabularnewline
242 & Warlpiri & 1.06 & 0.145 &\tabularnewline
363 & Yir Yoront & 1.05 & 0.146 &\tabularnewline
778 & Jiwarli & 1.05 & 0.147 &\tabularnewline
534 & Nhanda & 1.02 & 0.154 &\tabularnewline
563 & Ngarla & 1.01 & 0.156 &\tabularnewline
943 & Pintupi & 1.00 & 0.158 &\tabularnewline
1019 & Walmajarri & 1.00 & 0.159 &\tabularnewline
838 & Gooniyandi & 0.99 & 0.161 &\tabularnewline
1024 & Ngardily & 0.98 & 0.164 &\tabularnewline
417 & Yindjibarndi & 0.97 & 0.165 &\tabularnewline
918 & Atampaya & 0.96 & 0.168 &\tabularnewline
598 & Yandruwandha & 0.95 & 0.171 &\tabularnewline
771 & Kalkatungu & 0.94 & 0.172 &\tabularnewline
734 & Kukatja & 0.94 & 0.173 &\tabularnewline
967 & Thaynakwithi & 0.93 & 0.176 &\tabularnewline
807 & Gupapuyngu & 0.92 & 0.178 &\tabularnewline
982 & Nhirrpi & 0.89 & 0.187 &\tabularnewline
940 & Yawijibaya & 0.88 & 0.189 &\tabularnewline
606 & Mudburra & 0.85 & 0.196 &\tabularnewline
117 & Wirangu & 0.85 & 0.197 &\tabularnewline
493 & Nyiyaparli & 0.83 & 0.203 &\tabularnewline
31 & Djinang & 0.82 & 0.206 &\tabularnewline
475 & Southern Paakintyi & 0.82 & 0.207 &\tabularnewline
963 & Kungkari & 0.82 & 0.207 &\tabularnewline
118 & Badimaya & 0.81 & 0.208 &\tabularnewline
81 & Dalabon & 0.80 & 0.213 &\tabularnewline
929 & Wanyjirra & 0.79 & 0.213 &\tabularnewline
101 & Butchulla & 0.79 & 0.214 &\tabularnewline
85 & Burarra & 0.78 & 0.216 &\tabularnewline
237 & Warluwarra & 0.78 & 0.217 &\tabularnewline
845 & Iwaidja & 0.78 & 0.219 &\tabularnewline
972 & Ogh Unyjan & 0.77 & 0.220 &\tabularnewline
611 & Anguthimri & 0.76 & 0.223 &\tabularnewline
917 & Nyamal & 0.76 & 0.223 &\tabularnewline
946 & Kurtjar & 0.76 & 0.225 &\tabularnewline
618 & Mirniny & 0.75 & 0.226 &\tabularnewline
849 & Waanyi & 0.73 & 0.233 &\tabularnewline
572 & Ngamini & 0.72 & 0.234 &\tabularnewline
983 & Nhangu & 0.72 & 0.235 &\tabularnewline
841 & Worrorra & 0.70 & 0.242 &\tabularnewline
787 & Jawoyn & 0.70 & 0.242 &\tabularnewline
985 & Yaygir & 0.70 & 0.243 &\tabularnewline
1031 & Ngadjunmaya & 0.68 & 0.248 &\tabularnewline
767 & Karajarri & 0.64 & 0.260 &\tabularnewline
113 & Yulparija & 0.64 & 0.260 &\tabularnewline
252 & Warlmanpa & 0.64 & 0.262 &\tabularnewline
1011 & Yorta Yorta & 0.63 & 0.265 &\tabularnewline
941 & Wambaya & 0.62 & 0.266 &\tabularnewline
737 & Kukatj & 0.62 & 0.267 &\tabularnewline
697 & Kurrama & 0.62 & 0.268 &\tabularnewline
863 & Marra & 0.62 & 0.268 &\tabularnewline
518 & Yarluyandi & 0.62 & 0.269 &\tabularnewline
927 & Tiwi & 0.60 & 0.274 &\tabularnewline
99 & Bidyara & 0.60 & 0.274 &\tabularnewline
740 & Kugu Nganhcara & 0.59 & 0.277 &\tabularnewline
642 & Mangala & 0.59 & 0.279 &\tabularnewline
592 & Muruwari & 0.58 & 0.281 &\tabularnewline
1001 & Ngandi & 0.58 & 0.281 &\tabularnewline
921 & Gurr-Goni & 0.57 & 0.285 &\tabularnewline
1043 & Mbabaram & 0.56 & 0.288 &\tabularnewline
412 & Ritharrngu & 0.55 & 0.290 &\tabularnewline
170 & Wik-Ngathan & 0.55 & 0.290 &\tabularnewline
848 & Wagiman & 0.55 & 0.292 &\tabularnewline
857 & Amurdak & 0.54 & 0.295 &\tabularnewline
565 & Ngarinyman & 0.53 & 0.299 &\tabularnewline
1025 & Waalubal & 0.52 & 0.302 &\tabularnewline
847 & Ngalakgan & 0.50 & 0.307 &\tabularnewline
265 & Wardaman & 0.49 & 0.311 &\tabularnewline
935 & Rembarrnga & 0.49 & 0.314 &\tabularnewline
966 & Wik Mungkan & 0.49 & 0.314 &\tabularnewline
977 & Warndarrang & 0.48 & 0.317 &\tabularnewline
851 & Bilinarra & 0.47 & 0.319 &\tabularnewline
650 & Linngithigh & 0.47 & 0.321 &\tabularnewline
744 & Koko Bera & 0.46 & 0.322 &\tabularnewline
620 & Miriwoong & 0.46 & 0.323 &\tabularnewline
1008 & Yuwaalaraay & 0.46 & 0.323 &\tabularnewline
934 & Urningangg & 0.44 & 0.328 &\tabularnewline
1040 & Ngarinyin & 0.43 & 0.333 &\tabularnewline
621 & Mengerrdji & 0.39 & 0.347 &\tabularnewline
760 & Kartujarra & 0.38 & 0.351 &\tabularnewline
962 & Gunya & 0.38 & 0.354 &\tabularnewline
930 & Purduna & 0.37 & 0.355 &\tabularnewline
958 & Margany & 0.37 & 0.356 &\tabularnewline
1018 & Djapu & 0.35 & 0.363 &\tabularnewline
952 & Ngawun & 0.35 & 0.364 &\tabularnewline
12 & Erre & 0.35 & 0.364 &\tabularnewline
939 & Unggumi & 0.34 & 0.366 &\tabularnewline
928 & Bakanh & 0.32 & 0.373 &\tabularnewline
910 & Nungali & 0.32 & 0.373 &\tabularnewline
656 & Kuugu Ya'u & 0.30 & 0.381 &\tabularnewline
1026 & Gidabal & 0.28 & 0.389 &\tabularnewline
1032 & Kuku Yalanji & 0.26 & 0.397 &\tabularnewline
923 & Matngele & 0.26 & 0.399 &\tabularnewline
105 & Bardi & 0.24 & 0.406 &\tabularnewline
790 & Jaru & 0.23 & 0.408 &\tabularnewline
462 & Panyjima & 0.21 & 0.416 &\tabularnewline
968 & Ogh Angkula & 0.21 & 0.419 &\tabularnewline
1003 & Murrinh-patha & 0.19 & 0.425 &\tabularnewline
901 & Guugu Yimidhirr & 0.18 & 0.429 &\tabularnewline
30 & Duungidjawu & 0.14 & 0.444 &\tabularnewline
77 & Dhangu & 0.14 & 0.445 &\tabularnewline
204 & Wemba Wemba & 0.13 & 0.447 &\tabularnewline
377 & Umpila & 0.13 & 0.449 &\tabularnewline
852 & Gurindji & 0.13 & 0.449 &\tabularnewline
1023 & Wubuy & 0.12 & 0.451 &\tabularnewline
5 & Gangulu & 0.12 & 0.452 &\tabularnewline
645 & Malyangapa & 0.11 & 0.457 &\tabularnewline
62 & Dhay'yi & 0.10 & 0.459 &\tabularnewline
979 & Mawng & 0.10 & 0.460 &\tabularnewline
821 & Gumbaynggir & 0.09 & 0.465 &\tabularnewline
89 & Bunuba & 0.08 & 0.467 &\tabularnewline
1029 & Martuthunira & 0.07 & 0.472 &\tabularnewline
631 & Yalarnnga & 0.06 & 0.478 &\tabularnewline
856 & Patjtjamalh & 0.04 & 0.483 &\tabularnewline
427 & Yidiny & 0.03 & 0.487 &\tabularnewline
540 & Ngiyambaa & 0.03 & 0.488 &\tabularnewline
920 & Yadhaykenu & 0.02 & 0.491 &\tabularnewline
800 & Guwamu & 0.01 & 0.495 &\tabularnewline
554 & Ngarluma & 0.01 & 0.498 &\tabularnewline
13 & Dyirbal & -0.01 & 0.503 &\tabularnewline
996 & Emmi & -0.02 & 0.508 &\tabularnewline
94 & Biri & -0.08 & 0.533 &\tabularnewline
495 & Nyikina & -0.09 & 0.535 &\tabularnewline
915 & Alawa & -0.11 & 0.544 &\tabularnewline
925 & Larrakia & -0.12 & 0.547 &\tabularnewline
232 & Warnman & -0.12 & 0.547 &\tabularnewline
38 & Djabugay & -0.12 & 0.548 &\tabularnewline
853 & Lardil & -0.13 & 0.551 &\tabularnewline
752 & Kija & -0.16 & 0.563 &\tabularnewline
1012 & Warrgamay & -0.17 & 0.566 &\tabularnewline
433 & Pitta Pitta & -0.21 & 0.582 &\tabularnewline
911 & Nyawaygi & -0.24 & 0.596 &\tabularnewline
546 & Yanyuwa & -0.25 & 0.597 &\tabularnewline
835 & Gugu Badhun & -0.25 & 0.599 &\tabularnewline
945 & Wiri & -0.26 & 0.603 &\tabularnewline
978 & Wotjobaluk & -0.26 & 0.604 &\tabularnewline
305 & Western Wakaya & -0.28 & 0.609 &\tabularnewline
1002 & Yintyingka & -0.34 & 0.633 &\tabularnewline
949 & Kok Nar & -0.37 & 0.643 &\tabularnewline
926 & Limilngan & -0.40 & 0.654 &\tabularnewline
63 & Dharumbal & -0.50 & 0.692 &\tabularnewline
1042 & Thaayorre & -0.50 & 0.693 &\tabularnewline
965 & Oykangand & -0.63 & 0.736 &\tabularnewline
1009 & Gamilaraay & -1.56 & 0.940 &\tabularnewline
964 & Olkol & -1.73 & 0.958 &\tabularnewline
1007 & Yuwaliyaay & -2.56 & 0.995 &\tabularnewline
\bottomrule
\end{longtable}

\newpage

\textbf{Table A.3.12. Comparing power law and exponential distributions
with \(x_{min}\) using Vuong's likelihood ratio test.}

Part A. Using \(x_{min}\) from the power law fit. \(R > 0\) favours
power law.

* \(p\) \textless{} 0.05 after Bonferroni correction. ** \(p\)
\textless{} 0.01 after Bonferroni correction.

\begin{longtable}[]{@{}rlrrl@{}}
\toprule
\textbf{lex ID} & \textbf{language variety} & \(R\) & \(p\) &
\textbf{signif.}\tabularnewline
\midrule
\endhead
1042 & Thaayorre & 3.19 & 0.001 &\tabularnewline
982 & Nhirrpi & 1.80 & 0.036 &\tabularnewline
200 & Western Arrernte & 1.73 & 0.042 &\tabularnewline
1016 & Tharrkari & 1.70 & 0.045 &\tabularnewline
162 & Adnyamathanha & 1.58 & 0.057 &\tabularnewline
1007 & Yuwaliyaay & 1.58 & 0.057 &\tabularnewline
534 & Nhanda & 1.54 & 0.061 &\tabularnewline
762 & Kariyarra & 1.49 & 0.069 &\tabularnewline
790 & Jaru & 1.41 & 0.079 &\tabularnewline
1040 & Ngarinyin & 1.36 & 0.086 &\tabularnewline
930 & Purduna & 1.31 & 0.094 &\tabularnewline
935 & Rembarrnga & 1.31 & 0.095 &\tabularnewline
905 & Malkana & 1.26 & 0.103 &\tabularnewline
1021 & Watjarri & 1.26 & 0.104 &\tabularnewline
620 & Miriwoong & 1.25 & 0.106 &\tabularnewline
919 & Angkamuthi & 1.25 & 0.106 &\tabularnewline
89 & Bunuba & 1.24 & 0.108 &\tabularnewline
847 & Ngalakgan & 1.22 & 0.112 &\tabularnewline
554 & Ngarluma & 1.21 & 0.113 &\tabularnewline
1006 & Central Arrernte & 1.20 & 0.115 &\tabularnewline
918 & Atampaya & 1.19 & 0.117 &\tabularnewline
968 & Ogh Angkula & 1.16 & 0.122 &\tabularnewline
1030 & Putijarra & 1.14 & 0.127 &\tabularnewline
1029 & Martuthunira & 1.11 & 0.133 &\tabularnewline
920 & Yadhaykenu & 1.11 & 0.133 &\tabularnewline
1008 & Yuwaalaraay & 1.10 & 0.136 &\tabularnewline
443 & Payungu & 1.10 & 0.136 &\tabularnewline
400 & Thalanyji & 1.09 & 0.137 &\tabularnewline
940 & Yawijibaya & 1.09 & 0.137 &\tabularnewline
81 & Dalabon & 1.04 & 0.150 &\tabularnewline
1009 & Gamilaraay & 1.01 & 0.156 &\tabularnewline
563 & Ngarla & 1.00 & 0.158 &\tabularnewline
778 & Jiwarli & 0.99 & 0.160 &\tabularnewline
914 & Yinhawangka & 0.99 & 0.162 &\tabularnewline
91 & Bularnu & 0.97 & 0.167 &\tabularnewline
519 & Nukunu & 0.95 & 0.170 &\tabularnewline
288 & Wangkatja & 0.95 & 0.171 &\tabularnewline
518 & Yarluyandi & 0.94 & 0.173 &\tabularnewline
957 & Ngaanyatjarra & 0.93 & 0.177 &\tabularnewline
917 & Nyamal & 0.92 & 0.178 &\tabularnewline
228 & Warriyangga & 0.90 & 0.184 &\tabularnewline
1019 & Walmajarri & 0.89 & 0.186 &\tabularnewline
985 & Yaygir & 0.89 & 0.187 &\tabularnewline
958 & Margany & 0.89 & 0.187 &\tabularnewline
963 & Kungkari & 0.88 & 0.189 &\tabularnewline
507 & Nyangumarta & 0.87 & 0.192 &\tabularnewline
1001 & Ngandi & 0.87 & 0.193 &\tabularnewline
853 & Lardil & 0.86 & 0.194 &\tabularnewline
572 & Ngamini & 0.86 & 0.196 &\tabularnewline
787 & Jawoyn & 0.84 & 0.199 &\tabularnewline
117 & Wirangu & 0.82 & 0.206 &\tabularnewline
631 & Yalarnnga & 0.82 & 0.206 &\tabularnewline
606 & Mudburra & 0.82 & 0.207 &\tabularnewline
910 & Nungali & 0.80 & 0.212 &\tabularnewline
433 & Pitta Pitta & 0.80 & 0.213 &\tabularnewline
943 & Pintupi & 0.79 & 0.214 &\tabularnewline
922 & Nakara & 0.76 & 0.225 &\tabularnewline
841 & Worrorra & 0.76 & 0.225 &\tabularnewline
237 & Warluwarra & 0.75 & 0.226 &\tabularnewline
85 & Burarra & 0.71 & 0.239 &\tabularnewline
242 & Warlpiri & 0.70 & 0.240 &\tabularnewline
1024 & Ngardily & 0.70 & 0.243 &\tabularnewline
1011 & Yorta Yorta & 0.70 & 0.243 &\tabularnewline
921 & Gurr-Goni & 0.68 & 0.249 &\tabularnewline
929 & Wanyjirra & 0.66 & 0.253 &\tabularnewline
13 & Dyirbal & 0.66 & 0.256 &\tabularnewline
845 & Iwaidja & 0.65 & 0.257 &\tabularnewline
939 & Unggumi & 0.65 & 0.257 &\tabularnewline
857 & Amurdak & 0.65 & 0.258 &\tabularnewline
417 & Yindjibarndi & 0.65 & 0.258 &\tabularnewline
618 & Mirniny & 0.64 & 0.262 &\tabularnewline
101 & Butchulla & 0.63 & 0.265 &\tabularnewline
972 & Ogh Unyjan & 0.63 & 0.265 &\tabularnewline
269 & Wangkumara & 0.62 & 0.268 &\tabularnewline
849 & Waanyi & 0.61 & 0.271 &\tabularnewline
767 & Karajarri & 0.60 & 0.275 &\tabularnewline
979 & Mawng & 0.60 & 0.275 &\tabularnewline
493 & Nyiyaparli & 0.59 & 0.278 &\tabularnewline
852 & Gurindji & 0.59 & 0.279 &\tabularnewline
462 & Panyjima & 0.58 & 0.280 &\tabularnewline
856 & Patjtjamalh & 0.57 & 0.285 &\tabularnewline
866 & Thirarri & 0.55 & 0.292 &\tabularnewline
983 & Nhangu & 0.54 & 0.295 &\tabularnewline
865 & Diyari & 0.54 & 0.296 &\tabularnewline
838 & Gooniyandi & 0.52 & 0.301 &\tabularnewline
232 & Warnman & 0.51 & 0.304 &\tabularnewline
77 & Dhangu & 0.50 & 0.310 &\tabularnewline
642 & Mangala & 0.49 & 0.312 &\tabularnewline
645 & Malyangapa & 0.47 & 0.318 &\tabularnewline
740 & Kugu Nganhcara & 0.47 & 0.319 &\tabularnewline
475 & Southern Paakintyi & 0.45 & 0.326 &\tabularnewline
31 & Djinang & 0.43 & 0.332 &\tabularnewline
113 & Yulparija & 0.42 & 0.336 &\tabularnewline
835 & Gugu Badhun & 0.42 & 0.338 &\tabularnewline
863 & Marra & 0.42 & 0.339 &\tabularnewline
927 & Tiwi & 0.40 & 0.345 &\tabularnewline
1003 & Murrinh-patha & 0.37 & 0.354 &\tabularnewline
377 & Umpila & 0.37 & 0.356 &\tabularnewline
967 & Thaynakwithi & 0.36 & 0.361 &\tabularnewline
807 & Gupapuyngu & 0.34 & 0.365 &\tabularnewline
977 & Warndarrang & 0.34 & 0.365 &\tabularnewline
848 & Wagiman & 0.34 & 0.367 &\tabularnewline
949 & Kok Nar & 0.33 & 0.369 &\tabularnewline
760 & Kartujarra & 0.33 & 0.370 &\tabularnewline
650 & Linngithigh & 0.32 & 0.374 &\tabularnewline
5 & Gangulu & 0.31 & 0.378 &\tabularnewline
565 & Ngarinyman & 0.30 & 0.381 &\tabularnewline
611 & Anguthimri & 0.29 & 0.386 &\tabularnewline
598 & Yandruwandha & 0.28 & 0.388 &\tabularnewline
63 & Dharumbal & 0.28 & 0.388 &\tabularnewline
592 & Muruwari & 0.28 & 0.391 &\tabularnewline
1023 & Wubuy & 0.27 & 0.395 &\tabularnewline
851 & Bilinarra & 0.26 & 0.399 &\tabularnewline
697 & Kurrama & 0.24 & 0.405 &\tabularnewline
925 & Larrakia & 0.23 & 0.409 &\tabularnewline
941 & Wambaya & 0.22 & 0.411 &\tabularnewline
204 & Wemba Wemba & 0.22 & 0.414 &\tabularnewline
952 & Ngawun & 0.21 & 0.416 &\tabularnewline
771 & Kalkatungu & 0.21 & 0.418 &\tabularnewline
966 & Wik Mungkan & 0.20 & 0.419 &\tabularnewline
1031 & Ngadjunmaya & 0.19 & 0.423 &\tabularnewline
915 & Alawa & 0.18 & 0.427 &\tabularnewline
38 & Djabugay & 0.16 & 0.438 &\tabularnewline
901 & Guugu Yimidhirr & 0.15 & 0.440 &\tabularnewline
99 & Bidyara & 0.15 & 0.442 &\tabularnewline
1043 & Mbabaram & 0.11 & 0.456 &\tabularnewline
996 & Emmi & 0.11 & 0.456 &\tabularnewline
412 & Ritharrngu & 0.10 & 0.459 &\tabularnewline
12 & Erre & 0.10 & 0.461 &\tabularnewline
734 & Kukatja & 0.09 & 0.464 &\tabularnewline
800 & Guwamu & 0.08 & 0.467 &\tabularnewline
540 & Ngiyambaa & 0.08 & 0.467 &\tabularnewline
962 & Gunya & 0.07 & 0.471 &\tabularnewline
118 & Badimaya & 0.07 & 0.472 &\tabularnewline
62 & Dhay'yi & 0.07 & 0.473 &\tabularnewline
656 & Kuugu Ya'u & 0.06 & 0.475 &\tabularnewline
752 & Kija & 0.05 & 0.480 &\tabularnewline
1032 & Kuku Yalanji & 0.00 & 0.498 &\tabularnewline
252 & Warlmanpa & -0.02 & 0.509 &\tabularnewline
265 & Wardaman & -0.04 & 0.516 &\tabularnewline
1018 & Djapu & -0.08 & 0.531 &\tabularnewline
105 & Bardi & -0.10 & 0.538 &\tabularnewline
170 & Wik-Ngathan & -0.12 & 0.547 &\tabularnewline
744 & Koko Bera & -0.12 & 0.549 &\tabularnewline
978 & Wotjobaluk & -0.13 & 0.552 &\tabularnewline
427 & Yidiny & -0.13 & 0.553 &\tabularnewline
546 & Yanyuwa & -0.15 & 0.558 &\tabularnewline
1012 & Warrgamay & -0.15 & 0.558 &\tabularnewline
911 & Nyawaygi & -0.16 & 0.565 &\tabularnewline
821 & Gumbaynggir & -0.19 & 0.577 &\tabularnewline
923 & Matngele & -0.19 & 0.577 &\tabularnewline
305 & Western Wakaya & -0.22 & 0.588 &\tabularnewline
926 & Limilngan & -0.24 & 0.596 &\tabularnewline
495 & Nyikina & -0.26 & 0.602 &\tabularnewline
94 & Biri & -0.29 & 0.616 &\tabularnewline
928 & Bakanh & -0.33 & 0.629 &\tabularnewline
621 & Mengerrdji & -0.37 & 0.643 &\tabularnewline
1002 & Yintyingka & -0.37 & 0.645 &\tabularnewline
946 & Kurtjar & -0.39 & 0.652 &\tabularnewline
945 & Wiri & -0.40 & 0.656 &\tabularnewline
1026 & Gidabal & -0.45 & 0.672 &\tabularnewline
1025 & Waalubal & -0.53 & 0.702 &\tabularnewline
30 & Duungidjawu & -0.75 & 0.772 &\tabularnewline
964 & Olkol & -0.75 & 0.772 &\tabularnewline
737 & Kukatj & -0.77 & 0.779 &\tabularnewline
965 & Oykangand & -0.90 & 0.817 &\tabularnewline
934 & Urningangg & -1.25 & 0.895 &\tabularnewline
363 & Yir Yoront & -1.87 & 0.969 &\tabularnewline
\bottomrule
\end{longtable}

\newpage

\textbf{Table A.3.13. Comparing power law and exponential distributions
with \(x_{min}\) using Vuong's likelihood ratio test.}

Part B. Using \(x_{min}\) from the exponential fit. \(R > 0\) favours
exponential.

* \(p\) \textless{} 0.05 after Bonferroni correction. ** \(p\)
\textless{} 0.01 after Bonferroni correction.

\begin{longtable}[]{@{}rlrrl@{}}
\toprule
\textbf{lex ID} & \textbf{language variety} & \(R\) & \(p\) &
\textbf{signif.}\tabularnewline
\midrule
\endhead
363 & Yir Yoront & 4.52 & 0.000 & **\tabularnewline
841 & Worrorra & 4.44 & 0.000 & **\tabularnewline
918 & Atampaya & 4.40 & 0.000 & **\tabularnewline
996 & Emmi & 4.34 & 0.000 & **\tabularnewline
1024 & Ngardily & 3.99 & 0.000 & **\tabularnewline
117 & Wirangu & 3.88 & 0.000 & **\tabularnewline
964 & Olkol & 3.86 & 0.000 & **\tabularnewline
618 & Mirniny & 3.83 & 0.000 & *\tabularnewline
228 & Warriyangga & 3.69 & 0.000 & *\tabularnewline
99 & Bidyara & 3.66 & 0.000 & *\tabularnewline
920 & Yadhaykenu & 3.59 & 0.000 & *\tabularnewline
968 & Ogh Angkula & 3.56 & 0.000 & *\tabularnewline
1031 & Ngadjunmaya & 3.46 & 0.000 & *\tabularnewline
982 & Nhirrpi & 3.37 & 0.000 &\tabularnewline
305 & Western Wakaya & 3.35 & 0.000 &\tabularnewline
737 & Kukatj & 3.31 & 0.000 &\tabularnewline
800 & Guwamu & 3.27 & 0.001 &\tabularnewline
852 & Gurindji & 3.25 & 0.001 &\tabularnewline
493 & Nyiyaparli & 3.24 & 0.001 &\tabularnewline
762 & Kariyarra & 3.24 & 0.001 &\tabularnewline
760 & Kartujarra & 3.21 & 0.001 &\tabularnewline
845 & Iwaidja & 3.16 & 0.001 &\tabularnewline
856 & Patjtjamalh & 3.14 & 0.001 &\tabularnewline
77 & Dhangu & 3.12 & 0.001 &\tabularnewline
94 & Biri & 3.08 & 0.001 &\tabularnewline
12 & Erre & 3.07 & 0.001 &\tabularnewline
941 & Wambaya & 3.06 & 0.001 &\tabularnewline
118 & Badimaya & 3.04 & 0.001 &\tabularnewline
917 & Nyamal & 3.02 & 0.001 &\tabularnewline
5 & Gangulu & 2.97 & 0.001 &\tabularnewline
563 & Ngarla & 2.95 & 0.002 &\tabularnewline
945 & Wiri & 2.94 & 0.002 &\tabularnewline
1016 & Tharrkari & 2.94 & 0.002 &\tabularnewline
838 & Gooniyandi & 2.93 & 0.002 &\tabularnewline
1009 & Gamilaraay & 2.87 & 0.002 &\tabularnewline
1030 & Putijarra & 2.84 & 0.002 &\tabularnewline
926 & Limilngan & 2.83 & 0.002 &\tabularnewline
697 & Kurrama & 2.83 & 0.002 &\tabularnewline
606 & Mudburra & 2.83 & 0.002 &\tabularnewline
734 & Kukatja & 2.81 & 0.002 &\tabularnewline
1003 & Murrinh-patha & 2.81 & 0.003 &\tabularnewline
252 & Warlmanpa & 2.77 & 0.003 &\tabularnewline
905 & Malkana & 2.72 & 0.003 &\tabularnewline
546 & Yanyuwa & 2.68 & 0.004 &\tabularnewline
1042 & Thaayorre & 2.67 & 0.004 &\tabularnewline
443 & Payungu & 2.65 & 0.004 &\tabularnewline
269 & Wangkumara & 2.64 & 0.004 &\tabularnewline
740 & Kugu Nganhcara & 2.62 & 0.004 &\tabularnewline
1021 & Watjarri & 2.55 & 0.005 &\tabularnewline
1029 & Martuthunira & 2.55 & 0.005 &\tabularnewline
1023 & Wubuy & 2.50 & 0.006 &\tabularnewline
1040 & Ngarinyin & 2.48 & 0.007 &\tabularnewline
857 & Amurdak & 2.48 & 0.007 &\tabularnewline
1001 & Ngandi & 2.46 & 0.007 &\tabularnewline
31 & Djinang & 2.43 & 0.008 &\tabularnewline
1002 & Yintyingka & 2.37 & 0.009 &\tabularnewline
1043 & Mbabaram & 2.36 & 0.009 &\tabularnewline
790 & Jaru & 2.36 & 0.009 &\tabularnewline
1007 & Yuwaliyaay & 2.35 & 0.009 &\tabularnewline
1018 & Djapu & 2.32 & 0.010 &\tabularnewline
642 & Mangala & 2.32 & 0.010 &\tabularnewline
949 & Kok Nar & 2.31 & 0.010 &\tabularnewline
919 & Angkamuthi & 2.31 & 0.011 &\tabularnewline
787 & Jawoyn & 2.31 & 0.011 &\tabularnewline
965 & Oykangand & 2.29 & 0.011 &\tabularnewline
377 & Umpila & 2.28 & 0.011 &\tabularnewline
853 & Lardil & 2.25 & 0.012 &\tabularnewline
91 & Bularnu & 2.24 & 0.012 &\tabularnewline
204 & Wemba Wemba & 2.23 & 0.013 &\tabularnewline
807 & Gupapuyngu & 2.23 & 0.013 &\tabularnewline
417 & Yindjibarndi & 2.16 & 0.015 &\tabularnewline
1008 & Yuwaalaraay & 2.15 & 0.016 &\tabularnewline
957 & Ngaanyatjarra & 2.14 & 0.016 &\tabularnewline
242 & Warlpiri & 2.12 & 0.017 &\tabularnewline
778 & Jiwarli & 2.06 & 0.020 &\tabularnewline
771 & Kalkatungu & 2.02 & 0.022 &\tabularnewline
952 & Ngawun & 2.01 & 0.022 &\tabularnewline
925 & Larrakia & 2.01 & 0.022 &\tabularnewline
1011 & Yorta Yorta & 1.92 & 0.028 &\tabularnewline
30 & Duungidjawu & 1.91 & 0.028 &\tabularnewline
835 & Gugu Badhun & 1.90 & 0.029 &\tabularnewline
979 & Mawng & 1.89 & 0.029 &\tabularnewline
554 & Ngarluma & 1.88 & 0.030 &\tabularnewline
495 & Nyikina & 1.85 & 0.032 &\tabularnewline
518 & Yarluyandi & 1.85 & 0.032 &\tabularnewline
89 & Bunuba & 1.85 & 0.032 &\tabularnewline
288 & Wangkatja & 1.84 & 0.033 &\tabularnewline
929 & Wanyjirra & 1.82 & 0.035 &\tabularnewline
922 & Nakara & 1.80 & 0.036 &\tabularnewline
592 & Muruwari & 1.80 & 0.036 &\tabularnewline
650 & Linngithigh & 1.79 & 0.037 &\tabularnewline
63 & Dharumbal & 1.78 & 0.038 &\tabularnewline
631 & Yalarnnga & 1.78 & 0.038 &\tabularnewline
412 & Ritharrngu & 1.75 & 0.040 &\tabularnewline
767 & Karajarri & 1.72 & 0.042 &\tabularnewline
611 & Anguthimri & 1.72 & 0.043 &\tabularnewline
200 & Western Arrernte & 1.71 & 0.044 &\tabularnewline
656 & Kuugu Ya'u & 1.66 & 0.048 &\tabularnewline
934 & Urningangg & 1.63 & 0.052 &\tabularnewline
939 & Unggumi & 1.61 & 0.054 &\tabularnewline
13 & Dyirbal & 1.60 & 0.055 &\tabularnewline
911 & Nyawaygi & 1.59 & 0.056 &\tabularnewline
923 & Matngele & 1.59 & 0.056 &\tabularnewline
863 & Marra & 1.55 & 0.061 &\tabularnewline
427 & Yidiny & 1.54 & 0.062 &\tabularnewline
927 & Tiwi & 1.50 & 0.066 &\tabularnewline
940 & Yawijibaya & 1.49 & 0.068 &\tabularnewline
1006 & Central Arrernte & 1.49 & 0.068 &\tabularnewline
1012 & Warrgamay & 1.46 & 0.073 &\tabularnewline
928 & Bakanh & 1.45 & 0.074 &\tabularnewline
915 & Alawa & 1.40 & 0.080 &\tabularnewline
265 & Wardaman & 1.40 & 0.081 &\tabularnewline
921 & Gurr-Goni & 1.39 & 0.082 &\tabularnewline
1026 & Gidabal & 1.36 & 0.087 &\tabularnewline
958 & Margany & 1.33 & 0.092 &\tabularnewline
978 & Wotjobaluk & 1.31 & 0.096 &\tabularnewline
946 & Kurtjar & 1.30 & 0.097 &\tabularnewline
744 & Koko Bera & 1.28 & 0.101 &\tabularnewline
572 & Ngamini & 1.24 & 0.108 &\tabularnewline
540 & Ngiyambaa & 1.23 & 0.109 &\tabularnewline
1019 & Walmajarri & 1.23 & 0.109 &\tabularnewline
962 & Gunya & 1.22 & 0.111 &\tabularnewline
621 & Mengerrdji & 1.19 & 0.116 &\tabularnewline
977 & Warndarrang & 1.19 & 0.117 &\tabularnewline
966 & Wik Mungkan & 1.19 & 0.118 &\tabularnewline
930 & Purduna & 1.13 & 0.130 &\tabularnewline
565 & Ngarinyman & 1.08 & 0.139 &\tabularnewline
985 & Yaygir & 1.04 & 0.149 &\tabularnewline
62 & Dhay'yi & 1.03 & 0.151 &\tabularnewline
38 & Djabugay & 1.02 & 0.155 &\tabularnewline
935 & Rembarrnga & 1.00 & 0.159 &\tabularnewline
901 & Guugu Yimidhirr & 0.97 & 0.166 &\tabularnewline
105 & Bardi & 0.96 & 0.168 &\tabularnewline
237 & Warluwarra & 0.94 & 0.174 &\tabularnewline
848 & Wagiman & 0.91 & 0.182 &\tabularnewline
752 & Kija & 0.89 & 0.185 &\tabularnewline
849 & Waanyi & 0.86 & 0.195 &\tabularnewline
972 & Ogh Unyjan & 0.86 & 0.196 &\tabularnewline
113 & Yulparija & 0.85 & 0.197 &\tabularnewline
81 & Dalabon & 0.83 & 0.202 &\tabularnewline
1025 & Waalubal & 0.79 & 0.215 &\tabularnewline
851 & Bilinarra & 0.77 & 0.220 &\tabularnewline
821 & Gumbaynggir & 0.74 & 0.231 &\tabularnewline
598 & Yandruwandha & 0.70 & 0.242 &\tabularnewline
1032 & Kuku Yalanji & 0.65 & 0.259 &\tabularnewline
400 & Thalanyji & 0.64 & 0.261 &\tabularnewline
620 & Miriwoong & 0.61 & 0.269 &\tabularnewline
963 & Kungkari & 0.61 & 0.270 &\tabularnewline
847 & Ngalakgan & 0.59 & 0.276 &\tabularnewline
462 & Panyjima & 0.59 & 0.277 &\tabularnewline
232 & Warnman & 0.58 & 0.282 &\tabularnewline
645 & Malyangapa & 0.55 & 0.290 &\tabularnewline
170 & Wik-Ngathan & 0.55 & 0.293 &\tabularnewline
967 & Thaynakwithi & 0.52 & 0.301 &\tabularnewline
914 & Yinhawangka & 0.44 & 0.330 &\tabularnewline
433 & Pitta Pitta & 0.44 & 0.331 &\tabularnewline
507 & Nyangumarta & 0.35 & 0.363 &\tabularnewline
519 & Nukunu & 0.33 & 0.370 &\tabularnewline
943 & Pintupi & 0.33 & 0.371 &\tabularnewline
983 & Nhangu & 0.30 & 0.384 &\tabularnewline
534 & Nhanda & 0.26 & 0.398 &\tabularnewline
910 & Nungali & 0.23 & 0.407 &\tabularnewline
866 & Thirarri & 0.12 & 0.452 &\tabularnewline
865 & Diyari & 0.08 & 0.467 &\tabularnewline
162 & Adnyamathanha & 0.03 & 0.489 &\tabularnewline
475 & Southern Paakintyi & -0.07 & 0.527 &\tabularnewline
85 & Burarra & -0.24 & 0.596 &\tabularnewline
101 & Butchulla & -0.63 & 0.735 &\tabularnewline
\bottomrule
\end{longtable}

\newpage

\textbf{Table A.3.14. Comparing power law and lognormal distributions
with \(x_{min}\) using Vuong's likelihood ratio test.}

Part A. Using \(x_{min}\) from the power law fit. \(R > 0\) favours
power law.

* \(p\) \textless{} 0.05 after Bonferroni correction. ** \(p\)
\textless{} 0.01 after Bonferroni correction.

\begin{longtable}[]{@{}rlrrl@{}}
\toprule
\textbf{lex ID} & \textbf{language variety} & \(R\) & \(p\) &
\textbf{signif.}\tabularnewline
\midrule
\endhead
1042 & Thaayorre & 3.19 & 0.001 &\tabularnewline
982 & Nhirrpi & 1.80 & 0.036 &\tabularnewline
200 & Western Arrernte & 1.73 & 0.042 &\tabularnewline
1016 & Tharrkari & 1.70 & 0.045 &\tabularnewline
162 & Adnyamathanha & 1.58 & 0.057 &\tabularnewline
1007 & Yuwaliyaay & 1.58 & 0.057 &\tabularnewline
534 & Nhanda & 1.54 & 0.061 &\tabularnewline
762 & Kariyarra & 1.49 & 0.069 &\tabularnewline
790 & Jaru & 1.41 & 0.079 &\tabularnewline
1040 & Ngarinyin & 1.36 & 0.086 &\tabularnewline
930 & Purduna & 1.31 & 0.094 &\tabularnewline
935 & Rembarrnga & 1.31 & 0.095 &\tabularnewline
905 & Malkana & 1.26 & 0.103 &\tabularnewline
1021 & Watjarri & 1.26 & 0.104 &\tabularnewline
620 & Miriwoong & 1.25 & 0.106 &\tabularnewline
919 & Angkamuthi & 1.25 & 0.106 &\tabularnewline
89 & Bunuba & 1.24 & 0.108 &\tabularnewline
847 & Ngalakgan & 1.22 & 0.112 &\tabularnewline
554 & Ngarluma & 1.21 & 0.113 &\tabularnewline
1006 & Central Arrernte & 1.20 & 0.115 &\tabularnewline
918 & Atampaya & 1.19 & 0.117 &\tabularnewline
968 & Ogh Angkula & 1.16 & 0.122 &\tabularnewline
1030 & Putijarra & 1.14 & 0.127 &\tabularnewline
1029 & Martuthunira & 1.11 & 0.133 &\tabularnewline
920 & Yadhaykenu & 1.11 & 0.133 &\tabularnewline
1008 & Yuwaalaraay & 1.10 & 0.136 &\tabularnewline
443 & Payungu & 1.10 & 0.136 &\tabularnewline
400 & Thalanyji & 1.09 & 0.137 &\tabularnewline
940 & Yawijibaya & 1.09 & 0.137 &\tabularnewline
81 & Dalabon & 1.04 & 0.150 &\tabularnewline
1009 & Gamilaraay & 1.01 & 0.156 &\tabularnewline
563 & Ngarla & 1.00 & 0.158 &\tabularnewline
778 & Jiwarli & 0.99 & 0.160 &\tabularnewline
914 & Yinhawangka & 0.99 & 0.162 &\tabularnewline
91 & Bularnu & 0.97 & 0.167 &\tabularnewline
519 & Nukunu & 0.95 & 0.170 &\tabularnewline
288 & Wangkatja & 0.95 & 0.171 &\tabularnewline
518 & Yarluyandi & 0.94 & 0.173 &\tabularnewline
957 & Ngaanyatjarra & 0.93 & 0.177 &\tabularnewline
917 & Nyamal & 0.92 & 0.178 &\tabularnewline
228 & Warriyangga & 0.90 & 0.184 &\tabularnewline
1019 & Walmajarri & 0.89 & 0.186 &\tabularnewline
985 & Yaygir & 0.89 & 0.187 &\tabularnewline
958 & Margany & 0.89 & 0.187 &\tabularnewline
963 & Kungkari & 0.88 & 0.189 &\tabularnewline
507 & Nyangumarta & 0.87 & 0.192 &\tabularnewline
1001 & Ngandi & 0.87 & 0.193 &\tabularnewline
853 & Lardil & 0.86 & 0.194 &\tabularnewline
572 & Ngamini & 0.86 & 0.196 &\tabularnewline
787 & Jawoyn & 0.84 & 0.199 &\tabularnewline
117 & Wirangu & 0.82 & 0.206 &\tabularnewline
631 & Yalarnnga & 0.82 & 0.206 &\tabularnewline
606 & Mudburra & 0.82 & 0.207 &\tabularnewline
910 & Nungali & 0.80 & 0.212 &\tabularnewline
433 & Pitta Pitta & 0.80 & 0.213 &\tabularnewline
943 & Pintupi & 0.79 & 0.214 &\tabularnewline
922 & Nakara & 0.76 & 0.225 &\tabularnewline
841 & Worrorra & 0.76 & 0.225 &\tabularnewline
237 & Warluwarra & 0.75 & 0.226 &\tabularnewline
85 & Burarra & 0.71 & 0.239 &\tabularnewline
242 & Warlpiri & 0.70 & 0.240 &\tabularnewline
1024 & Ngardily & 0.70 & 0.243 &\tabularnewline
1011 & Yorta Yorta & 0.70 & 0.243 &\tabularnewline
921 & Gurr-Goni & 0.68 & 0.249 &\tabularnewline
929 & Wanyjirra & 0.66 & 0.253 &\tabularnewline
13 & Dyirbal & 0.66 & 0.256 &\tabularnewline
845 & Iwaidja & 0.65 & 0.257 &\tabularnewline
939 & Unggumi & 0.65 & 0.257 &\tabularnewline
857 & Amurdak & 0.65 & 0.258 &\tabularnewline
417 & Yindjibarndi & 0.65 & 0.258 &\tabularnewline
618 & Mirniny & 0.64 & 0.262 &\tabularnewline
101 & Butchulla & 0.63 & 0.265 &\tabularnewline
972 & Ogh Unyjan & 0.63 & 0.265 &\tabularnewline
269 & Wangkumara & 0.62 & 0.268 &\tabularnewline
849 & Waanyi & 0.61 & 0.271 &\tabularnewline
767 & Karajarri & 0.60 & 0.275 &\tabularnewline
979 & Mawng & 0.60 & 0.275 &\tabularnewline
493 & Nyiyaparli & 0.59 & 0.278 &\tabularnewline
852 & Gurindji & 0.59 & 0.279 &\tabularnewline
462 & Panyjima & 0.58 & 0.280 &\tabularnewline
856 & Patjtjamalh & 0.57 & 0.285 &\tabularnewline
866 & Thirarri & 0.55 & 0.292 &\tabularnewline
983 & Nhangu & 0.54 & 0.295 &\tabularnewline
865 & Diyari & 0.54 & 0.296 &\tabularnewline
838 & Gooniyandi & 0.52 & 0.301 &\tabularnewline
232 & Warnman & 0.51 & 0.304 &\tabularnewline
77 & Dhangu & 0.50 & 0.310 &\tabularnewline
642 & Mangala & 0.49 & 0.312 &\tabularnewline
645 & Malyangapa & 0.47 & 0.318 &\tabularnewline
740 & Kugu Nganhcara & 0.47 & 0.319 &\tabularnewline
475 & Southern Paakintyi & 0.45 & 0.326 &\tabularnewline
31 & Djinang & 0.43 & 0.332 &\tabularnewline
113 & Yulparija & 0.42 & 0.336 &\tabularnewline
835 & Gugu Badhun & 0.42 & 0.338 &\tabularnewline
863 & Marra & 0.42 & 0.339 &\tabularnewline
927 & Tiwi & 0.40 & 0.345 &\tabularnewline
1003 & Murrinh-patha & 0.37 & 0.354 &\tabularnewline
377 & Umpila & 0.37 & 0.356 &\tabularnewline
967 & Thaynakwithi & 0.36 & 0.361 &\tabularnewline
807 & Gupapuyngu & 0.34 & 0.365 &\tabularnewline
977 & Warndarrang & 0.34 & 0.365 &\tabularnewline
848 & Wagiman & 0.34 & 0.367 &\tabularnewline
949 & Kok Nar & 0.33 & 0.369 &\tabularnewline
760 & Kartujarra & 0.33 & 0.370 &\tabularnewline
650 & Linngithigh & 0.32 & 0.374 &\tabularnewline
5 & Gangulu & 0.31 & 0.378 &\tabularnewline
565 & Ngarinyman & 0.30 & 0.381 &\tabularnewline
611 & Anguthimri & 0.29 & 0.386 &\tabularnewline
598 & Yandruwandha & 0.28 & 0.388 &\tabularnewline
63 & Dharumbal & 0.28 & 0.388 &\tabularnewline
592 & Muruwari & 0.28 & 0.391 &\tabularnewline
1023 & Wubuy & 0.27 & 0.395 &\tabularnewline
851 & Bilinarra & 0.26 & 0.399 &\tabularnewline
697 & Kurrama & 0.24 & 0.405 &\tabularnewline
925 & Larrakia & 0.23 & 0.409 &\tabularnewline
941 & Wambaya & 0.22 & 0.411 &\tabularnewline
204 & Wemba Wemba & 0.22 & 0.414 &\tabularnewline
952 & Ngawun & 0.21 & 0.416 &\tabularnewline
771 & Kalkatungu & 0.21 & 0.418 &\tabularnewline
966 & Wik Mungkan & 0.20 & 0.419 &\tabularnewline
1031 & Ngadjunmaya & 0.19 & 0.423 &\tabularnewline
915 & Alawa & 0.18 & 0.427 &\tabularnewline
38 & Djabugay & 0.16 & 0.438 &\tabularnewline
901 & Guugu Yimidhirr & 0.15 & 0.440 &\tabularnewline
99 & Bidyara & 0.15 & 0.442 &\tabularnewline
1043 & Mbabaram & 0.11 & 0.456 &\tabularnewline
996 & Emmi & 0.11 & 0.456 &\tabularnewline
412 & Ritharrngu & 0.10 & 0.459 &\tabularnewline
12 & Erre & 0.10 & 0.461 &\tabularnewline
734 & Kukatja & 0.09 & 0.464 &\tabularnewline
800 & Guwamu & 0.08 & 0.467 &\tabularnewline
540 & Ngiyambaa & 0.08 & 0.467 &\tabularnewline
962 & Gunya & 0.07 & 0.471 &\tabularnewline
118 & Badimaya & 0.07 & 0.472 &\tabularnewline
62 & Dhay'yi & 0.07 & 0.473 &\tabularnewline
656 & Kuugu Ya'u & 0.06 & 0.475 &\tabularnewline
752 & Kija & 0.05 & 0.480 &\tabularnewline
1032 & Kuku Yalanji & 0.00 & 0.498 &\tabularnewline
252 & Warlmanpa & -0.02 & 0.509 &\tabularnewline
265 & Wardaman & -0.04 & 0.516 &\tabularnewline
1018 & Djapu & -0.08 & 0.531 &\tabularnewline
105 & Bardi & -0.10 & 0.538 &\tabularnewline
170 & Wik-Ngathan & -0.12 & 0.547 &\tabularnewline
744 & Koko Bera & -0.12 & 0.549 &\tabularnewline
978 & Wotjobaluk & -0.13 & 0.552 &\tabularnewline
427 & Yidiny & -0.13 & 0.553 &\tabularnewline
546 & Yanyuwa & -0.15 & 0.558 &\tabularnewline
1012 & Warrgamay & -0.15 & 0.558 &\tabularnewline
911 & Nyawaygi & -0.16 & 0.565 &\tabularnewline
821 & Gumbaynggir & -0.19 & 0.577 &\tabularnewline
923 & Matngele & -0.19 & 0.577 &\tabularnewline
305 & Western Wakaya & -0.22 & 0.588 &\tabularnewline
926 & Limilngan & -0.24 & 0.596 &\tabularnewline
495 & Nyikina & -0.26 & 0.602 &\tabularnewline
94 & Biri & -0.29 & 0.616 &\tabularnewline
928 & Bakanh & -0.33 & 0.629 &\tabularnewline
621 & Mengerrdji & -0.37 & 0.643 &\tabularnewline
1002 & Yintyingka & -0.37 & 0.645 &\tabularnewline
946 & Kurtjar & -0.39 & 0.652 &\tabularnewline
945 & Wiri & -0.40 & 0.656 &\tabularnewline
1026 & Gidabal & -0.45 & 0.672 &\tabularnewline
1025 & Waalubal & -0.53 & 0.702 &\tabularnewline
30 & Duungidjawu & -0.75 & 0.772 &\tabularnewline
964 & Olkol & -0.75 & 0.772 &\tabularnewline
737 & Kukatj & -0.77 & 0.779 &\tabularnewline
965 & Oykangand & -0.90 & 0.817 &\tabularnewline
934 & Urningangg & -1.25 & 0.895 &\tabularnewline
363 & Yir Yoront & -1.87 & 0.969 &\tabularnewline
\bottomrule
\end{longtable}

\newpage

\textbf{Table A.3.15. Comparing power law and lognormal distributions
with \(x_{min}\) using Vuong's likelihood ratio test.}

Part B. Using \(x_{min}\) from the lognormal fit. \(R > 0\) favours
lognormal.

* \(p\) \textless{} 0.05 after Bonferroni correction. ** \(p\)
\textless{} 0.01 after Bonferroni correction.

\begin{longtable}[]{@{}rlrrl@{}}
\toprule
\textbf{lex ID} & \textbf{language variety} & \(R\) & \(p\) &
\textbf{signif.}\tabularnewline
\midrule
\endhead
363 & Yir Yoront & 4.52 & 0.000 & **\tabularnewline
841 & Worrorra & 4.44 & 0.000 & **\tabularnewline
918 & Atampaya & 4.40 & 0.000 & **\tabularnewline
996 & Emmi & 4.34 & 0.000 & **\tabularnewline
1024 & Ngardily & 3.99 & 0.000 & **\tabularnewline
117 & Wirangu & 3.88 & 0.000 & **\tabularnewline
964 & Olkol & 3.86 & 0.000 & **\tabularnewline
618 & Mirniny & 3.83 & 0.000 & *\tabularnewline
228 & Warriyangga & 3.69 & 0.000 & *\tabularnewline
99 & Bidyara & 3.66 & 0.000 & *\tabularnewline
920 & Yadhaykenu & 3.59 & 0.000 & *\tabularnewline
968 & Ogh Angkula & 3.56 & 0.000 & *\tabularnewline
1031 & Ngadjunmaya & 3.46 & 0.000 & *\tabularnewline
982 & Nhirrpi & 3.37 & 0.000 &\tabularnewline
305 & Western Wakaya & 3.35 & 0.000 &\tabularnewline
737 & Kukatj & 3.31 & 0.000 &\tabularnewline
800 & Guwamu & 3.27 & 0.001 &\tabularnewline
852 & Gurindji & 3.25 & 0.001 &\tabularnewline
493 & Nyiyaparli & 3.24 & 0.001 &\tabularnewline
762 & Kariyarra & 3.24 & 0.001 &\tabularnewline
760 & Kartujarra & 3.21 & 0.001 &\tabularnewline
845 & Iwaidja & 3.16 & 0.001 &\tabularnewline
856 & Patjtjamalh & 3.14 & 0.001 &\tabularnewline
77 & Dhangu & 3.12 & 0.001 &\tabularnewline
94 & Biri & 3.08 & 0.001 &\tabularnewline
12 & Erre & 3.07 & 0.001 &\tabularnewline
941 & Wambaya & 3.06 & 0.001 &\tabularnewline
118 & Badimaya & 3.04 & 0.001 &\tabularnewline
917 & Nyamal & 3.02 & 0.001 &\tabularnewline
5 & Gangulu & 2.97 & 0.001 &\tabularnewline
563 & Ngarla & 2.95 & 0.002 &\tabularnewline
945 & Wiri & 2.94 & 0.002 &\tabularnewline
1016 & Tharrkari & 2.94 & 0.002 &\tabularnewline
838 & Gooniyandi & 2.93 & 0.002 &\tabularnewline
1009 & Gamilaraay & 2.87 & 0.002 &\tabularnewline
1030 & Putijarra & 2.84 & 0.002 &\tabularnewline
926 & Limilngan & 2.83 & 0.002 &\tabularnewline
697 & Kurrama & 2.83 & 0.002 &\tabularnewline
606 & Mudburra & 2.83 & 0.002 &\tabularnewline
734 & Kukatja & 2.81 & 0.002 &\tabularnewline
1003 & Murrinh-patha & 2.81 & 0.003 &\tabularnewline
252 & Warlmanpa & 2.77 & 0.003 &\tabularnewline
905 & Malkana & 2.72 & 0.003 &\tabularnewline
546 & Yanyuwa & 2.68 & 0.004 &\tabularnewline
1042 & Thaayorre & 2.67 & 0.004 &\tabularnewline
443 & Payungu & 2.65 & 0.004 &\tabularnewline
269 & Wangkumara & 2.64 & 0.004 &\tabularnewline
740 & Kugu Nganhcara & 2.62 & 0.004 &\tabularnewline
1021 & Watjarri & 2.55 & 0.005 &\tabularnewline
1029 & Martuthunira & 2.55 & 0.005 &\tabularnewline
1023 & Wubuy & 2.50 & 0.006 &\tabularnewline
1040 & Ngarinyin & 2.48 & 0.007 &\tabularnewline
857 & Amurdak & 2.48 & 0.007 &\tabularnewline
1001 & Ngandi & 2.46 & 0.007 &\tabularnewline
31 & Djinang & 2.43 & 0.008 &\tabularnewline
1002 & Yintyingka & 2.37 & 0.009 &\tabularnewline
1043 & Mbabaram & 2.36 & 0.009 &\tabularnewline
790 & Jaru & 2.36 & 0.009 &\tabularnewline
1007 & Yuwaliyaay & 2.35 & 0.009 &\tabularnewline
1018 & Djapu & 2.32 & 0.010 &\tabularnewline
642 & Mangala & 2.32 & 0.010 &\tabularnewline
949 & Kok Nar & 2.31 & 0.010 &\tabularnewline
919 & Angkamuthi & 2.31 & 0.011 &\tabularnewline
787 & Jawoyn & 2.31 & 0.011 &\tabularnewline
965 & Oykangand & 2.29 & 0.011 &\tabularnewline
377 & Umpila & 2.28 & 0.011 &\tabularnewline
853 & Lardil & 2.25 & 0.012 &\tabularnewline
91 & Bularnu & 2.24 & 0.012 &\tabularnewline
204 & Wemba Wemba & 2.23 & 0.013 &\tabularnewline
807 & Gupapuyngu & 2.23 & 0.013 &\tabularnewline
417 & Yindjibarndi & 2.16 & 0.015 &\tabularnewline
1008 & Yuwaalaraay & 2.15 & 0.016 &\tabularnewline
957 & Ngaanyatjarra & 2.14 & 0.016 &\tabularnewline
242 & Warlpiri & 2.12 & 0.017 &\tabularnewline
778 & Jiwarli & 2.06 & 0.020 &\tabularnewline
771 & Kalkatungu & 2.02 & 0.022 &\tabularnewline
952 & Ngawun & 2.01 & 0.022 &\tabularnewline
925 & Larrakia & 2.01 & 0.022 &\tabularnewline
1011 & Yorta Yorta & 1.92 & 0.028 &\tabularnewline
30 & Duungidjawu & 1.91 & 0.028 &\tabularnewline
835 & Gugu Badhun & 1.90 & 0.029 &\tabularnewline
979 & Mawng & 1.89 & 0.029 &\tabularnewline
554 & Ngarluma & 1.88 & 0.030 &\tabularnewline
495 & Nyikina & 1.85 & 0.032 &\tabularnewline
518 & Yarluyandi & 1.85 & 0.032 &\tabularnewline
89 & Bunuba & 1.85 & 0.032 &\tabularnewline
288 & Wangkatja & 1.84 & 0.033 &\tabularnewline
929 & Wanyjirra & 1.82 & 0.035 &\tabularnewline
922 & Nakara & 1.80 & 0.036 &\tabularnewline
592 & Muruwari & 1.80 & 0.036 &\tabularnewline
650 & Linngithigh & 1.79 & 0.037 &\tabularnewline
63 & Dharumbal & 1.78 & 0.038 &\tabularnewline
631 & Yalarnnga & 1.78 & 0.038 &\tabularnewline
412 & Ritharrngu & 1.75 & 0.040 &\tabularnewline
767 & Karajarri & 1.72 & 0.042 &\tabularnewline
611 & Anguthimri & 1.72 & 0.043 &\tabularnewline
200 & Western Arrernte & 1.71 & 0.044 &\tabularnewline
656 & Kuugu Ya'u & 1.66 & 0.048 &\tabularnewline
934 & Urningangg & 1.63 & 0.052 &\tabularnewline
939 & Unggumi & 1.61 & 0.054 &\tabularnewline
13 & Dyirbal & 1.60 & 0.055 &\tabularnewline
911 & Nyawaygi & 1.59 & 0.056 &\tabularnewline
923 & Matngele & 1.59 & 0.056 &\tabularnewline
863 & Marra & 1.55 & 0.061 &\tabularnewline
427 & Yidiny & 1.54 & 0.062 &\tabularnewline
927 & Tiwi & 1.50 & 0.066 &\tabularnewline
940 & Yawijibaya & 1.49 & 0.068 &\tabularnewline
1006 & Central Arrernte & 1.49 & 0.068 &\tabularnewline
1012 & Warrgamay & 1.46 & 0.073 &\tabularnewline
928 & Bakanh & 1.45 & 0.074 &\tabularnewline
915 & Alawa & 1.40 & 0.080 &\tabularnewline
265 & Wardaman & 1.40 & 0.081 &\tabularnewline
921 & Gurr-Goni & 1.39 & 0.082 &\tabularnewline
1026 & Gidabal & 1.36 & 0.087 &\tabularnewline
958 & Margany & 1.33 & 0.092 &\tabularnewline
978 & Wotjobaluk & 1.31 & 0.096 &\tabularnewline
946 & Kurtjar & 1.30 & 0.097 &\tabularnewline
744 & Koko Bera & 1.28 & 0.101 &\tabularnewline
572 & Ngamini & 1.24 & 0.108 &\tabularnewline
540 & Ngiyambaa & 1.23 & 0.109 &\tabularnewline
1019 & Walmajarri & 1.23 & 0.109 &\tabularnewline
962 & Gunya & 1.22 & 0.111 &\tabularnewline
621 & Mengerrdji & 1.19 & 0.116 &\tabularnewline
977 & Warndarrang & 1.19 & 0.117 &\tabularnewline
966 & Wik Mungkan & 1.19 & 0.118 &\tabularnewline
930 & Purduna & 1.13 & 0.130 &\tabularnewline
565 & Ngarinyman & 1.08 & 0.139 &\tabularnewline
985 & Yaygir & 1.04 & 0.149 &\tabularnewline
62 & Dhay'yi & 1.03 & 0.151 &\tabularnewline
38 & Djabugay & 1.02 & 0.155 &\tabularnewline
935 & Rembarrnga & 1.00 & 0.159 &\tabularnewline
901 & Guugu Yimidhirr & 0.97 & 0.166 &\tabularnewline
105 & Bardi & 0.96 & 0.168 &\tabularnewline
237 & Warluwarra & 0.94 & 0.174 &\tabularnewline
848 & Wagiman & 0.91 & 0.182 &\tabularnewline
752 & Kija & 0.89 & 0.185 &\tabularnewline
849 & Waanyi & 0.86 & 0.195 &\tabularnewline
972 & Ogh Unyjan & 0.86 & 0.196 &\tabularnewline
113 & Yulparija & 0.85 & 0.197 &\tabularnewline
81 & Dalabon & 0.83 & 0.202 &\tabularnewline
1025 & Waalubal & 0.79 & 0.215 &\tabularnewline
851 & Bilinarra & 0.77 & 0.220 &\tabularnewline
821 & Gumbaynggir & 0.74 & 0.231 &\tabularnewline
598 & Yandruwandha & 0.70 & 0.242 &\tabularnewline
1032 & Kuku Yalanji & 0.65 & 0.259 &\tabularnewline
400 & Thalanyji & 0.64 & 0.261 &\tabularnewline
620 & Miriwoong & 0.61 & 0.269 &\tabularnewline
963 & Kungkari & 0.61 & 0.270 &\tabularnewline
847 & Ngalakgan & 0.59 & 0.276 &\tabularnewline
462 & Panyjima & 0.59 & 0.277 &\tabularnewline
232 & Warnman & 0.58 & 0.282 &\tabularnewline
645 & Malyangapa & 0.55 & 0.290 &\tabularnewline
170 & Wik-Ngathan & 0.55 & 0.293 &\tabularnewline
967 & Thaynakwithi & 0.52 & 0.301 &\tabularnewline
914 & Yinhawangka & 0.44 & 0.330 &\tabularnewline
433 & Pitta Pitta & 0.44 & 0.331 &\tabularnewline
507 & Nyangumarta & 0.35 & 0.363 &\tabularnewline
519 & Nukunu & 0.33 & 0.370 &\tabularnewline
943 & Pintupi & 0.33 & 0.371 &\tabularnewline
983 & Nhangu & 0.30 & 0.384 &\tabularnewline
534 & Nhanda & 0.26 & 0.398 &\tabularnewline
910 & Nungali & 0.23 & 0.407 &\tabularnewline
866 & Thirarri & 0.12 & 0.452 &\tabularnewline
865 & Diyari & 0.08 & 0.467 &\tabularnewline
162 & Adnyamathanha & 0.03 & 0.489 &\tabularnewline
475 & Southern Paakintyi & -0.07 & 0.527 &\tabularnewline
85 & Burarra & -0.24 & 0.596 &\tabularnewline
101 & Butchulla & -0.63 & 0.735 &\tabularnewline
\bottomrule
\end{longtable}

\section*{References}

\printbibliography[keyword=inA1,heading=none]
